\title{3 months}
\author{Huxley Sparks}
\begin{document}
	Zeus
	In the garage, laptop compiling code, hooked up to a machine. Sporadic movements manifest in the electrical metal golem. On another screen, it runs
	the logs of what each component is doing and if behaving properly. They are never perfect but the main design of each machine makes it
	valuable. Spider for recon, android phone as traveling tool, metal locust destroy bigger bots, imploding after use. Only family he has is his
	older brother, Poseidon. Zeus was on his own around 17, family dead, Poseidon gone to sea. Bond between them was strong despite distance, communicating by
	mail or phone. Until 20, Poseidon gave him cash to help pay for his school.

	    With everything going wrong around him, how does he stay calm? he tells me it was only his father; the sole person who believed in him and asked for nothing
	in return, not even his love. Everyone in his family spoiled and smoothered him, treating him always as a child. His dad treated him as an equal, talked to
	him with respect, followed his journeys, pushed him off his mental cliffs. After a few years, his dad left him. Before leaving, his father told him to believe
	in his new parents so he can have a normal life and to use the tools he had given him. As he cried as his dad left, "Don't cry, it never gets you anything."
	His dad hugs him closer, "You'll be fine, you'll be great. I don't expect you to love me, that's not what I want from you."
	
		Zeus graduates from high school early, with honors. Before walking inside his house to meet his congragulation party, he asked himself why. Feeling  
	disconnected from its contents, he left to live with his brother. While there, he attended college, on his own accord, besides the ultimatum his brother
	gave him about college or the streets. Poisedon majored in literature and when they went fishing with his brother's friends, he always told vivid stories.

		With everyone asleep, Poisedon eyes begin to close. He feels a tug on his sleeve, "keep going." Zeus is wide awake, yearning to hear the complete 
	story. Rolling his eyes, chuckling, "I'll finish, get me some coffee though." In the cockpit, Zeus goes to the coffee maker and pours a cup when he hears her
	voice. "USSR, please respond." Grabbing the receiver, "Can I help you?" "Hi, USS, I need you to change your route by 15 degrees, there's a large buoy on
	your path tha can cause damage, please change route. Zeus moves to the wheel and turns it. "Thanks USSR, I thought you were going to rustle me about the
	buoy not showing up on the radar." "Sure thing."

		"Miss, how old are you, your voice sounds soft." "Too young to be called Miss yet, you, boy?" As they chatter, Poseidon walks in and Zeus doesn't see
	him until he reaches for the receiver. "It wasn't her fault, I was just curious." "Athena, I expected better from you. You know that this channel is reserved
	for important transmission. If you want to have a chat with Zeus, please use channel 9." "Yes Sir, right away, Sir. Thank you, Sir." As he leaves, "Oh yea,
	thanks for the changing the route for me."

		2012, the big fright. An epedemic spreads quickly around the world as sun rays. All religions pointed to this year as the apocalypse. Everywhere,
	messages of repent, convert, pray, donate. Everyone becomes extremly religious, segregating themselves from other religions. As tension rose, heretics started
	sprouting up, saying that they had to be the cause of the apocalypse.

		Near the end of the year, a few of them had in their hands nukes. Other nations went to their arms and declare themselves a distinct religion. A stand
	still, the gunslingers believed they had to be alive until their God came. It was one heretics hatred for another religion that caused defcon. While the 
	missles were in the air, people dropped everything, they became their true selves. Only a few became satisfied of those who wre oblivated in the blast. The
	ozone damaged, soil, water and vegetation. The most valuable items were unscathe areas.
