\title{Arch}
\author{Huxley Spark}
\document{begin}

		Thoughts: Hero beats challenge | lives in society | strives for challenge | dies
			>problem => people see as threat, achievement as small
			Arch - persistence | broken after impatience

		On the bland day, Arch sails his tugboat further into the sea. Steering into the abyss, he doesn't blink. On the radio, cries of panic warn him to 
	change his course. Their words never reach up to his ears but he ends up turning it off when he notices the green light on. Reading the other dials, everything
	looks normal. "The exception is the compass embedded in the controls, its hand twirling round and round without no end. Arch turns to the window to check the
	ship direction, "I must be close."

		Going to the back of the boat, he lets himself take a glance  of everything behind him. Feeling the ship get further and further from the shore brings
	him comfort (tranquil?). There's nothing worth staying back over there, this is how it has to be.

		Sitting down with his back on the fencing at the ship, he wonders if he could have been anyone else, a version of himself less ruthless. He thinks of
	Adam, married to his wife, happy working and going back to her near the end of the day. Both of them were there when it happened, the chaos in that building.
	He supposes that Adam stayed away in consideration of his wife and his life. Arch could have done the same for at least his life but to challenge chaos was
	too strong to avoid.

		The tides cause Arch to slam to the fence behind him. In response, he puts his arms over the railings to keep him attached to the wall. Everything
	after his spirit was a blur. When he woke up, he found himself in Adam's bed. Adam comes with food at once, giving it to Arch, as Adam retells him of his
	actions. "You ran a swift stride to the entrance, getting a gun from an officer, shouting up in the air to startle them to hide and knocking out the first
	criminal by slamming the door open. I lost sight of you from there. The only thing everyone saw from the outside was the fire alarm go off. The cops stood 
	still from being overwhelmed with confusion. Gunshots still pierced through the sirens and everyone kept thinking you were already dead."

		"When we saw hostages running out of the building, we forgot about you. Then the fire appeared and knew that was you. Time had slowed down as we saw
	the fire start to consume the whole building. The sirens, bullets, screams and the fire, it was too much that a few bystanders fainted. At its climax, we
	saw someone pushed out through glass and fall to the ground."

		"From there, the situation turned from human threat to natural disaster. The whole time outside, I saw the stubborn anger on others. Assuming that it
	wasn't good for you, I had to move you out of there once you got out. They all waited by the entrance to apprehend you, to make it stop. Maybe you didn't have
	enough time, maybe you knew; you broke though glass and landed on the branches of a tree to the side of the building. You were on a the brink of consciousness
	but still managed to help me put you in my car. And that's how you ended up here."

		"I left some clothes in the shower whenever you take a bath. I'll be back, I'm going to take my wife to dinner. She's been more accepting about the
	fiasco you did out there and having you here."

		Arch hears the front door close; he looks down to his meal, scraps to him. It would satisfy most humans but to him, hunger would be immune to the 
	crumbs. He sets it aside on the shelf and gets off the bed, to stand upright once again. Twisting his torso, lifting each leg to his chest, lunging and
	extending his arms over his head. Done, he goes towards the window to see what is outside. He sees all the buildings, garages, houses, a few factories. A ball
	bounces from to and fro, one empty space to another, cars drive themselves and nobody cutting the lawn. He clears his eyes but the perception persist.

		"So the search is still going on for the fugitive that made a disaster of a police contained situation. Wanted for breaking several laws, dramatizing
	hostages and assault charges on the criminals." Arch goes to the television and decides to listen to it as if it were a radio. "Next to me, I have Emily,
	one of the hostages of the horrible event. Can you tell us what happened?" "Yes, yes I can Stan. The lunatic came shooting bullets everywhere. He took shots
	at the captivators while they held a few of us by them. He said something that we had to do our part too, in order to live. I didn't know what he meant and
	then he shot the guy who held me hostage. The bullet was this close," she holds an imaginary bullet an inch away from the side of her eye, "he could have 
	killed me, all of us. Luckily, we survived and now want to put this freak in jail where he can't ever put the lives of the innocent at risk again."

		Arch turns off the tv in disgust, not being able to look at those he helped nor their kind. He goes to the kitchen and finds the fridge less satisfied
	with its contents than he is. Still hungry, he gets a pen and paper to leave Adam a note, saying that he left so he can handle his own problems instead of
	being a problem to him. He thanks him for his help and leaves the note on the fridge.

		Walking home, he goes through a park. In this park, there's a playground where kids roam and their parents monitor their actions. A particular child
	grabs his attention since its hard to ignore the only loud cry of a child in the vecinity. The boy was to the top of the tower until he realized how far he was
	from the ground. He held to the post of the tower tightly, crying for help. His dad comes to him, soothes the boy as he brings him down. Instead of pushing
	him to go higher or to accept the position the boy is in, his father places him on one of those imaginary animals with a spring under them so he can just
	move back and forth, close to the ground.

		Crossing the street, he sees people near him go to the end of the sidewalk in order to cross and then go south to reach the place Arch had already
	left a few minutes ago. Two houses from the spot is his home and now he's inside, wondering about his new view. The walk had been boring, the people boring,
	his awaking, boring. He turns on the tv in hopes of plunging himself to danger, again but all he's shwon is a warrant for his arrset. Looking out his windows
	with the curtains parted, he sees people staring from the distance, startled when his eyes confront them; the people pointing, calling the police, keeping 
	kids away from his home. Thinking he shouldn't have came here or left twenty minutes ago, he goes out the backyard, jumps a few fences until he is on the 
	street.

		Lucklily the Gods are in favor of him, making night come faster than he expected. With the advantage, he diverts from the standard route and goes on
	the dirt path. By himself, he ponders the life he is to end up with for as long as he continues to live. Pacify, null, quarantine, diasrm, sedate. He shrugs
	his shoulders, thinking that he already signed  his own death warrant. "Guns blazing seems like a good way to die, very violent."

		Then he thought about it, if he was to die, it would have to be by a formidable opponetnt, not a suicide request. Arch kicks a few rocks down the path,
	head down, thinking. "I'm not going to wait for him, her, whoever to show herself. I'm going to find it and fight until I become nothing. The greens start
	covering most of the path he's walking, whispering to his ears. "He is ready at the sea, to test your strength and valour. Go, this land holds nothing worth
	meaning for you. I should go, nothing here."

		On the ship, Arch stands in the front, in the rain, looking ahead. Waves ebb harder, knocking things over except him. There are times when the waves
	come aboard and knock him down and try to throw him to the sea. Hanging on the side, he pulls himself up and stands upright in front of the ship. Beams
	of light flash in this dark storm, waves as big as mountains. As one heads for straight for him, he says, "Lets see if I can stand against your sceptre."
