\author{Huxley Sparks}
\title{Brother}
\notes{ Detached person's brother observations, wants to see where his brother is wandering to}
    I see him on the bench, reading a book as I lean on the post. He sits between two people who are texting their friends
about what happen at the movies or what party they're going to over the weekend. No one would expect much out this lone
outcast that everyone would think he's a mute rather than taciturn. I've seen all the medals, trophies and plagues (honor)
handed to him, laying at the back of his closet. More awards than anyone in the family put together and remains in the
unknown.

    Friends weren't his thing. Going a week without a cellphone for him was normal; he would just use the thing like a 
minimal pda. Of course he knows interact with someone since we were the ones that brought friends to the house. Sometimes
they went to him to tell a secret, ask for his opinion. That's where I things were strange, like an aura of awkwardness
lurked around him and cause anyone who got close enough to deviate from their normal behavior. His answers were logical
and lexical, thrown in the air even when we didn't ask the question yet.

    Looking down the road, I see a concrete dark slab dissolve as it extends further away from us. He could care less if the
bus came or not. He would stay there until he's alarm set off ten minutes later of the bus' arrival. If it rang while
off the bus, Roark would leave the group. As to where he goes, I have no idea where or how he manages to keep working. 
Not a word is said when I go to the factory and I don't bother to bring it up since the silence manifest quickly in the
conversation. I wouldn't be surprised if he's quit for a month now, he could always money better than anyone. There
is something minimal and tranquil in his gait and clothes.

    Immune to the obsession of trying to be perfect. After a certain amount of time with the use of reflection and
logic, he says with to himself, "I'm done." Rarely do I hear those words from a person who is working on a skill. People
will thinking they are improving over the years, that experience decreases their chance of mistakes but it doesn't.
Mistakes still happen, years just makes a person more comfortable. 

    Thinking him as a brother, he never had innate skills that made him special; we were both almost identical in
everything except age. Despite the space, I still followed his footsteps until he lost me in the fog. I tried looking
for him, calling his name but his curiousity lead him astray and I was too afraid of leaving certainty. As I got more
popular, the faster his mind would develop. Things that kids struggled like math was a matter of a quick glance and
a swype of his pen. 

    That was another thing about him, he despised using pencils. If he could, he would have used pens during those test
with bubbles on them. He always did hate those questions, answering when asked why, "it only tests how well you read
and how you manage your time." He failed those test because he filled the paper in pens but all the kids knew he got
all the questions right. An F was put on the test, never on his records.

    When you see his work, especially math, there would be so much scratched out work. Several hypothesis materialize
in ink and are eliminated as an answer with a slash. The first session against his homework would be fast and cruel,
I've never seen work done that fast. In the morning, he would go meditate on each error and revise several times his
finished work.
