\title{Green Grass}
\author{Huxley Spark}
\begin{Outline}
        Previous bliss | talking to friend about their trip as they sail back home | gender only when attracted | Alex and Quinn
        Trip in forest | acid implicated | hectic nature | serene sea
        Quinn - jester
        Alex  - persistant
\end{Outline}
\begin{Document}
            Leaning over with his back on the railing, Quinn's head is upside down and looking ahead. Besides him, Alex directs his eyes towards his friend
        that appears to be covered in black and red vertical stripes originating from the collar to his pants if clothes could match his chaotic behavior. Quinn
        laughs as Alex smiles, shaking his head at the thought that passes in his friend's head. "You know you're going to fall in right?" "I assume if I'm that
        careless, you'll catch me." Alex's foot is placed by Quinn's only anchor to the ship and he kicks it up. Quinn laughs even louder as he declines to the
        sea but at that very moment, Alex grabs his foot to keep Quinn's back in the same place on the railing. Throwing his body up, Quinn glues his feet back
        to the floor, putting his hands on his hips as he directs a grin to Alex. Alex just rolls his eyes after Quinn kicks her leg.

            "Lets move to the shade," Alex says, already moving closer to the door. Quinn leans on the wall besides Alex who stands erect, arms hanging loose. 
        Without looking to Quinn, "What do you think is going to happen to the forest?" His face looks similar as if he were to look meaning within a passage, that
        the words used and arranged are done with a specific purpose in mind. Palms up and elbows down, "I hate to say but its not going to be there any longer.
        The land has already been bought and according to the new owners, malls would bring more visitors." Alex kicks the pole in front of her, she squints after.

            "What's more valuable, to live a more efficient life or life?" Alex hesitated to answer, knowing Quinn, she had to let the question simmer in her
        head before saying something. Anyone else would say the more efficient life since its better than the status quo but are those two what he is considering?

            Quinn then goes on with one of those soliloquy about the day, as if reciting what the muses want him to say. "Just two people walking on that island
        on that morning. Abandoned by the locals for a couple of weeks now and already seen as an obstacle for the inevitable future. Wood used for destroying
        wood and changing the ground to a tombstone of the land once there. It is best not to talk about the dying part since it is when something becomes brittle
        and undone."

            "A place that Artemis would command people to build her temple; children could run around, dodging trees and creating new adventures. We took it slow
        in comparison to them, our attention less wandering but more analytical. Asking questions with a foundation that we agree on, to see where the ground would
        crack. Our intention isn't mere destruction but the pursuit of child-like curiousity. All the filters, the veil over our eyes, has now been lifted as
        we thread the virgin ground that its innocents is neglected."

            Alex held Quinn hand as he continued, "We have to watch our Atlantis sink to the depths of the oceans while the corpse is mutilated by its neighbors.
        We are but a grain of sand in comparison to the numbers to advocate the new change of the island." With his head down, "I hate the inevitable." She
        feels Quinn put his hand into a fist, slamming his free hand into the wall. Alex brings him closer and her warmth soothes his anger, pacifies his
        hands.

           Leaning on her, eyes still looking beyond the railing; "To have played follow the leader with a rabbit. Running after it for about half an hour and
        never did once try to jump in a hole. I remember it stopping to look back before jumping back to motion with the thought that we would always stay behind.
        Its vanity is how I flanked his right and he fell into my hands. I swear the rabbit was laughing when I held him by ears, you saw it."

            "I didn't see the rabbit laughing but I found it kind of weird that he was comfortable while being held up by us." "I know, right. It wasn't scared
        of us. It was only obvious that we were going to let him go and when it did, it stood there like a minute or so looking at us, waiting to see if were
        going to play again. When we started walking further into the forest, the rabbit got the message and jumped away quietly and with light feet. It stayed
        the path we used, looking back us a few times, ready to continue the game we had played."

            "Our second entertainment was the wind that became music for us. Using leaves as mini snares, an animal's screech as a riff and tumbling rocks as the
        base; the beat was a serene trance. Crisp sound without electricity or speakers, enough room to dance around; that's when I grab your hand, lifted it
        to the sky and decided to make our feet jump to the rhythm. My body had leaned towards yours, yours to mine, we both went different directions with
        our hands holding us together and then it became this invisible bond that existed between us as our bodies became the manifest of flow dancing next to
        another."

            Feet is what Quinn looks at, come from crossed legs, his shoulders trying to meet in front of his chest, under his forehead. Her hand slips up to
        his neck; she remembers the chase along the trees. She had forgotten the years he spent in track since she but a few fingers shy from grabbing his shirt.
        Her heart was definitely beating faster than his; he taking the time to notice the water beyond the shore. Turning over his shoulder, seeing the nymph
        deadly grin, he turns to her with open arms. Her arms go up, limbs overwhelmed with the surprise.

            She slides down using his body as a sleigh, screaming from ecstasy. Then his knee rising up, she falls over and their bodies race to the floor. Facing
        the sky that leaves float around like clouds, hears the water's waves. The motion of approaching and receding, a rhythm natural to the sea, done on
        a soft sand. Some of the sand gets displaced as the water continues the beat, movements in a trance. Sometimes it reaches to the dirt and sometimes it
        barely touches the shore. Near the end, the ocean tends to linger longer on the sand, as if never wanting to separate. Some water stays behind before
        the last wave comes.

            After a splash, Alex is on the ground; catching her breath, her hair undone. As for Quinn, he wanders around the forest while trying to keep his pants from slipping.
        Securing it to his waist, he puts his hand on a redwood. His second time being here is now without his father. He remembers his dad showing him around
        the area, letting him run around where he desire; knew that he would be alright in the end. Even when his dad didn't hear anything from him for an hour,
        Quinn saw from a bush that his dad was treading along with his head wandering around the forest. Then his dad disappeared and that's when he started
        feeling scared. Thoughts went in his head of his dad leaving or probably he got hurt. That's when his dad jumped on him from behind and lifted the son
        that went from fear to alacrity after being lifted into the air. Both were happy here but Quinn's dad is no longer near.

            When a hand touches his shoulder, he point to the origin as if skipped the transition between here and there. His excited smile diminishes to a lips
        with the sides curled up, cheeks down. Seeing her almost start to reflect the same feeling to him, he grabs her by the waist, brings her close and 
        whispers to her ears, "Can you believe that you actually surprised me?" Looking up to him, "What's wrong?" He kisses her on the lips, putting her back
        on the redwood.

            Laying on the bench of the ship, she sleeps with her head resting on his chest, holding on to his shirt as it were a blanket. Wrapping his arms around
        her, thoughts in his head pop repeatedly. That the playground he used to play on will now become a cementary; he kept away infintely from his previous
        self. He is a person that has to accept this change, in spite of how much kicking he might do. He can't let her know how much this affects him, she
        would fall deeper than him if she knew the truth. He has to walk away, happy for the fact that he at least got a taste. "But why do good things always
        come to an end?" Then he looked at her, thinking if this is real, an end is approaching.
\end{Document}
