\title{Homecoming}
\author{Huxley Spark}
\begin{Outline}
        Visiting the remains of a burnt town, zombies,, public outrage. Zombies are in past | empty bullet chamber, panting, fresh blood, ghosts, worried about
    footsteps behind
    Parts: old home, foot step towards it, flashback, original route pulls / school / bank / playground
    Person: Business suit / gas mask | incomplete, reflects himself, | desolation | Kid looking
    Dead friend is the end of him / he should have got out | optimist
\end{Outline}
\begin{Document}
        A polished black (pointed suit heel shoe) oxford strikes the crumbled cement that plants tear apart to only meet with a sky that denies them a naked
    sun. Knee lifted to pass the jagged burst of earth; the pinstripe 3-piece suit continues his journey now on the center of the street. Cars that hit the
    curb too hard are left with the doors open, interior deteriorating, a few cars flip upside-down, some crashed into fences or walls. Scavenged for anything
    in the car that can produce heat, cars are left as the only corpses that don't rise again. Walking by this outside morgue of cars  (outside mall), he
    readjust his gas mask as he keeps his eyes on the sight in front of him.

        A circular disk that purifies the dead air that wanders the area is connected to the left side of the mask. Eyes hidden behind an opaque one way glass
    frame that extended from one side to another made him forget that he had a face. Despite being here before, everything seemed new and so distant from him.
    Coming here to see the sinking of the ship that he was able to transfer to another after being struck by a glacier  As he saw from the other ship, all the
    people trying to take all that they could from the ship without realizing that the lifeboats could suffice with human capacity. Few escape while the majority
    fell to the swarm, the sun being denied to them hence. He drops a few lifesavers, first-aid and blankets to improve the survivors chance of moving on yet
    he remembers to stay his distance as a orbiting arbiter.

        Bring back his hand from his extended arm, he grabs the revolver while keeping away from the hot tip, popping out the cylinder and finding two empty
    chambers. Putting back the gun on his holister, underneath his jacket; kicking the body that he corrects back into the right state, hating the fact that he
    miss the target on the first try. Coming with no backpacks, bags, suitcases or backup, the gun and knife as his tools at hand. The two shots being a vex,
    attracting the feet draggers. A persistence silence provides him solace in this gray day.

       Paint falls from the iron rods that are meant to prevent them from getting through, rust as infectious spores. Walking with hands in the suit's pockets, the]
    glass frame being below the filter and shoulders squeezed together, shaking a little. Stopping in front a two story house with a gate that consist of cement
    columns and iron gates in between, one foot facing the house while the other still parallel to the sidewalk. His sight first focuses on the surrounding area,
    looking for anything moving when wind isn't present. A can from inside an anonymous house falls, probably from a shelf that held on too long and finally
    gave in to the weight. He puts his sight to the sounds direction and waits a little, expecting to see another ghost in human skin. Gun in his hand, he closes
    his eyes and tries to hear footsteps within his radius.

       In the living room, he sees the sunlight enter through the vertical blinds as they set their shadows on the white squared-tiled floor. Sitting down with his
    back reclining on the seat and him reading a book in his hands  With the cars all away, he could hear the trees wave in the air. Reaching down besides him,
    he gets a glass of water and takes a drink, his sustainance that removes most of the excess. After breakfast, he's been reading for at least 5 hours with
    that cold water to prevent his stomach from growling. Extending his legs, he takes a deep breath and closes his eyes to see a picture of a steamer along
    a nile in Africa.

        At night, everyone is back in the house, restless. Television has nothing watching if there's no cable and the youth find the streets very enticing. 
    Parents start playing a game of dominoes on the table as the other kid takes another shower for his night out. The reader leaves when he the others are
    busy so he doesn't have to witness the same ritual that happens every time his brother goes out. First, the younger one doesn't tell them ahead of time that
    he's going out and then goes ad hominem on them. Parents respond by telling him to go back into his room. He says its not fair, they say he doesn't do anything
    in the house. Then an hour later, they become deaf when asleep; the younger leaving through the back door.

        Surrounded by the tree shadows in an area that distance itself from the city lights, where the landscape is not tailored for retail value. Cold, isolated
    and a hint of desolution from the fallen fences. Hard to read where the night flourishes and leaves stirring, thinking to oneself that one is being watched
    by an animal that wants to consume him. This paranoia sinks its teeth deep into his head and instead of going to the city to take some vicodin, he stays and
    says to himself that it's fine, breathing in and out, acknowledging the fact that his mind has been shaped to where it associates the absences of familiarity
    as hostility. A routine yelling is more soothing than a silence in the woods that isn't pregnated with the engines of cars from the freeway close to the
    forest. A path without any cement nor signs point to others where to go.

        He leans closer to his house before lifting his foot and returning it to his regular route. Eyes lifted to the gray wall at then end of the path and 
    already seeing the gate perpendicular to the wall as a way to climb up. To go back and round would leave him vulnerable, its probably best to climb over
    then, he tells himself as his head nods and then settles. Walking to it, he fills the empty chambers with bullets and then snaps the cylinder back in place,
    letting the tip wander follow what his eye sees. He then puts it away as he approaches the wall and looks up, barbed wire.

        Hands hanging from the top of the top allow a head and elbows manifest before his whole body settles away from the ground. Below, other hands extend to
    the sky, scrapping the wall that they all forgot how to climb. A challenge that needed a little thinking now impossible to those that follow him. As he points
    his gun to their heads, he decides to put it back to the holister and close his coat, making the revolver disappear. Looking pass the wall, he checks the
    path for any others dragging their feet in the grave of abandoned homes and buildings, light post on the ground, cars crashed into walls and even to each
    other.

        His feet touch the ground, a drop from the top, right shoulder drives to the left side of his pelvis and rolls a little on the concrete. Coming out of the
    roll in a jog, he slows down to keep his ears and eyes alert for anything that might have been waiting for him to get off the wall. He takes out his gun,
    points it to the ground on the side of him and scans the perimeter with the intention of killing. The gun points to the car with a human corpse inside and then
    it sways to the house with the broken doors and windows, the door still swinging at random times. Noise is the enemy here and every time it makes itself 
    visible, Damian must greet it with an assassin's concern. If he gets himself in a jam, there is not restart button to press.

        Another three shots are fired and the decaying humans return to being a statue of the curb, fence and seat of a car. Keeping his gun at hand, he starts
    jogging away from the area. If he didn't come here for his home, what is his purpose being here, kamikazi style? The only other building that would have
    any meaning to him is close and built like a prison.  His presence in the area will soon be public knowledge and he should start thinking about leaving soon,
    hopefully his mind will convince his body that its a good idea. Passing yards of dead grass, baseball bats, 2 by 4's, and knives laying on the ground with
    old red stains on them, he closes his eyes and turns away to the thought of what had really happened here. "They wouldn't listen so how could I help."

       A strip of concrete street that disappears in the horizon, plants with their tops tilting down, (starving girl) trees standing by themsevles, wallowing
    about losing their beauty and friends. The ground had already claimed back some of its land by swallowing the sidewalk and now is trying to consume the street.
    The whole street being covered in dust, dirt covering the gray to beyond recognition; the street having the texture now that is similar to dessert ground. 
    After every step, another crack presents itself and the level it varies from the previous is random.

        A fog sets in and by reflex, he puts his hand on the revolver. The eyes that sprout from the earth and hang in the sky no longer shine but stare at him
    like an angry god. Walking underneath is a game of chance, their foundation in question as well where they choose to fall. After passing three, he hears
    the first one give up and slam onto floor, dust lifting into the air and a deep bass to scatter within the area. Damian jumps a little as he turns back,
    expecting the worst to be running behind him but when he finds the shattered eye, his breathing becomes easier. The serenity he had carried is gone as he
    keeps the revolver in his hand at all times.

       Blue metal bars extend to at least twice his height with space that he could almost slide through if it weren't for his head that got in the way. Fences
    planted enthusiacally everywhere in the school, Damian shoots the lock of the main gate and walks inside. Continuing walking between two parallel fences, his
    eyes gander at the collisum that decays, next to the baseball field. Boards piled on vertically on the fences, rifles mounted on the top of the bleachers
    and tents on the football field. His eyes sway away for a moment, trying to prevent himself from imaginating what had happened here. When he returns his sight
    back to the place, a sun shines on fresh cut grass and a cranberry running track that surrounds the field. Four lines that go all the way around, numbered and
    practicing taking place. 

        A few rest by the football post while four people stand on the race track start line. The third is who they turn their heads to while he takes time to 
    address each, watching the eyes to his left and then to his right, staying longer with the friend he likes. (girl, platonic) When the coach tells them to get
    ready, those four get into their stance; balls of feet on the ground, back parallel to the ground, tips of hands holding the body up and neck stretched up. 
    "Go!" He is second to last on the first lap and she is in front of them all. On the third lap, he holds in his pain and pushes further than his body wants
    to, hard for his eyes to remain open when he squints with the urge to throw up.

        Fourth lap, he's in first yet the ship is bursting in its hulls. The captain says that's good enough, that the ship can slow down to finish or stop if it
    wants to. "Listen to what we're telling you." As he crosses the line, the air that opens his mouth wide doesn't exit and he falls to the ground, body stiff
    and all limbs squeezed together. "We'll you finished, now get up." He can hear her footsteps, how much faster they became after he crossed the line. "Damian,"
    she screams, the word being broken when she screams again. As he tries to extend his limbs, it feels like he's is bound by an invisible rope. "I'll be fine
    if I can just get myself up." 

        Its the sadness he hears in her last cry before crossing the line that he gains control of his legs, places his feet under him and propels the rest up
    into the air, breaking the last binds on his chest. Another bind falls on him, her arms and his legs maneuver to the grass where he lets himself finally rest,
    she in his arms and vice versa. Less than a minute later, the rest finally finish the mile and bring water to the firsts runners. Damian grabs the bottle, 
    twists the caps and lets the water pour into his open mouth; water splashing over his whole face.

        Standing on the track, black dress shoes and all, including the mask; he kicks a few rocks off the track. The numbers have faded, the 5 now looks like an 
    'l' next to 'n.' The people on the ground are in a state beyond lethargy in which they can't rise naturally again. As he looks at the bodies, he hopes that
    his eyes don't find something that he recognizes; he holds his gun so tight that it feels like the gun is an extension of him. Walking through the decayed
    city of fabric, his head swings left to right and back again to find the truth, to stop the second guesses and finally have a certain answer. What it means
    to him is that he has lost his immunity ever since he touched the ground here and is in search of something else.

        Walking in the corridors, he thinks about the classes. Doors that locked from the inside, rooms that had proper ventillation; people could have survived.
    Lifting his head up, he encounters a blue metal door left ajar with a body rotting in between the room and the door. He stops for a moment and thinks to 
    himself that she wouldn't make this mistake, she would know that the familiar face that scratched the door was just an empty shell that focuses on the first
    essential need. With his head still turned over his shoulder, he approaches the door and peeks inside.

        Blood and black smoke stain the white walls and the many sinks in the room. Broken glass on the floor but no bodies to be found. Breathing becomes 
    naturally instead of the hold to a point of failure and then release. Glass crunches under his boot as he steps inside, trying to find the specific details
    of what had happened here besides the end of use. Blinking several times after finding a piece of paper, he picks it up and begins to read.

        "Day 27, we had run out of food and the hoard has a sense that we're trapped. No guns and the only weapons we have is anything we can make from this lab.
    For us to live, we have to make an assault on the dead frontier that lays in front of the door. The mob is thick and people here are losing their hopes as
    fast as their patience. I already gave them the specifics about the situation and most are ready for the suicide flight. Supposely a teacher, less than 
    400 meters away from here, keeps a fridge of food at all times so we're going to try our luck there...I want this nightmare to end already. I miss being
    able to run outside on my own accord rather for survival."

        The paper seems to be wrinkled in the middle, as if the bottom had shoved to the middle where the hands layed.  Straightening as much as he can, he folds
    it into a small square and puts it in his breast pocket, patting it to make sure it still there. He pops out the cylinder, "all bullets are there," and snaps
    it back in place as he steps outside, hearing footsteps somewhere in the fog. His intuition tells him to go right despite not having an idea of what teacher
    she is talking about. Walking en route to the other side of the school, he tries to think about how recently the journal entry has been written. The blood in
    the room had dried and the ink held a intense black as he read it, maybe not so long ago.

        With no school blocking his view of the sky above his head, all buildings away from him as he stands in a 5 meter radius with only a flat cement in his
    circle does he notices the desolution of his condition. It would have been best to have came here with backups but no one wanted to go and rarely did that
    stop him from deviating from the rest. The risk has to be taken, he thinks to himself, I have absurd needs that I have to satisfy. Taking a deep breath in,
    he sees a body standing by the fence, walking repeatedly into the wall. Damian just looks away and returns to his expedition.

        179, his hand feels the warmth of the vertical door handle where a door knob would be. It opens. What he finds first is the black void and reaches inside
    to turn on the lights. When light shoves the darkness away, he finds death hanging on the floor, walls and even on the ceiling. Golden hair on the floor,
    he falls to the floor. He keeps thinking to himself it can't be her, she much better than this, she was his shooting star that he couldn't catch up to, that
    no one else could either. Closing his eyes tightly as he held the strand of hair in his hand, he saw himself running past her during a race. Now he saw himself
    as having gotten away, the only person who could. Everyone behind him had fallen and it was only up to this point that he decided to look back at what had
    really happen and taken off the veil of obsession.

        With his mouth open, he had attracted the attention to the room, 179. Bent besides the body, refusing to accept the hair as golden, that she had died it
    a different color because she was smart; he kept the ambiguity on the body. He had taken off his mask, feeling that he couldn't breathe in the thing and
    now exposed to the environment, his first breath is a grasp of air after almost becoming unconscious from being underwater. His chest expands like his heart
    wants to escape, his shoulders moving in counterclockwise circles at a time, his chin tucked and his hand as a veil for the body. When he hears footsteps at 
    the door, his right hand goes up, pulls the trigger and another body is on the floor. The child that is his conscious tugs on his shirt, telling him that
    there isn't another exit besides that door, that they have to get out now.

        He pulls the gun back to him, takes some bullets out and refills the revolver without having to look at it, knowing where everything is and that 
    everything will fall into place. Another body barely walks in before the revolver decides to have it drop to the floor. He lets the revolver take charge as
    the child watches the deterioration of the suit, the mask left behind and that time is short now. He fades away like the shadows of the room and the suit
    is now outside, the halls flooded with rags that are considered clothes. Surrounded, he keeps the radius between him and the rest constant, shooting instantly
    when anyone crosses the imaginary circle. 

        He shoots three within a second and their bodies becomes an obstruction for the others that are trying to get closer. His only plan is to run out of 
    bullets but maybe if he's lucky, he'll make a wall that will prevent the advance. He turns his back away from the rest as he looks at the wall that he
    top is farther than his jump. His hand swings back around and shoots two, one at 11 and the other at 2. Looking at the top, he sees the golden sun reach
    for him.

        Like a child jumping for his teddy bear that is being held above him, he jumps repeatedly to no success. He can feel the cold death swarm making his
    circle smaller, their scent overwhelming at this point. He throws up a little in his mouth when he comes to accept that he's stuck here. He pulls out another
    revolver from his suit and pays attention to the closest footstep near him. Bang, Bang; bodies of meat slam to the floor. Air drops out of the swarms'
    hanging jaw; they climb over the inactive soldiers. 

        One revolver is popped open while he keeps the others at bay as he reloads. He puts the empty revolver in his pocket that has bullets, lets his hand 
    work and pulls out a properly loaded gun. "Shut up, shut up, shut up," he yells; shooting the front until both revolvers were empty. Right after that, he
    just ran up to the closest body and started punching him in the face. He punches another face, moving deeper into the concentration. Punch, elbow, kick; all
    of them to their faces. With each assault, space is made to go further. 

        As he moves closer to the door, he sees one of them moan as their head falls back. Damian's eyes dilate and he jumps on the bastard. Both are the floor
    but he sits up right as he punches its face. With each punch, he expects to hit the concrete. Bones crack as he punches harder but at this point, he already
    absorbed in his fury to be disturbed by anything else. A decaying tentacle wraps around his left arm, pulling it away. Switching his attention, he pulls
    it away from their dead, grabs the revolvers and starts smashing their faces. He fractures one of their noses, knocks one down, breaks a skull and shoots
    his final bullet into their chest. 

        A wave of rags covers his right arm that causes him to fall to the ground. Rolling under his arm, he pushes most of them off him. The sky disappears from
    his sight, the sun no longer visible. His anger still boils but his body has been taken too far. All his talent switched in for an invalid retribution. Their
    genocide would never bring back a smile to her face and at that point, he takes a deep breath in and holds in, receding from his assault. No escape now yet
    that's not what he wanted. He can feel the swarm slither on his legs and arms, putting a weight that it feels like it connected to the ground. "I miss you,"
    he lets out in a whisper, finally putting his head down so he can rest.
\end{Document}
