\title{Never there}
\author{Huxley Sparks}
\begin{Outline}
        How people are apt to make life interesting while disconnected | Two workers who been at a factory notice the temporary worker's span
            Jack : there just to get the money; asleep
            Henry : stern supervisor / mess up name, tries to warm up to him / smokes
            Ellis : worker / nervous about being contested against
        Three days of work before notice him / cookies / need him to help with packaging | 2 days (82)
\end{Outline}
\begin{Document}
        Hands pounce on two places on the convey belt while leaving behind a product that is to be sealed, shipped and consumed. Ellis is going faster than before
    ever since Henry decided to join since Martha had to go the bathroom. Henry offers a smile that is unable to soothe the discomfort in Ellis; giving his
    supervisor only a smile of discern. When his hands touch only the metal behind him, he hears another tray slams on top of the previous one. No time to
    look back, Ellis thinks to himself, Henry has to think that I'm always doing my job. Ellis doubles up, grabbing two cookies in each hand and making a second
    pounce immediately after the first one. He keeps doing this until the cookies on the conveyor belt stay in place and Henry is gone.

        Ellis shoulders hang down from fatigue clinging onto his back. During this lucky (inevitable) repose, Ellis slows his heart beat back to normal; which
    almost happens if Henry didn't say something and point a finger at him. Shaking back into worker status, lifting his head back on top of his shoulders,
    he hastily looks for something to do. He reaches for the metal besides him but finds only the table that held the trays. Looking behind him, whatever was
    behind him was gone, leaving only a wall to accompany him. Turning back, he sees Henry gone from the machine and lets his eyes search the perimeter for
    the provider of his purpose to speak to him.

        By the freezer, he sees Henry pointing repeatedly to the carts and a place beyond the conveyor belt with a mouth exerting its maximum range as someone 
    stands in front of him. "Who is that guy?" What stands awkward about the worker is that he doesn't have any gloves. Ellis tries to remember all the guys
    in the kitchen since rarely does he see them. It could be one of them, dressed differently today. As he kept looking, he saw that the anonymous worker had
    arm with no tattoos. This attribute stood out to him since he clears remembers that most guys in the factory had tattoos, on their arms, especially everyone
    who worked in the kitchen. He would have kept trying to figure out who this guy was until he heard the conveyor belt start again and he shifted back into
    efficient unconsciousness.

        Standing before the time puncher that used a number input with a hand recognizer, he already had his mind set on his leftover pizza. Standing outside of
    the line, leaning on the wall stood no name, eating his food. Ellis thought that he was weird, why would anyone want to eat besides the clock when they're
    allowed to eat outside the building or the cafeteria? This is when he started to think that this new guy probably stole large batches of food and was just
    waiting for everyone to leave before committing the deed. On his part, Ellis didn't have to do anything. The workplace had cameras everywhere so if the
    temp decide to steal, he would be gone before lunch.

        Through the kitchen's door window, he sees the temp walk by. Ellis kept wondering how the hell the temp managed to steal food without being caught. "That
    bastard," he says in a low voice. Worried that he might be blamed for the missing food, he jumps out of his seat and searches for Henry. Opening the door
    that leads outside, he finds Henry leaning on the adjacent wall, smoking. Having found Henry, he must have lost the words he was going to say getting there.
    A smoke exits Henry and ask Ellis what is it this time. "Well, its ... its about the temp worker that you, i mean, that started working here today. He's
    stealing from us." Henry puts his cigarette down and asks if that's so. "It is, it is. I saw him, he walked by the door." Henry lifts an eyebrow up, "So
    you're assuming he's stealing from us because you saw him walk by a door?"

        "No, no, its not that." Then Ellis thought he had cried wolf for the last time. "He did steal, he was waiting for everyone to leave the workplace before
    making his move. Just check the video cameras and you'll see." "Fine, we'll watch the videos after work. If you're right, I'll have him arrested after he
    puts more unpaid hours here." Ellis' head sank into his shoulder as his face was in bliss; another bullet dodge that would have cost him his job. Now he
    could put this behind him and let his hands do the work.

       Like a statue that stares to anyone in their sight, Ellis saw the temp at work. Or, just standing at work. He couldn't believe that the temp was doing
    nothing and wondered if Henry was watching. Then he sees the temp become animated, disappearing into the freezer and before the door could close, bringing
    two carts that are taller than him out to the conveyor belt. With the trays lifted that were near Ellis, the empty carts are pulled one by one and are
    stacked horizontally. A few seconds later, the area becomes empty and the temp returns to a stoic stance. All Ellis was waiting for is the temp to rub
    his nose repeatedly, snort a large amount of air.

       The temp activates several times for each hour that passes by, remaining in his thoughts until the very last second and then dedicates his whole facility
    towards the tasks he was assigned to. Always finishing at the same time, 55 seconds. To look at something else is for Ellis a conscious effort of not staring
    into the face of the temp worker. With the speed he does the work, would he be capable of a more heinous act? All Ellis wants now is to leave but when he
    looks at the clock, there's still three hours left. Returning his eyes to the spot, the temp is MIA.

        A loud clash sounds from behind him and when he checks what it is, he finds the temp right next to him. He turns away quickly back to the conveyor belt,
    back to the world of hands and cookies. The speed he used to do the cookies is gone, his hand hitting the metal a few times until he checks where the cookie
    is. Sweat forms on the back of his shirt as he swipes away some that were on his forehead. Heart beats faster without his legs having to move, nothing of
    his body exerting more force than its used to. When Henry passes by, he asks Ellis if he's okay. "Ye .. Yesss ... yes, sir ... I am." Henry walks away while
    keeping Ellis in his peripheral sight.

        "Aphrodite, the polar opposite of Artemis. Where Artemis represents children, specifically boys, and virgins; Aphrodite is sex. Being known as the lover
    of smiles which is an eupheism for genitals. The worst Artemis has done is cause Agamemnon to kill his daughter to have the wind favor his army. As for
    Aphrodite, she brings destruction for those that don't recognize her. Hippolytus gave tiime to Artemis but not Aphrodite and for that, she caused her stepmom
    to fall in love with her. From that, the stepmom hangs herself while leaving a note saying that Hippolytus was seducing her. After reading this, his
    father had lost all trust in son. Forcing his son into exile without reconsidering his hasty judgement, he also prays for the death of him. His wish happens
    as Hippolytus is en route out of the city until a mishap happens with the chariot, causing him to be dragged to death by jagged rocks. When the father finds
    out about his death, he also finds out that this was the vile scheme of Aphrodite. Everyone of left scared of the deity that is a deity among the gods."

        Ellis sees the temps head snap back from a daze and burst into action. This time the temp runs and finishes the whole procedure in 30 seconds flat. Its
    like he cut all the excess to his work to the bare minimum for the cycle to keep going. Of course Henry was aggrevated about the temp just standing there
    for the rest of the time but he had told him that was all he had to do. To go back and say something more would make him seem inferior. The only way he was
    going to get back at the temp was in the cycle. One mistake and he could get him fired, make him seem like the fool. Henry tried to keep the temp within his
    sight as much as possible but his duties required him to stay on the move. But then again, Henry would pop his head out from the kitchen or from the office
    exactly when the temp had one minute to finish the task.

        At 5, Ellis meets Henry at the security room. Inside, Henry is looking at a screen that shows the temp going to his car. When he closes the car door,
    the turns on and leaves the lot without hesitation. "You might be right, Ellis. I've never seen anyone leave work that fast before. Well, lets check the
    videos." He sits down while Henry rewinds the tape back to lunch. Ellis breathing was now calm and the day seemed more brighter despite still being in a
    building without windows. As he watched the tape rewind, both noticed that it looked like the temp did nothing at all. Confused, he slowed the speed down
    and saw a blur move inside the factory whenever the temp disappeared. For some reason, Ellis had a feeling that the temp was standing behind him, knowing
    everything that was going through his head. Ellis' back arches inwards on its own accord.

        "The myth goes that the people of Phaeda, known for their association with Poseidon and giving rides to strangers, will soon meet destruction after
    arriving back from helping a stranger. This is what Odysseus thought would happen since Troy, the talk of blasphemy he committed and Poseidon heard. The
    sea has been cruel to him and to whoever was with him. His desire to go home was greater than being cautious of other people's safety. That is why he decide
    to omit the fact that Poseidon had a vehement attitude towards him. When they left him on the shore of Ithaca, asleep with his treasure beside him; the ship
    sinks before the harbor of its native land."

                                  ^watching the temp stand besides the line.
        "Slow it down," says Ellis. Henry looks at Ellis when he says, "Maybe you should take the day off tomorrow, you're starting to see things that aren't
    there." "He was like that during work, who says the phantom isn't as mysterious during break." Rolling his eyes, he lets the video play at normal speed at
    the beginning of lunch. On the side of the line, the temp stands there looking to his left but what they find weird is that he's looking above the kitchen.
    "The air vents, he's looking at the air vents. That's how he took the food out without being noticed." The more Henry heard Ellis talk today, the more
    enchanted his story became about the temp. He lets the video play until they see the temp punch out and head directly to his car to eat.

        "Check the other cameras. This one has blind spots, yea, that's it, blind spots. This sinister clever robber is trying to make a fool out of us." As Ellis
    talked, he noticed Henry's eyes come into focus, pupils dilate. "He's trying to make you look stupid." That's when Henry turned around and went through the
    videos of the other cameras, forgetting about Ellis presence, studying the film carefully for a change of color on objects. Playing it in slow speed to give
    the temp no chance to pass him, Henry was ready to throw him out. From behind, Ellis continued to watch the empty space on the screen that held Henry's 
    attention, wondering if he went a little too far by making the vicious Henry develop a taste for the temp. Ellis to the side of his foot and covers his head
    with his hand and elbow.

        For a few seconds, Ellis remains buoyant in the air as Henry slams his fist on the table, emitting a low grunt. A hard landing back to the seat returns
    his sight to the empty screen. "He thinks he can laugh at me without being persecuted," Henry at this time then takes a cigarette, lights it and takes a
    puff before returning to his soliloquy, "no one in this factory is better than me. I control the production line. Taking a day off means a day of low
    production." Facing Ellis, "people like you only know how to do one thing and in your case, put cookies in the conveyor belt. As for the temp, I think his
    name is Jack or Joey, I forget but I like how temp sounds on him. Temporary." He laughs, lifting his chin to the ceiling and letting a haughty roar out.

       Another day on the job and Ellis sees what he assumes is Joey standing, listening to the demands the supervisor is ordering out of him. Henry's mouth seems
    to run forever in time while during that time, he sees the temp glance at him. "Oh shit, he knows. He knows and he's going to kill me." Taking deep breaths 
    as he's released from the temp's glance, he soothes himself by saying that the temp wouldn't kill, not for something that small. Really? Ellis lets out
    a chuckle that cracks.

        "Prometheus, titan? Mortal. As the gods monitored the humans; humans had to work extensively for their work. All their time consumed by trying to satisfy
    their stomachs. Man was doomed to destruction like the previous versions unless something different happened. This is where Prometheus steps in, by bestowing
    humans fire, in addition, math, science and writing, they were saved from their awful fate. Work became compressed into a few hours with the tool giving
    to the humans. Hmm, I wonder what time is it." 

        Lunch again and Ellis finds him at the spot besides the line, eating his food while the queue moved. At 12:03, Ellis was exactly in front of the temp and
    all Ellis could help but think is that the temp is looking at him from underneath the forehead, tightening his grip on his elbow.
\end{Document}
