\title{night time}
\author{Huxley Sparks}
\begin{document}
		From above, the contagious orange beam strikes the floor. Shadows that fall on homes, buildings and streets are diluted by the interrupting orange. A 
	cheap imitation of day that people refuse to accept.
		
		Stripes of black striking (soft) my face as I drive in the night; empty lanes and dark trees. Thre night fills the inside of the car since they made
	it clear that she can no longer linger outside. She wraps her arms over my body, pressing herself closer to me as her head lies on the side of my face. Those
	lucid eyes of hers, light from the moon. As the car stays close to the street with each gentle pull from the turns, we both drift tot the void.

		Sound drumming my ears, feeling the sound vibrations on my body, her warmth, the car's speed; all while being enveloped in the dark; this is how it
	feels to be a shadow. No one around to make me think otherwise. Being alone, the island causes me to glide on the streets, a vex absent from the ride. I then
	feel her warm, smooth hands gently touch my cheeks, from top to bottom; pausing at the chin, as if deciding if it would be better to keep it there or not. She
	lets it continue until her hands are around my neck; then her arms. She presses her moist (barely wet) lips on my cheek, her eyes closed, holding them there
	for a while.
		
		The orange blur replaces the black strip as the outside becomes more darker. Less concrete, more open spaces, the moon more apparent, quiet. She opens
	one eye to see the outside, she smiles. I smile. She presses on me again with more warmth, unable to restrain herself. The pressure is uncomfortable but I bear
	the pain for her, to keep it perfect.

		She then turns the music low, wanting to hear the engine purr to the dark abyss that I'm driving in. A slight touch of evil, I guess it would sound 
	like that since its the anti-presence of life (full, vacant). The further I drive, the younger she feels. This mute girl nymph with eyes ajar, smiles at me 
	from the seat beside me. Her body more fluid; her shoulders lowered, arms hanging besides her, hand leaning on the seat, legs extended. Her one piece dress
	(two straps) flows gently from top to bottom.

		I keep on driving, further into the mountains, farther away from the city. Some bliss styas behind as we get closer. Then I look at my side to remind
	myself, I turn away and smile. My warmth renewed; I return to the wheel with the foot closer to the floor.

		It becomes apparent that people are not expected where I'm driving to while she opens her window. From having tied hair to it flying in the air like
	ribbons, bliss fills her face. Resting her head on the window on top of her arms that do the same, she starts to forget. My head fills with music, a guitar
	strumming slowly with emphasis on the pauses and echos; a long, loud echo. The noise of the wind is too low for our ears.

		Instead of going furhter, the car sets himself on a mountain and climbs up. She wraps her arms under her legs to prevent her from letting herself jump
	around the car. I laugh at how adorable she acts. She blushes, I soothe her by putting my arm over her shoulder, bringing her closer and tell her that I'll
	always make her happy. The excess in her body leaves as she puts all her trust on me.

		Near the top, me and her hold hands, a light hold from mine to hers. Our smiles faint; she anxious to arrive and me focusing on getting her there. Its
	not long now.

		I park the car by the end as both of us get out and continue on foot. the remaining distance becomes steep, making the hike harder for her. Ahead of 
	her, I keep my hold on her to help her go foward. Whenever I feel a slight tug, I turn to see her trying to catch up. Probably I should slow down but I know
	she wouldn't want to waste any time away.

		My alarm goes off. hearing it, she starts to run towards the top. I sprint to the top while bringing her to my speed. The longer in the run, the more
	pain we feel. We both keep our foucs on the top, not the pain.

		In the end, we reach the top. As I recover, she walks closer to the edge. I look at her, the beautiful orange aura of hers and feel the ectasy in me.
	After the moment of bliss, I go back to my car alone.
		
