\title{Obscure Orbs}
\Document{begin}
\begin{Document}
    Descending head first, his whole body upside down, going further and further into the void. Eyes closed, arms wrapped around tightly
the belief he decided to establish. 
    
    Dream foreshadows choice, death by belief | Jack / languid, disappointed with standard

        He sits on the couch, hands cover his face as elbows rest on legs. No light originating from a box that would sedate his mind from
    the life he has to continue until he dies. Wake up, work and sleep. Other people in his life would just be a distraction from the cycle
    he despises. To lose consciousness of body movements for a third of the day for a paycheck that one should be happy with. To fill the
    house with excess to demonstrate to others how well we are doing like them. Always comparing ourselves to someone else and never focusing
    on what we really want that would be easy to extract after close inspection. Theta waves decrease, time runs faster and our thinking strives
    more for the weekend, forgetting chunk we call the Weekdays.

        Being detattached from the world gives a person a genuine perspective on the world. Patterns manifest as the people around him, the constant
    need to change one's weight, making more delicious food, how to celebrate a festival and reminiscing at parties. The only variation is that
    randomness that our memories are anchored into the world and effect how quick file is retrieved.

        More of the life he sees, the more he notices that nothing is certain. Sometimes when speaking, words sound foreign and when he writes them
    down, he wonders why the combination of marks create meaning. Breaking through the superficial foundation was easy and as he hit the concrete,
    he noticed that there were cracks. Math is for him based on accept notions of signs. Why can't a person say that a + b = 2, treating the letters
    as numbers instead of variables holding a value. Nothing in the world that he sees offers him anything to hold on to, not even his thinking 
    because he can't test whether its being influenced or not. It might be his character or someone with an elaborate fashion of implanting ideas.

        Lifting his eyes back to reality, the sun has left him behind with a black phantom covering the sky. Limbs are pulled harder by the couch,
    keeping him hostage. Reclining back, face looking up to the ceiling; his body becomes warm that he starts loosing consciousness of it. A head
    on the edge of the couch falls like the rest of the body as if in a wave of fatigue.

        Descending without having a sense of where up is, his head is ahead of his body. The question that pops in his head is whether he fell
    or jumped. With nothing here, should he be worried about this predicament? No, everything is gone except me. A black void with pain and 
    pleasure left out, meaning gone. No point to live or die so what does one do?

        

    
\end{Document}
