\title{Orphan?}
\author{Huxley Sparks}
\document{begin}

		In the void, I drift from one space to another without knowing where the most of me is concentrated. Unsure from what angle I'm watching this pitch
	black space, I search for anything to have a form. Everything or nothing lies underneath this black silouhette in front of me. Where my eyes fail, my ears
	hear a sound. A pattern that is different to me, provoking a blank canvas in my mind. What to do, what to think? Have I ate?

		Like surfacing from the ocean for air after being held down in the water, horizontally, my chest pops up from the bed while my eyes remain shut. Still
	dark but now I know I can take off the covers, that something will be there when I open them. I wait, trying to retrace my steps to when my consciousness 
	turned offf. Looking before now, the black granite greets me once again, preventing me from going further. All my efforts to reach my memories are weak to
	take off the veil set on my mind. For now, I have to just use what I have and hope that I acquire something to help me see my past.
		
		The only thing I'm sure of is that I'm on a bed, feeling the covers on my body and my head resting on a pillow. I take some air in to stablize my 
	breathing, removing any subtle vex on my mind.	

		To face the unknown, I open my eyes with caution, expecting that me closing them again will save me from any threat that is near. I stipulated too much
	about the danger where I slept, this room. In a short moment, I found myself comfortable with the room, windows with the drapes closed, drawers, clothes on
	the floor and a mirror hanging on the door. Sitting upright on the bed, I become skeptical about the room. "How did I end up here and whose room is this?"
	There were no pictures in the room, just space. Finally getting off the bed, I take another look around, streching my arms up, yawning. As my feet take steps,
	one foot hits the concrete pile of clothes. Caught off gurard, I go closer to the pile and start dissembling it. Clothes thrown everywhere until I reach the
	hard core. The core's name is "The Book of Proofs."

		Easy to lift, comfortable to hold. Opening the book, I flip throught the pages and see pen marks on most of the text, notes written on the margins,
	exercises done and a few sentences written after each chapter. I end up on the contrapositive proof, negating a whole statement so its still true. There were
	a few examples written in pen on the margins. "The number one doesn't exist in the set complementary to the set containing 1 to 10." "Eat before expiration
	date -> Throw away after expiration date." "Keep calm and continue on."

		Having found one book on the floor, I decided to see if there were any more under the piles. The second book being a step away from the first book.
	From logic to fiction, the Harvard's classics, Vol 17 was open, a page folded by the clothes resting on top of it. I move my foot in a swiping motion to see
	if it passes through the piles. After 10, I find the last book, "The Cambridge Guide to Expertise."

		I then return to the bed with all the books on it, wondering what kind of person has them in their room. With nothing coming to mind, I strengthen the
	page from the Harvard's classics and then go through the pages. Fewer pen marks on this book, words and phrases highlighted, endings with interpretations in
	pen and some notes on the margins.

		Still curious, I open the third book and find no pen marks on the text. Turning the pages rapidly, some papers fall out from the book, probably held
	on by the pages and the cover. Putting the book aside, I pick up the paper and see numbers and tables. One of the papers is titled as "Point of Fail." Two
	tables, Subject A, Subject B, with the latter being the controlled group. The measuring activity, running times. Control B had the lower time while A was a
	minute behind. After ten rows, A is almost near B while B also increased in speed. At 13, A passes B while keeping its climb. Eventually both reach their 
	plateaus except when the page nears the end, A breaks it.

		Placing the paper inside the book, an orange cylinder attracts my eye. Questions start popping in my head as I reach for it and when I see that the
	container had no label, my questions increase exponentially. Before I can open the container, I hear a noise come from the kitchen. Shifting my attention, I
	hear that someone is making coffee with it barely brewing. Startled and remembering that this might not be my room, I close the books and leave them on the
	bed, starting to walk out the door.	
