\title{Deviated}
\author{Huxley Sparks}
\document{begin}
\section{1, 10:15}
	
	...Around and around do these solid black figures walk in the air, being sucked to the imaginary vortex in the middle of the room as he sits
	with his back to the wall, letting the show play on. They stay up above the spot, spinning, and then the other figures from the lines start
	to head to the revolving space. More of these small dolls fill the space and start congulating() into a mold that looks familiar but is still
	unknown to him. It becomes less visible that the thing's size, similar to him, is made of those ants, as it moves without any wiggles in
	its form.

		What stands apart from the figure is its eyes, colorful glowing eyes of a woman completely enveloped by a cloak. Those eyes that
	vibrate with radioactive energy with a pattern of pastel colors on a pond, swirling as the gentle breeze convinces it. Blue, pink, green and 
	yellow dance, some colors acting like water and oil while the others combine to lighter colors. His head almost falls off his body as he lets
	those eyes put him in a trance, lost in those eyes. Neither move, him hypnotized and her intentions unknown.

		During this confrontation, a beat starts to appear in the room. A sound of echo and pauses, rythm smooth. He moves back a little, 
	closes his eyes with hands messaging the sides, shaking his head side to side. Looking at her as he has a knee to the ground, smiling, he
	notices her start drifting towards the white wall. He doesn't move towards her, he only adjusts his stance to be upright as he sees the
	female phantom disappear in the wall as if she was a figment of his imagination. Alone in the room again, he opens his eyes.

		A book case stares at him from across the couch, holding the colors that he had seen fall to the ground. The walls are no longer
	white, black contour lines absent from where walls, wall and floor or wall and ceiling join. Everything back to what it is supposed to be as
	he makes his way to the kitchen, setting water to boil. Sitting down in the kitchen table, he opens his notebook and starts to write. A while
	passes when the light above his head is replaced by the sun out his window and his water is ready. Walking silently to the stove, he pours
	hot water into a cup with tea inside. He lets the aroma be his sweet ambrosia, holding the warm cup in his hand, eyes closed and taking the
	first sip. As it goes down his body, rejuvinating him, he turns and puts his back on the wall, eyes on the tea. A faint red with a herb as
	small as pepper, spinning around in the cup.

		Back to his paper, tea by his side and his hand giving support to the lead head that yearns for more sleep, he writes of his new
	experience in the other dimension and how it varies from the other methods.  These methods include meditation and drugs, such as absinthe,
	marijuana, acid and dmt. The binuaral beat he exposed himself to was replicate the effects of the drugs by directly affecting the brain, sort
	of a passive meditation. Look at the clock on top of the window, he exhales as he puts his head further down, having only 2 hours of rest
	before he has meet with his professor. {10:47}

\section{2, blackboard, 590}

		Walking to his school, the buildings become a fancy to Roark. Holding papers and a moleskine in his right hand, he turns to the
	clock tower as it strikes 1, hitting the bell one time. Out of nowhere, a man texting someone else bumps into Roark. "Pay attention where
	you're going," the man says after going through, loud enough so Roark couldn't dismiss it. Looking back, "Uh, okay." Returning back to his
	route towards his classroom, he walks in a concrete path that has tall full buildings in four quardrants, windows perfectly spaced out. 
	What he notices the most is the absence of a fire escape ladder or stairs to the side of these buildings, "safety precautions suck."

		Inside, he stands in front of his professor's office, reading a sign saying "Not in right now, check later." Smirking, he walks
	down the quiet corridor that amplifies his footsteps as he walks to his classroom. Upon opening the door, he finds his professor deep into
	Legrange's formula, a writing notation alien to those uninitiated. The professor walks from one side of the board to another, keeping his
	eyes on his work the whole time, as if he is hoping a muse will point him in the right direction. Making a silent chuckle, Roark goes to his
	desk and places his stuff without making a noise. Comfortable by putting his legs on top of the desk, he closes his eyes as he pays attention
	to the rants of his professor.

		"I must be doing something wrong, either I integrated too many times, not enough, or a did a differention where I wasn't supposed to.
	It doesn't make sense that the maximum for this function is negative. I probably switched the signs somewhere by accident, the question is
	where. Does it matter if I change the end sign? Yes, it does. If I switched the sign someone in my work, then the answer is not even the 
	right number. Damn" he slams his hand on the board, "6 hours today on this and not much progress."

		As the professor looks at the clock close to the ceiling, he notices Roark sleeping on the chair. "Always sleeping when something
	important is being done, aren't you, Roark?" "I guess you wouldn't believe I was thinking really hard with my eyes closed? Anyways, I think
	you should take a break considering you worked on it for six hours straight, it might give you a new perspective to help you decipher your
	work." 

		Walking down the steps, the professor inspects the student: bed hair, glasses with top rim, moleskine, black jacket, blue jeans and
	running shoes. "Please tell me that you actually considered to do something more revelant to abstract mathametics." Roark puts his papers on
	his desk, leans on the table opposite of the professor as he sees the professor's sigh. "Why do you want me to get in trouble, Roark? Is
	it because I push you too hard. If it is, you can just transfer to another teacher." Roark responds by smiling towards the elder. Picking up
	the paper, the professor goes page by page, taking a moment to revise the work. He then grabs his pen and starts making slashes and a few
	comments on his papers. Looking at Roark again, he writes more into the paper.

		On his chair, he calls Roark to come. Approaching the front of the desk, he awaits the useful scrunity. {1164} "To tell you the
	truth, Roark. I do like your idea, trying to experience the other dimensions that only exist in mathematics but some of the methods you're
	including will get both of us in trouble. Is it possible for you to take out that one part." "No." "When you mention meditation and binuaral
	beats, there is no use for the others." "Professor, I'm not a bad person. I didn't put anything that would offend anyone but someone will
	always take it the offensive. I don't care much for the trivial reactions. For my paper to be complete, I have to consider all options."

		"Then why not hypnosis instead of the others?" "Hypnosis is just an unconscious voluntary assisted meditation. If a person can't
	meditate, then hypnosis isn't possible." "I see that you're acute with the methods." The professor takes a look at his work and then with
	his back facing Roark, "why don't you turn the censored paper for review and publish the complete instead?" Right away Roark wanted to say no
	but he respected his professor enough to meditate on the thought. "Logically, you're right professor. That would save me the hassle from
	the board and get my message to the public but I can't." "You even agree, why do you have to make things harder for you?" Sighing, "Maybe its
	because I think too much."

		His body facing the clock and his face turned towards Roark, "I could just stop you here and end this fiasco for the both of us." 
	Roark lowers his brows, "but I won't. Mathematics, despite being so logical, progress can be made by making some illogical assumptions. If
	you're going to take this route, know that you will need strong concrete evidence for thesis or else I won't sign off on it to get it 
	reviewed by the board." Handing back Roark his paper, both hold their glances towards the other until the professor breaks of contact with
	his brows pointing down. Roark waits a little to see the professor turn back to the board, grunting at not being able to interpret this
	dance of greek symbols. 

		Looking over the whole board, Roark notices that there's too much excessive symbols. Picking up a dry-ereaser, he wipes a few of them
	off. When the professor see Roark doing this, he opens his mouth wide but then closes it quickly, taking another look at the board with a
	new perspective. {1570}

\section{3, 1572}

		...Trying to keep his eyes opened, Roark leans his back to the wall as he waits outside in the rain. It wasn't the water that kept him
	up but the expectation of someone near and dear to him to arrive. The building that holds him up, a red ancient giant that makes only helps,
	never letting him have it easy. Having enough of the rain, Roark walks to the entrance that is indented inside. His dry clothes flow smoothly
	along with him as he grabs the handle, turning it and realizing that its locked. He turns it a little hard, just a few more times to make sure
	its locked and then starts to think how? "I've lived here for at a 3 years and the front never had a lock. It doesn't need to, an closed door
	is enough to keep most people out. Besides, its the elevator that needs a key to go to any of the rooms."

		Returning back to the rain, he inhales, looks up with eyes closed and wonders when that person will come. Roark can't remember anything		about his friend, they probably were best friends when they were kids. Hanging out with each other, running around the park, jumping off 
	the edges of the playground, climbing trees, going under the bridge; these were what came easily to Roark's mind about his typical childhood
	years. Reminiscing about his past, he gets a flash that knocks him on his knees. In the park, there's a kid crying. A yellow shirt with blue
	jeans, crying. Giving him a hand, he sees that its not short or soft. Outside the building, the kid is crying in the street.

		Roark's legs spring off to the speed of sound towards the kid, disregarding everything in the world. Unfortunately its too late. At 
	the edge of the curve, the asphalt part of the street became flood with enough water to sink a ship cruiser. The passing water rejects his
	attempt by letting Roark hit its surface, a cold concrete. His pain is replaced by the failure to rescue the boy even though none of the
	events where his fault. Having exhausted all his energy going kamikazi, he falls to his side.

		Wood wrapped with a carpet slams him on the head. Waking up, he puts his hands on the floor and shakes his head. "Damn. What the hell
	was that?" After picking himself off the floor and slowing his breathing, he picks up a journal by the bureau and heads to the table. "Oct 12,
	rain outside red building, childhood memories, yellow shirt drowned in a massive yet coordinated flood."

		Reviewing all his logs about his non-experimental sleep ever since he started his paper, water has been a persistent image and it 
	always is drowing someone. None of the stories make sense and as time passes by, the more he sees that everything is just a bunch of letters
	arrange is an tolerated pattern. He puts the journal away knowning that he won't able break through when there's a wall in the way. Reclining
	back to the chair that follows from one wall to the corner and then the next wall, he sees James wave to him. Roark tilts his flask towards
	him and James sits opposite of him. "What do think Athena has done this time, become rich?" Letting loose, Roark lets his head rest on his 
	hands as elbows become parallel to the table.

		James orders a dark lager while Roark hands the bartender his flask. "Honestly, why don't you just buy it yourself?" "Since its rude
	to go in a bar and drink only from your flask." "Isn't that what you're doing?" "I appreciate the ambiance here and didn't just want to get
	it for free because someone has to work for it to keep it going. So me and him had a talk and worked things out which means he's technically
	my drug dealer that gives me my fix for free and I always tip the correct amount." "Fine, I'll stop."

		Drinking their choices, Roark listens James talk about his own project with mathematics revolving around the torus and elipse. That
	supposely the circle isn't the most natural of shapes or best shape for energy. The best example is the planet's orbit. Considering that
	the sun is the only massive object that has the most gravitional pull that renders the rest neglible, why doesn't the planet rotate in a 
	circle instead of an elipse. This also applies to many parts of the human body, like the eye, head and even running stance. For the body
	to best use its momentum, the arms must be spiralling in a elipse shape. Same thing with the feet, moving like an elipse, which looks also
	similar to stepping over a log.

		With everything else around James losing focus, Athena comes and brings everyone together for a hug. James is yanked from his seat 
	while Roark pushes right into it using his hand. She squeezes tight with eye closed, a warm ball of friends together always made her feel 
	good. Once she sits down between them, she calls the bartender to get her usual. "Don't stop talking James, I just wanted to make sure you
	guys knew I got here." Her spectacular arrival had left him in a daze where his lips lacked words, "I guess what he's trying to say is now
	he can't go on."

		She hugs James again, apologize and gets him another drink. "I'm sorry James, its too much that I had to do something." Smiling, "its
	fine, really. I think Roark was getting bored with my talk." Roark stares at him with his forehead over his eyes, "yes, math is boring." 
	Athena punches Roark on the arm, hard. "What the hell?" Athena's eyes peek from the side of her head, "fine, you're both wrong and I haven't
	had enough to drink yet."

		Wine slowly pours out the edge as the glass is tilted onto pink fluffy clouds lips of Athena's. This is her second drink and she holds
	with stable balance. "I finally got a giant client to become one of my customers for my business, git writer. It took a long time of 
	convincing him to sign up it was harder for me since I'm don't take off my pants. I had to get his attention his attention off me and onto my
	product instead and it didn't take long after a gave some idea of what value he could get in return instead of a one-night stand that would
	cost him more than a whore." James couldn't believe he was hearing this kind of talk coming from her, "shouldn't you be talking about numbers,
	not relationships?" "I wish I could but in business, trust is capital. Why do you think referrals are the most essential thing in business? I
	hate it myself and rather go direct. Also, as being a woman in entrepreneurship who's fit, most men in it will crave me. Many rich and 
	successful men." She nudges Roark head with hers.

		About ten glasses huddle in front of them as they talk, Athena talking about the traffic analytics and conversion while James was
	writing numbers down on his napkin and manipulating in every form possible to make an accurate prediction. Watching the red wine still
	swirl up from one side to another, Roark tries to think about who the kid in the yellow shirt. It has to be a friend, the friend he's waiting
	for. He was waiting for someone in the beginning and maybe the potential danger made him forget.  As the wine settled, he saw the streets
	clear of water but the boy missing. Seeing her head start to turn, he takes a gulp of his drink.

		Roark ask with a gentle smile, "so what's next in your path for global domination?" "Well, making you my slave would be an 
	achivement. Since I have made the big domino fall, my next move is to keep the momentum going and go for more. Despite having this new client,
	I'm barely going to have money to pay for the company expenses which don't include my own." James interjects, "you could always live with me
	and I could pay for your food." "Uh no, and if suggest that again, I'm taking you clothes shopping with your credit card and show you how
	much a girl can buy." He takes back what he said. 

		"Its not really a problem, cutting back for my business has actually made me realize what I don't need, like that many clothes. Buying
	less food also makes a great diet. So enough about worrying if I'm doing fine, time for some scruntiny." James looks at Roark to see what she
	means by this. "Its simple, honey, you just tell me what I need to improve for my business." "During a celebration?" "Yes. Its nice to take
	a pause and reflect but one can't forget to keep moving foward." "You can start by getting James another drink, he's still hesistant."

		Athena writes stuff down as they all laugh when they mix criticism with old memories of them together. Of how Roark noticed Athena's
	cowboots the first time he met her, "guys always tell me about my eyes and don't picture me wearing anything else." Or how James had helped
	Roark with a math problem that he spent days on by crossing out the handwritten 's' and replacing it with the integration sign. The clock
	yawns with its hands holding the 12 and 2; the bartender reminds them that he'll soon be closing up. 

		Roark and Athena both hold up James on the sidewalk as he staggers to the left and they set him straight. Maintaining his posture 
	after spending some time with the green fairy. The last thing Roark wants to do is let Athena see him struggle. His eyes, everything spinning
	and yearning for sleep is a piercing in the hull. Anchoring his route on the correction of James, Roark lets himself go in the same direction
	of the spinning to make it to harbor.

		"I don't like the city life that much, Roark. Seems like everything is automated and leaving nothing for people to do but to sit and
	talk. If I wanted to do that, I should have been a politician." "Most people want everything easy, the challenge is to find people you want
	to be with. Just how we are skeptical when someone talks straight, the same goes for them." He takes a step foward wondering if the building
	is going to slam him from the right. "I think you would have been great at a ranch, you're not afraid of getting your hands dirty." "Yea,
	I kind of did that when I was small, had to do yard work for an apartment to help my dad."

		On Sundays, he had to help his dad do the green for the apartment. Cutting the lawn, raking leaves, picking up trash; he hated doing
	this yet he saw it as necessary. To finish the essentials first and then work by investing in himself. Books were his best friend during
	school, friends that were much older and knew more talked to him at any time of the day. Their progress gave him hope of becoming more of than
	a worker in a city, buying stuff that were mediocre and going through the same work routine. When his legs were tired, during breaks and days
	off, he read.

		"At least you had both parents to care for you; a chance at normal life. I didn't. My mom died during childbirth, Amelia. Dad told me
	that she hated the name but loved the letter 'A.' My dad was a walking paradox, a well-read cowboy. Wanting to give the best gift to me and
	her, he named me Athena. He never treated me like a princess, I was too good for that."

		Walking with her head tilted to the sky, Roark world slows down and he corrects his gait. "A princess is never born, they're made. 
	Too bad most girls are too cocky and say they are -- Don't you dare say I'm a princess." "With the way you act, hell no." James bumps into
	Roark after he sees that she pushed him. "Take a right, we're going to my home instead." 

		"Why don't you want to be with me, Roark?" His loses his bearings during that instance, "Uh." "I'm curious, most guys I meet want to
	sleep with me, even James to a small extent. What's your deal, are you gay?" "Whatever helps you sleep at night." "I'm serious." As all
	three climb the stairs, "I always put all my focus into one thing and tend to lose sight of everything around me. Sure, I do go out with you
	and James; at home, its like I'm the only person in existence. I'll keep it simple, 'I like you Athena, I just need to handle my important
	project.'"

		At her door, they lay James on the floor next to the wall as Athena and Roark stand by her door. Standing in the shadows of her home,
	"Are you saying there's nothing I can do to convince you otherwise?" The snake's beautiful eyes and slender silouhuette hiss that clandestine
	suggestion. The curve to her body reminds him of a wave of water, a cry, "no, I need to do help him. I'm sorry." Roark walks away as Athena
	picks up James and sets him on her couch.

		By the window with the lights on, rain drips from the sky. 

\section{4, 3840}

		The artificial sandman comes to soothe Roark by means messaging his ears. Getting low hours of sleep, he had to find a way to get
	the required core sleep, deep sleep. Research has lead him to believe that delta waves can help since they appear more frequent in deep sleep.
	The only problem he's had that the constant insomnia creates a deceptive lucid dream, unable to tell he's in a dream or not, forgetting to
	check. When he looks at himself, he sighs. He grabs some headphones, plays the binuaral delta wave and lays on the bed. His body needs the
	black dreams, it needs the rest.

		Where he lays feels soft, body almost weightless, warm all around. Its like falling into a cloud. The first sound he hears, he 
	ignores, "delta waves." Then as more come in, louder and an innocent tone, Roark figures out that he's not alone. Opening his eyes, he gasps
	for air, looking for a surface. An involuntary inhale proves to him that this is a lucid dream, exhaling all the breath out of him. All ready
	there, he gets off the sand and turns toward the music where a siren with red hair sits on a rock away from him, like 400 meters.

		Singing in a cipher, bubbles also exit from the rock, going around her, providing a melody to her song and changing color according
	to the beat. The words, "I'll forever miss you,"  make his feet run after her while his brain is trying to analyze the song. "She'll be
    gone if I understand completely, have to stay on her track." Seaweed becomes dense in the path that he follows her, through an
    intersection inside a plaetau. Her image still shines in the dark void that he's volunteered to enter, going over rocks, squeezing through
    tight alleys while having her red hair in his sights.

        "There has to be a better way to catch up, I'll never catch up by running after her." Even with that in his head, he couldn't stop. He
    just ran faster and kept all his focus on her. "I can't lose her." As he almost loses sight of her, he trips over a rock and fly in the
    water, watching himself hover over the floor. He gasps then shakes his head, he strokes with his arms and kicks with legs. Swimming faster
    and getting closer to the girl, thought start to reformulate in his head. He notices that she always manages to stay a little bit ahead of
    him, further than his hand extends. "She could have left me. So, where is she leading me to."

        When he sees over her that there's nothing but a wall of a turqouise void, he stops. She stops and stands on the edge, never considering
    to look at him. He walks besides her to see if her view will show him anything. "A dark blue turqouise." A bit more concentration shows him
    bacteria size gray flakes in the abyss. She rests her head on his shoulders, he stays focused on the scene. "I've seen this before, I know
    I have. Where? How the hell have I seen this before?" Find her head on him, he grabs her by the shoulders, puts her head up and looks at her
    ruby red eyes. Before he says anything, she wraps her arms around him and puts her head over his shoulders, eyes and mouth closed. He's
    left in shock.

        "Red, gray, a mix of black, blue and turqouise, this colorscheme isn't something I've seen before but it looks so natural. I have to
    write this down, I have to find more, I need to..." she pulls the hair from his head hard. His thoughts drift, his consciousness drift and
    he stays at the right here, right now. Breathe in, breathe out, diaphram extends and deflates. "There's more to this than colors. I didn't,
    I should have paid more attention to her." Looking down at her fin, he sees that its artificial, latched to the sides of her waist. Curious,
    he says aloud to her, "who are you?" 

        Her grip remains constant and Roark is wondering if she heard him or that it was foolish to try talking to someone underwater, that even
    if he could talk, sound doesn't play well with water. He sighs and stays with the hug, playing with her red velvet hair. "So this is my dream,
    what is the manifest of her that includes red and deception?" Putting a little more thought into it, he sees that it must mean that he's
    not paying attention to something subtle in his life. "I can't, I have to finish this. Including anyone else in this ship ride will make
    more hassle for me; its just best I do this alone."

        Standing by the cliff, he finally is alone. The girl beside him is gone, everything behind him is gone, the water is gone and even the
    ground he places his feet on is gone. A white space, art covered in white paint; knees buckle and his hands make contact with the ground.
    On all fours and he can't bring himself to see what he's done, this is all his fault. This is what is going to happen if he has his choice,
    he thinks to himself, always trying to see what is underneath, passing the essence a going further. "I'm going to past existence and all
    I'll find is this, my white grave."

        His hands hold on the side with a vicious grip; he comes to with a small shock lighting his face. With only one arm under his control, he
    reaches over the arm and onto the bureau for the notebook. Putting his back to the side, he opens to fresh page and writes about the 
    combination, "lsd and meditation cause the user to experience another dimension with reflection of self, very lucid. If user is unsure of
    what they desire, the dimension will imitate their want." The girl, "red hair, fake fin, dark blue turqouise with gray flakes. Everything
    rolled over with white paint." 

        5:15 says his clock as he continues on with his experiments, he has no other choice since the insomnia he's developed from the begin of
    his project has kept his eyelids rolled up, under the control of chaos. Water flows into him as he holds up the glass, tilted in the air,
    standing tall; the instant elixir that helps him become more immune to the side effects. Sitting on the edge of the counter with one hand on
    it, legs in front of him and keeping a watch on the notebook, some wires cross in his mind, "maybe I should see the effect of meditation, lsd
    and binuaral beats."

        Coming back from his room with headphones, he sits on the couch, puts the headphones on, takes a tab and controls his diaphram. One, two,
    three ...He opens his eyes to find the same room he's been living in for a while. Closing his eyes, he now finds himself near rapids with
    kids everywhere, all of them wearing yellow shirts. He stands on the other side and everyone else on the other. The yellow shirts are distinct,
    like rosarch blots. They all talk to each other but the rapids drown out the noise. He looks to left, close to the horizon and then to the
    furthest right, water always connected.

        Eyes still attached to the right side, he spots something being carried by the water. Running closer, he sees that its an yellow shirt
    with several black circles, varying in sizes, perfect balance and a line that flows from one circle to another. Watching pass by, he sees
    others cheer as it passes and then begin to take off their own yellow shirts. Its like they threw a sun into the water, all the shirts stick
    together. Now they wear are a gray striped shirt, all of them. Then it comes to him, what is he wearing and proceeds to check. A gray
    stripped shirt.

        Movement becomes difficult as if the shirt were made of iron. It forces him to sit down and watch the others. One compliments a gray
    by the texture of shirt, another by the length, the slim fit, how they're matching, similar. Small groups start forming among the population
    and then eventually there are 5 segments, each keeping their distance from the other. Cries of anger are thrown from one to another and 
    the fire burns more and more until they spot Roark on the other side of the river. They cry blasphemy, saying that he thinks that he's better
    than all of them since he's not living with them. He becomes their enemy for being different.

        Weapons take form on the other side and Roark begins to worry. Checking behind him, he finds a wall behind him, preventing him from 
    going anywhere else. From his seat, he hears that their success is a matter of time, he has to stay there and face their wrath. He has no
    other options. The rapids are filled with anger of poseidon, crashing from shore to shore and with other waves. It would be foolish to try,
    Roark's fate is locked.

        Ten catapults are made and set upon his location. People at their stations, ready for the signal to fire from their leader. With anger
    ricocheting in him, he overcomes the weight of his shirt and stands to face the opponent. The leader steps back a little and gives the order
    in a higher than normal pitch. As the meteors pass the top of the arch, middle of the river, Roark jumps into the rapids. His body is now
    prey to water currents and as he is thrown further down the trail, he watches the rocks indent the ground he stood on. This was his last view
    before the rapid removed his consciousness.

       Lights keep flashing on and off, leaving a blue imprint on his mind along with serenity. His body drifts on top of the water while 
    remaining dry and the river being the only thing in existence. The yellow circle raft he's own floats on a thin layer of water. Slowly 
    returning to full potential, he drags himself to the edge and puts his hand in the water. His whole arm gets wet but its only his elbow
    that continues to stay wet. Then he arranges his arm so hand and shoulder are wet while keeping his elbow dry and under the water. He coughs
    and looks ahead to where the water leads. There seems to be an ending to it, "all I can do is sit."

        Rising up, he takes another look at the raft and finds black spots on it. Stains from an artist, each part having a common crease. Then
    it runs up to him, jumps and slaps him, these were the shirts that they threw into the river. The sudden shock had knocked him to sit back 
    with his hands behind him. "They all had yellow shirts except for me, where's mine?" Getting closer to the end, he sees a yellow shirt 
    standing, facing him and looking up to him. Lower himself to meet the boy eye to eye, he sees that the yellow shirts is too big for the kid.
    The boy takes the shirt off and holds it to Roark while still wearing a yellow shirt. Docking, Roark approaches the boy and carefully 
    accepts the offering. "Thanks." With the shirt on, he feels a subtle warm caress his body and notices its a perfect fit for him.

        The white canvas that they walk in starts changing color, a lot. The boy observes in amazement while Roark tries to figure out what's
    going on. Pay close attention to the colors and how often they change, it reminds him to close his eyes. Then he hears it, the same piano
    key being struck several times, the tone getting louder and more music accompanying to convey the walking of an alley with an old flame, 
    Roark realizes that its his alarm. Just this sudden awareness should have waken him up but he's still here. He shakes his head, closes and
    opens eyes rapidly, throws water in his face. Sitting down besides the kid, "I'm going to miss the deadline today, damn." The boy then
    turns to him and says, "ha ha, no you're not, have fun." With that, he pushes Roark over to fall into the white space. Further he goes down,
    the more slower his descend becomes until he floats at the center.

        Coming after him, the boy appears and smiles. "If you really want to get out, he have to go all the way up." The confused Roark is that
    after the boy with the yellow shirt said this, he pointed down. "Obviously up isn't down, right?" Then again, he that was true, why isn't
    floating in an empty void. Putting all his trust into the boy, he starts making his wave further down. Its like swimming against a current
    but he doesn't stop, not if he can still keep going. He feels a white phantom pull him by the shoulders, trying to make him go back.
    "Keep going, you're almost done."

        His legs hurt, sore from being used passed potential, arms unwilling to even hold food to eat; he crawls further down. With his last
    breathe, he pulls himself a little closer to the distance. Anchored to his spot, he tries to catch his breath. "Let go." Roark looks up
    and sees only a spec talking to him. "I've trusted him this far, might as well keep going." Removing his grip, he feels his body slingshot
    all the way, past his origin. He then is projected all the way to the sky where he ends up breaking through a ceiling and landing in a 
    dark attic. The hole repairs himself and he finds himself in complete darkness.

        A shock goes through his body, his chest beating his head in getting to the air first and faces the window. He turns off his alarm and
    notices that the window is open. Cold holds his hands and he feels that he should wrap himself in a blanket that has been near a fire. 
    "Is it possible that temperature can also affect the mind's status as it affects the body." He throws his hand on top of his notebook,
    brings it to him and starts writing all the ideas about temperature, how temperature can give a trance more support, make it more immune
    to disturbance from the consciousness.

        The sun rises for the day and he gets light that is reflected off some buildings as he writes. Closing his book, he decides he has another
    hour or three before he needs to keep his appointment. Through the kitchen and to the bedroom, he lets himself colapse on the bed, arms
    spread out and face on the pillows. Before drifting into rest, he sends Athena a message, saying, "Morning sunshine. How are you guys doing?"
    With this, his body falls deeper into the softness while the heater gives him comfort.

\secion{5, Mary, 6393}

        Sitting at the table on the patio, in a white satin dress, texting her friends, her omelete is brought to her along with some juice. James
    enters the restaurant for brunch with Mary and spots her a few feet away from her. He stops, hesistates about going to her. The exit isn't
    that far from him and she's busy with her phone, maybe she doesn't even know that he's here. "But I already told her I was going to meet her
    here." Taking a deep gulp, he walks to the table and sits down in front of her. She looks him from her cellphone and tells him she's almost 
    done.

        Munching on some breadsticks, he puts his head on his left palm and sees his reflection off the restaurants glass. His reflection is
    reading "inventiones mathematicae," at home, pass midnight. Drifting further from the worry that about what to do with his hands, if he is
    sitting properly while he waits or any she might be texting about him, he turns the page. Legrange algorithm made by an MIT student that he
    found a few flaws but was supportive because of the new implementation. Then as he turns the other page, an angry face of her is on it. He
    turns the page and she's there again. More pages get infested with her and he's wondering where is the math. Putting the book down, he then
    sees the face next to him and letters on her.

        Snapping her fingers near his face, "James, I'm here." She snaps them again, "Are you even paying attention?" He shakes his head, "Oh,
    I was worried about what to get you for our reunion." Her eyes squeeze as she smiles, "Don't worry about that, you're taking me shopping for
    that next week, I want you to get the perfect gift and I think you're not capable of that. What bad manners I have, I didn't even ask about
    you. So, how are you?"

        Taking a breathe in, "Not so good, I've been talking to my professor about my math thesis and its become cubersome to test the methods
    for legrange's formula. One method actually saved us a paper of work while the other one had to be done by computer because of its recursive
    and repeative nature. There's like 20 methods to try but there doesn't seem to be a way to implement it. I always believed that you can solved
    mathematical problems in any way, that there were only better ways of doing so. This formula is showing me that this is not the case, that
    the problem itself restricts the possibilities. I should just stop here and say this is true except that I just need to try harder. Theroems
    are not disproved by a simple contradiction like ..." (6800)

        Mary sits there with her cheek on her right hand, those vacant eyes with her eyebrows pointed down. Apparently she had been coughing her
    discomtempt for a while but only up to now has James became aware of it. James covers his mouth with his hands and lets her talk. "I thought
    you would never stop. How many times do I have to tell you James, I hate math. Nothing that you can ever do to make me even like it. Remember,
    when I ask how you been, I don't mean anything about your work. Let's try this again, 'how are you?'"

       She might as well had her hair pulled back, glasses on, and a pen and clipboard at hand when she asked him that question. He knew he had
    turn off his logic, "she doesn't want to hear it." Hearing her fingers tap the table, he blurts out that its was great, coffee was great.
    "See," she said smiling, "now that wasn't hard, was it." With eyes closed and head down, he tries to catch his breath while she is oblivious
    to his state.

        Taking another glance at her phone under the table, "James, I'm getting restless. You promised me that you were going to finish your 
    discertation this year and as November is here, you're not done yet." "I'm almost done, there's still time." "You're not listening, I hate
    how you're making wait, I shouldn't be made to wait, considering how valuable I am." Blonde hair with a white head band, pearl white skin,
    blue eyes, pink lips, a white satin dress and white shoes. In his head, "her being my girlfriend is blessing and I'm pushing it to its extent
    where this fantasy might crumble." He then says, "I'm sorry," she smiles, "I'll make it up by somehow during the wedding."

        "No, I want something now. I just told you how I hate waiting and now you're trying to make me wait more. Are you even paying attention
    to me." "yes, yes, yes," he says has holds his hands togther, placing his head on it. "If you really cared about me," she turns away from
    him, "you would drop everything to be with me." He shuts his eyes tighter, "so hard to love two things."

        "I'll let you move into me." She turns her face half back to him, interested. "Yes, that's it, you can move in, get a start on how life
    would be together." Now she is facing him completely, "then I can decorate it as I wish?" "As long as it doesn't interfere with my work." He
    was glad to put some logic into the suicidal convenant, a defence into the contract. Elastic, she clasps his and leans to kiss him. "Yay,
    I'm going to have so much fun fixing that classroom you call your home. I'm probably going need some help from my friends on this." She
    then shifts to her cellphone as James drinks some of her orange juice that leaves a taste of hemlock in his mouth.

        "Its fine, James, your home is going to keep her busy while you do what needs to be done, your passion, your discertation. You're 
    definitely going to hate how your home is going to look after she's done with it yet you're going to be happy with yourself. Sometimes you
    can't have everything you want and Mary is prime example of this. If you decided to stay in the status quo, she would have left you and
    I doubt you have the ability to get someone like her beauty or prestige. You're going to have to bleed but its worth it."

       Putting her cellphone in her purse, "now that you decided to listen to reason, I'm going to tell you that my father is going to offer you
    a job in his business as a wedding gift and I want you to accept. When you end your paper, that is the last time I want to hear about math,
    especially in my house." Under the table, James clenches his fist. "You know that I don't like an office job and that my profession pays well.
    If you're annoyed by math so much, we could just not talk at home." Her eyes squint. "Can you let give me some time to think about it, with
    the you know what on my mind, I can't be thinking too far ahead in the future, despite all the good fortune it holds for me."

        "Don't see why you need more time with that but I'll give to you since I already know what you're going to say. And if you don't, things
    will just get worse for you." The band on her purse is streched slowly and vigorously by her delicate hands. James takes a quick peek down
    and see the tortured strip. His smiled stretched back, "you know I'll do anything to please you, its just so hard to let go and I'm thankful
    for you being so understanding of it." Her head rises up a little higher as she tilts her head up slightly, "yes, I am great, huh."

        "I apologize for my rude behavior, James, its just not natural for a lady like myself to wait. I get ansty. I just want it now and I 
    somehow forget to consider you. Finish your silly paper so all ends will be tied up and when the day comes, all you have to do is say two
    simple words." "I know." He goes to kiss her on the lips only to have her cheek offered to him instead. "Since we're already here, what should
    we do this weekend?" This weekend is when he had planned to spend the whole time with some other mathematicians to work on his 
    project and if whenever she said those words, that time would be allocate to her only. "Spend my time with you but didn't you say you had to
    do something with Ashley?"

        Tilting her head to the side and looking up, "No, I don't think soooo..." She tends has her hand dive to her purse to pull out the 
    cellphone and she checks her messages and calendar. While she is occupied with the query, James checks the time, he thinks to himself
    "have to meet my professor in twenty minutes." "Scratch that, you're right, I do have something planned, excepts its with Cynthia. You do
    listen to everything I say, oh you. I guess you'll have to go another weekend without me."

        As he leaves the table, he feels like he just left the atmospheric pressure had changed from ferious to benign. She back on her cellphone
    once he left is seat and he considering how life will be with her being more commmitted to him.

\section{6, status quo, 7961}

        Reaching for the door knob, hooking the key into it slowly and trying to find the spot where the lock opens, light posts have been on
    for a while but now the street is empty. Shoving his way in after the lock gives in, he exhales all the weight of the day into his room. 
    Dropping his keys on the pantry, he goes to his couch and lets his body collapse on it. Eyes are still alert, unlike his body, which craves
    his bed. Willing to give in since it has been a long day, he stares at his work in the living room. Three white boards hang on each wall, 
    extending almost to the length of each, full of equations, notes, colors and crossed work. He was glad of having installed the white boards,
    the ideas that Roark had.

        James knew that there was something that he could see subconsciously, he felt that he was overlooking something. His professor had agreed
    with his opinion after going through all the pages even though he was less skeptical, "it looks right to me but I wouldn't be surprised if
    you find something wrong." As he laid on the couch, his right brain dominated thought since the left had been overworked. The colors on
    the wall became more animated, as if they were shaking in place. Some text moved more than others and that's what attracted his eyes the most.
    The integration, the trigonometry identity, some algebric work and the picture. About ten percent of the all three boards where being 
    highlight and despite being arduous for his body, he got up and circled each selection so he could remember after passing out.

        Fall back again to the couch, he sees a picture of Mary by the bureau, in a silver frame. Maneuevering his feet to hold the frame, he
    flips it down gently. Just seeing her while he did his work made him feel like pulling a cover over his head. Now he can hear her, "you're
    writing look chicken scratch. Write better, people are going to think the worse of me if they see you writing this way." She pestering
    him about the time, sitting with her legs crossed, leaning back on her chair and texting her friends, hearing her press buttons. Sometimes
    he wishes he could, only once, go up to her and give her a soft push so she would tumble down on the chair. Despite how rude she is, he could
    not bring himself to do that, it was taboo for him. If anything, she had forced him to learn to focus more by becoming staying concentrated
    while she was there.

        Stretching his arms and legs from his body, he feels warm enough to get back on to his feet. Going to the smallest circle, he takes
    a look trig identity. 'sin(two-theta) = 2cos(theta)sin(theta).' "It's right, sine of two theta has to be 2 cosine theta, sine theta." Grabbing
    a marker, he works with the classic a squared plus b squared equals c squared. From there, he turns the a to sine, b to cosine and c into one.
    Diving each by cosine squared gets him tangent squared plus one equals secant squared. Still not seeing any problems, he draws a right 
    triangle, labelling the sides and angles. Standing back, he stares at his fresh work with his muse to the side of him. 

        After looking at it for a while, his eyes become more vertical. Then as if a daimon had taken his body, "sine two-theta can be morphed
    into something else." Quickly closing his mouth with his hand and having his eyes pointed to it, his brain starts processing the statement.
    He thought, "its an alias, not mandatory. There might be an easier way that the normal approach, I should probably turn sine two theta into
    something better fitting for my work." Crossing the right side of the equal sign, he leaves a note saying to try again.

        Fatigue clenching his hand on James' lungs, he decides to rest by going to the kitchen, setting some tea on the stove, resting by the
    counter with his left hand on it, eyes still on the board. Putting more of his weight on the ceramic tiled counter give his feet comfort.
    Paying attention to the second, James tries to keep his breathe slow and constant but it seems like every time he takes a breath, he gasps
    for air after coming from a dive. Hands become cold, shoulders weak and his neck giving to the weight of his head. Throwing back up his head,
    straighting his back and his arm, he yawns.

        He takes a sip of the tea from the counter yet the elixir has declined in assisting his recovery. Finally agreeing with his body, he 
    decides to clock out. His eyes go from the board to the tea as he lets his subconscious play with the math while he tries to recall the day.
    Skipping over brunch, his mind blacks out the whole day until arriving home. He then goes to the living room, grabs his bag, pulls out his
    noteboook while walking back to the kitchen and glances over the fresh ink. About 15 pages of new work, different types of font styles and
    much crossed out work. With another sip, he puts his arm besides the notebook that's laid across the counter, moving his head closer to
    the work. Meticiously inspecting the signs, readjusting his glasses, he sees something with a faint hue of red. He marks the suspect and
    realizes that his body is near its end. Finishing his tea, he takes the last drink by standing upright, tilting his head back and the cup 
    over his head.

        Laying on the bed, limbs stretched out and his eyes yearning for some darkness, he still hasn't given up on the subconscious notion of
    something being wrong with his work, that he's overlooking something. "There has to be a way," he tells himself. Eyes closed but he remaining
    conscious, "If I can sense it but can't see it, then I have to change how I see things." He then slips from reality and drifts to the clouds
    where anything can be a manifest of his ideas revolving in his head. The world becomes darker and less of himself becomes bound by chains
    of physics and time.

        He finds himself lying on a black surface. It extends from one horizon to another with everything else being a white space. Still not
    aware of where he is, he gets off the black line and starts walking on some imaginary floor. A deep inhale and then he remembers to think,
    "this isn't my bedroom." Walking back to the black surface, he looks at what he's been walking on. Making his feet go to the same level he
    was walking, it passes through an empty space. With his arms still holding on to the other side of the surface, he tries lowering himself
    to the point where half his body is off. No surface to walk on. "Wasn't I, no. I just imagined it, that's it. Uh, soo, now what?"  Grabbing
    and releasing some of his hair near the back of his neck, he looks to the depths of the white void.

        Accepting his current conditions, he starts to think about the sine problem he had before arriving here. He begins with the triangle but
    then he consider if that's the only way to consider sine. "The essence of sine is the function, a wave on a graph. Starting at (0,0), a 
    line that moves up and down smoothly in relation to angle on the square." From the far left, he starts to see something jumping towards him,
    the jump seeming bigger as it gets closer. On his feet, he tries to time the jump right and moves closer to the foreign life form as it 
    pierces through the spot he was laying on. Check the change, he finds segment smaller than before.

        Trapped, he moves his eyes to the sky and sees a zenith. Curious, he holds on to the side and checks the bottom of the line, another
    maxima. Amazed, he steps off the line and tries to get a better view of the enlarged function. He then makes another changes, adding a cosine
    function with a blue line. The sine function becomes red. His eyes, absent of fatigue, watch the functions rotate like a dna double-helix.

        "Nice trick, already did it in my head before." As he stood there looking at the ordinary, he wondered if it beat a computer in graphics.
    So as he continue to see, the lines were slowly becoming more dense, becoming planes. To this graph, the z coordinate was added and the lines
    were now 3 dimensional. Those line had spread all throughout the space that he saw himself being lifted by a translucent carpet with flashing
    colors. Walking up and away to let the function behave naturally, it started flat, dipped and climbed about 5 times up as it went down. 
    Leveled was green, lowest more blue and the top, vibrant red. {9484}

        Everything paused, the mathematical blanket function had stopped expanding, there was an end to the axises and James was sitting down,
    writing on a notebook while glancing at the image a few times. Much better than a computer, able to experience math in person instead of
    being a distant observer.

        Eyes dilated and on the mountain, he walks closer to it. A landscape completed in tiles, smaller than his hand, varying in hue by each
    one. He runs his hands on it, no friction. Something inside of him comes to focus, "go for it." He hesitates, "I could get hurt, what
    would it accomplish, why me?" His subconscious already making the decision that he knew he would make, moving slower to the edge before the 
    dip and a sitting on it. He then takes his hands off the floor, lifts his legs up and lets his body slide down the dip and up. The first
    time he barely goes a forth of the tallest peak up and it sends him back to the beginning and more, becoming airborne. 

        Time slows as it seems to him that he hangs up there, gravity forgetting all about him. The lines of tiles shake a little from what he 
    sees. Putting all his focus on one, an electric charge goes from one end to another. Before trying to think what to do with it, he's thrown
    back at full speed when makes contact with the ground and goes up and down, barely making it to the peak. He tries to look back to the line
    but the momentum he had left had moved him over the edge and down he went again.

        To go up, he went down and now everything that was below no longer exist. He was thrown to another white void without seeing the 
    transition from one to another. At first he didn't want to believe, that he was going to come down in a few seconds, how ever long those
    seconds took. It was only til he realized that he was sitting down on a supposely surface that he accepted facts. 

        "Quarantine, quarantine, location has been quarantine for your own protection." Red lights had started flashing and the world had become
    dark except for the pathetic orange lighting. All he could hear under the alert was something heavy and metal closing, either like doors
    and/or windows. James backs up to a corner and tries to keep everything in his sight, pupils almost covering his iris, heart ready to explode,
    fist cocked back.

        Rustling happens on the opposite corner of him. Red lights spinning around, showing more of the room while the dark loses focus yet
    becomes more dangerous. It claws along the walls, wanting to be sure the James knows it presence, trying to scare him. Light always skips
    the monster as it stares at its target, contemplating when to strike, maybe a little longer. No, waiting is hard for it, its body moving
    forward while its limbs hold it back. As James looks into the dark and dangerous void, he maintains is fortitude, legs shoulder with apart,
    body orientated to the side while his head faced the other corner. Keeping eyes alert, the lights move take longer to spin, the noise
    seems to be elongated and then everything becomes dark.

        In mid air of the tackle, James feels the hands and feet of the monster on him. While everything is still dark, his arm shoves off
    the hands off him and when they hit the ground, slobber lands on his face. Now he sees but the monster's face is covered in the shadows.
    "Can't fight something I have no analysis on." James tucks his legs in and strikes the monster off him, propelling him back to the darkness.
    A loud hollow (dung) of metal is heard and feet readjusting itself. With his foot to the wall to strength his balance, he resumes his posture
    and tries to find it.

        "Something is in here, you already got a taste of it and so has he," James looks at his red arm, "it messed up and now I doubt he'll do
    the same mistake twice." Letting the rest of his body relax, he scans the room for anything useful while his ears pay attention to any minute
    change in sound. Connected to the wall, he finds a bar, about half his size, on the right of him. After tugging it, he knew didn't have the 
    strength. He then returns to his stance and waits for the monster.

        He hears the scratching of the metal as the monster towards him and James rolls forward, going underneath him. A fast turn about and he
    sees the monsters green eyes look back on him as he stands close to the wall. It jumps again, a pop resonates and James moves away from the 
    wall. It shakes its head and swirls it head left and right, wanting to kill. James then grabs the metal bar, goes to the other corner and
    taps the wall. The monster jumps to the sound only to clash with the wall. Coming out of the daze, the bar hits it, making it spin.
    Collapsing on one knee, having the bar provide him support, James checks to see if the monster isn't moving. Back on the floor, James
    stands up as he use the bar as a cane and gets closer to it.

        "Quarantine, quarantine, QUARANTINE" The noise becomes loud that causes a storm in his head. Too much wind blowing, lights spin faster
    to the point of becoming a hypnotizing flash. Closing his eyes, moving away, he tries to clear everything up in this chaos. Then he's on
    the floor and its hands are on him. He evades the kick move and from the ground, he sees green eyes stare at him as they hover in the
    darkness. "QUARANTINE"

        His wakes up as if someone had tazered him, limbs flying about. Recognizing his room and his bed, he starts to slow his breathing
    and relax more. "quarantine, quarantine." He looks to his the side, finding his cellphone ringing without words. As he checks the number,
    "its Mary." Tired, he goes back to sleep.

\section{7, Athena}

        A rooster crows in the darkness and she gets up before turning the light. Hair as a thick messy aurua, a shirt with a rugged past,
    pijamas and bare feet. She turns off the alarm clock that flash 6:00 am in red light. Taking a deep breath in, she rises and gets out of
    the bedroom.

        Black coffee is being made as she prints a few files to look at on the table. As the water passes whatever mechanism to reach the coffee
    and pass the filter, she sits, look at the latest numbers of her startup. Barely reached sustainability that has escaped her too soon, 
    customer were leaving and she wanted to know why. It goes from 2 to 70 in one day, others where she gains like 17 new customers. She 
    underlines a few numbers, crosses a few things from the home page and then checks her email.

        An aroma of bliss floats to her, filling her the ambrosia that she yearns every morning. By the counter, she pours her self black coffee
    and holds the cup in her two hands, the warmth spreading through her body. Close to her mouth, she smells the simplicity rejuvinate her. One
    sip gets her up to 80% and she keeps the cup with her as she goes back to the papers. Coffee besides her as she reads email, she's has to do
    it, there's no other way to avoid it.

       First email, "Dear whom it may concern, it would be great to have a chat tool be added to git writer. Just a nice way to stay connected.
    Thanks, bye." About fifty emails to that same template, all asking for a chat feature to be integrated to her product. "Irssi for linux users
    and google talk for all others, next issue." From the hundred she assinged to herself to read, there was another majority that asked for
    a different design, to be look pleasant to others while the user had it on their laptop in a coffeeshop that will not be named. She takes
    another sip of her coffee, closes her eyes and says, "our product comes in all colors, that's if you like black only." She wanted to stop
    but there were still more to read.

        "Hi, techie/writer here. Is it possible to have a word analysis feature? Since git writer is to make writing easy, I thought it could
    also make a writer better, let him see patterns in his writing and determine what to do about it. Before, we have to rely on intuition
    and familarity but we don't see the whole picture like that. If not, I'm still stay with you guys, git writer does what I want and has
    no fluff. Great stuff."

        Her arm slides further away from her as her head gently descends to the letter. As sweet as the coffee she drinks, it creates a tabula
    rasa state in her mind where the previous emails don't exist. But she had to let go of this feeling, feelings aren't what make and
    maintain a business, its practicability. She then puts his advice to her pen's scrutiny, working on the probabilities, checking the 
    cost versus value of creating such a functionality. Text being written on the screen, a steady stream and she can picture the bottom
    of the window displaying some useful facts about the writing, just like her vim configuration. Next, the sentences became shorter, flow
    into short blurbs of nonsense with irregular pauses. And so she opens her eyes, "not even if hell freezes over will I add chat." On
    her agenda, she sets a date for the 'word analysis' project.

        She couldn't believe that most of her users were like the fifty emails she read, lacking the focus to stay with one thing. That writing
    has to now be done with others all the time. To be alone while writing is blasphemy. Crumbling all the emails away, James pops up from the
    couch, hair slanted to the left, smiling, "uh, good morning. Did I break anything?" She laughs, "No, you want breakfast." His stomach
    growls loud enough that both of them here.

        On the table, both eating, James thanks her for everything, letting him sleep over, breakfast and understanding. "Really, that's enough
    food. Any more and I'll explode." She made him five eggs, two handfuls of hashbrowns and a pitcher of glass while also having the same
    amount on her plate. At some point, she looks down to her food and finds her papers near, rekindling the fury she had about the feature
    that they didn't need. "I want to punch the person who said the customer is always right." Making slow progress on the food, James makes
    contact with her says, "no one is ever right and you assume they are, you'll end up with contradictions soon enough." She felt that the
    weight she held was shared by James, who never has taken a mba course, like herself, yet is full of knowledge that newbies should
    listen too. Never biased, always based on facts.

       "If you don't mind," she looked straight at him, "if you can -- sure, always good to help you, especially when it comes to numbers." Both
    help clear the table of dishes and stand over the papers, she giving him the papers to consider. "These are conversions, visitors to sites,
    number of clicks on ads, and etc, etc, and few new milestones." He spread the papers around like a dealer spreads cards but with all of them
    facing up, all relating to all the papers present. A red line arched from one paper to another, a blue lined stemmed to five papers, some
    turned the color yellow, a few select became bright, rising above the others. The paper of interest as her growth.

        "Don't be worry about the decline of customers since yesterday, its normal for points to richochue on a graph." He then drew a line that
    best fit all the points and brought to her attention that her fall and kept her above most points. "What I'm scared of is the type of function
    your customers are increasing, its exponential. If you do the marketing right or good enough, a million users is possible within a month." 
    She turns away from him, her knees touching and feet apart, pointing to the same object, mouth ajar and her hands to her cheeks. She then 
    smooths herself, her hands straighting any creases on her and returns back next to James. "Why would you be scared James?" she asks, looking
    coy. Once she said that, he pointed to her capital, "you're going to need more cash and not even increasing the sale price is going to cut
    it."

        Estatic for the potential for her business, she knew who she had to talk to, Houston Grant. "At least triple of what you have now. I
    don't know how you're going to get the money so I'll leave that up to you. As for the second, I saw that you was considering add anohter
    feature to your product, not such a good idea." With her raised as she stood back from the table, her right hand on her hip, "Explain, James,
    explain." "All my analysis is based on the product being constant and that the only thing to change is the exposure and how well it scales.
    Adding another feature will add more uncertainty to your endeveur and increases your chances of failure." She was now next to him, staring 
    hard at the papers. "You might be up to it and it might be a great idea but rarely do people respond well to changes, best to do it later."

        James finds her facing the window, her mind closed to everything in the world, she, alone, thinking. She was considering the obstacles
    that lay ahead of her and weather to heed to the oracle's words. Then she thought about the world she was in, business. It wasn't math, lines
    are fuzzy and one just had to feel in order to progress. She tried to use that method least, creating a foundation strong in logic except
    it was a mandatory skill. Turning to him, "if this were purely a mathematical problem James, I would agree. Except there's people involved
    and that makes it complicated. I like the idea for the new feature and I shouldn't let something like uncertainty scare me to post-pone it."

        She puts order to the table full of papers and walks James out. "I'm glad that I'm not in business, I just don't fit in." She then grabs
    him by the sleeve and says, "other way around, business doesn't go base on numbers, too much feeling."

\section{8, Probability}

        "What do you think this is?" he asks as he holds the jar open. Reaching for the lid, "something that you shouldn't have open," closing
    the jar. The detective squints his eyes at him, "can you at least tell me something about the jar, doc?" "First, I'm not a doctor, I'm a 
    chemist." He straightens his lab coat and inspects the jar, "this is ergot, main ingredient for producing lsd and uh uh, " he opens the jar,
    "looks like uh someone has ..." leaning closer to the jar, "like someone has taken a small amount." Taking back the closed jar, Chris looks
    around the top for any fingerprints left behind. "You're not going to find anything on it, chemist students all wear gloves when working
    with chemicals, especially with that one."

        Both of them stand in the white room, with white floors where white cases store all the chemicals in jars. Chris blood was rushing and
    all he was doing was standing there, hearing that he's wrong. He soon finds out that the chemist is right and hands him back the jar. He
    checks the floor for any foot marks and at once, hears the chemist. "This place is restricted to everyone else except chemical workers hired
    by the job so if you want to find out if the worker we met outside was in here, the call this case closed." Chris wanted to shut him up, 
    duck tape over his mouth, effective and amusing; "no, he might actually say something useful, soon enough." Still wandering the room, "you
    can wait for me outside, I feel like taking a stroll here, try to get some inspiration."

        By the door, the chemist leans against the wall, cellphone out, finding something to kill his time. Inside, Chris walked by chemicals
    that didn't sound familiar. He thought he would find stuff off the periodic table but the only closest came to be monoxide. He was sure that
    had oxygen, "one, I suppose." Going to corridor after corridor, all he saw was the same foot print and came to accept that it must have been
    the student worker he just talked to. Not wanting to waste more time, Chris walks out the room.

        "I'm done with that." Chris exclaims while the chemist is still playing around with his cellphone. "Can we go home now?" Chris finds out
    that's it 7:02, "let me find something, anything that leads me to a path. I won't be able to live with myself with this guy getting away."
    Shrugging his shoulders, the chemist followed the officer with his head down.

        "Can you tell us who's been access the ergot in your facility, please." The worker then types away on the computer and within seconds,
    tells him no one has. "Show me the screen."  The row says ergot and the number of uses says zero. "That's what the computer says, don't
    blame me. I remember specifically typing in the times it has been used, a chemical like that is rarely used except by one person. I don't
    know how the computer would say zero. Don't blame me." Chris was picturing a hacker that had learned to make the chemical off a website and
    decide to come to school, make it and profit at someone else's expense, laughing at him for being left out in the cold.

        "That bastard, he probably hacked the school computers to erase the records. He can't be that smart, he's dealing drugs, there must have
    been something that he's been careless about." He was alone as the chemist left to get something to bite. Leaning on the wall, he looks at the
    blue white ceiling.

        Returning back to the wall, there was a whiteboard behind a podeium. Officers of his unit wear all around him, seated, talk to the others,
    using their cellphones, staying busy to tolerate the wait. Chris was keeping watch on the door, hoping it would open already so he can start
    on his quest. It was hotter in the room for him than for anyone else and he unbutton his shirt a little, "no one will notice one button off."
    As he unbuttons it, the Sheriff walks it and lowers his aviators, letting Chris see his discomtempt with how he's dressed. Chris quickly
    returns the uniform to its proper image and sits down upright, like everyone else has once they see him at the podeium. 

        He puts his hands on the edge of the podium, looks at all cadets from one wall to another. Expanding his diaphram, he speaks. 
    responsible for the greatest achivements in history and capable of so much destruction. It worst state is when it is not thinking according
    to standard, which can be handle if spotted early in a child. But the problem is not innate but fabricated, by drugs. PCP, meth, marijuana,
    speed and the such are mind alterating drugs that can crumble a society. Our program is to stop drugs at the source, anyone that is
    fabricating here in the state or main suppliers that ship it here."

        Most of his half an hour long speech involves society, prevention and the extraction of drug dealers. "If I were to me, I would 
    personally have them executed but since we have to respect human rights, persecuting comes a far second." With that he ends his speech
    and starts calling out names to assign officers to locations of interest. "South Central bank residental," Chris jumps up from his seat while
    holding on so no one in the room actually sees his excitement. The pause after the location seems to lag forever for Chris, like it was
    meant that he never have the chance to prove himself. "Steven" He struck out a bar after scoring two skyscrappers and sank into his seat,
    waiting to hear his name called to whatever they needed an extra body to work on. 

        "Chris, Chris, pay attention." Shaking himself back into the room, "I said, you're to investigate the university of Washington for any
    student fabricating drugs." He then slips back into his self loathing and the room becomes silent. 20 minutes later, everyone gets up and he
    gets washed outside of the room with the urge to talk to the Sheriff. He breaks from the current and moves to the left of the door, waiting
    for the Sheriff to exit.

        The Sheriff steps outside and notices someone waiting. Turning his head towards Chris, "Is there anything you like to ask me, deputy?"
    Chris' yes came a little slow, still looking down. "I wanted to know why I didn't get South Central, I have a great record in the academy
    and my first year has been extraordinary, I know I can do this, I want to do it." Putting his hand on his shoulder, "look son, I didn't pick
    you because I'm focusing more on the end instead of the means. Its still a risk to choose you to do South Central despite your performance
    but you have to realize that you always won't get the important parts, sometimes you have to be the supporting actor. They have more 
    experience than you on the field, they know what to do when they get in trouble. You, you know everything need to persecute a criminal and
    it would be a waste if you got hurt during cross fire or worse." "I won't get hurt, I won't."

        "I'll make you a deal since this is a little unfair to you. If you can prove to me that you're ready for the field by doing the task, 
    stopping students that are fabricating illegal drugs, I'll consider equivalent to the others who have more years than you. Until then, don't
    ask me for anything else." With that, he walks away from him in the corridor. Still angry that he is stuck with the elementary task of 
    apprehanding small delinquints. He's so much better than what they think of him. Only way to show it now is to stop all illegal drugs from
    coming from universities and putting all the chemists in jail.

        "Any more bright ideas?" the chemist ask him as he chomps on a few chips. He can't leave now, he's found nothing. He's done everything
    that a normal detective is supposed to do, investigate the crime scene, ask witnesses and ... cameras. Yes, there were in a building that had
    cameras. Looking up, he sees a camera on the top corner of a wall looking back at him. "Come on, we have to talk to the student worker."

        At the counter, Chris asks how many packages of ergot the school had bought. "Three, the first one lasted 40 years, the second a year and
    the third one about 2 months ago. We're on the fourth one. The first time we ran out was last year." "I'm going to need the survellience 
    videos from the past two years for my investigation."

        The chemist walks out the building as Chris remains inside, talking to the security guard about the videos, "I've been here for five years
    and I haven't seen anything interesting on those videos but if you say so, you can check it out yourself. It's going to be be long, even
    on fast forward. Two months takes about eight hours." In his head, "Am I going to spend this much time to track him, is he even worth it
    compared to those from South Central? He can't, he just one man, kid, whatever."

        "We all have to do our part."

\section{9, prejudice}

        Chris is by himself waiting for a person that might never come, in a room, seated, staring into another room where time goes counter
    clockwise and fast. A day passes and he sees a few students, routine exercises, heat water with a hot plate, measure liquids correctly
    using a gradulated cylinder and writing into their lab books. All of them holding each glass with two hands and never walking with more
    than one at a time.. Leaning back, chair two front legs lifted, he continues to watch for the monster to make its obvious appearance and
    figure out a way to take him out.

        While the room on the screen was empty as time flew by, Chris recalled the jar he opened. Merely a small quantity was taken out of the
    jar and its been months since the third one has been used so, "he's doing small quantities? Frequently? How the hell is not caught yet?
    Have to stop him. He must be stopped." Then he remember seeing the quantity, a few spoon fulls; the chemist had told him only enough to
    produce a quarter of a sheet, much more of a waste if he was selling the stuff. Fogs lingered in his prediction about the criminal, what
    his ultimate intention is, maybe he just need a little to attack specific people and ruin them for life, ruin a good future that was going
    to be possible with them. That's when Chris slams his hand on the chair's arm, all four legs on the floor now.

        He can already see the chemist standing by the door, playing with his phone, waiting for him to let him go; that's why he told him to take
    the day off. If he found anything he needed help, a simple call would suffice. The chemist would just be annoy for the rest of the time and
    he didn't have time to mess around if it meant replaying all that video again. It was best to leave him out today. "Four hours and I have
    yet to find this scum."

        White walls, gray counters, features exaggerated of the sinks, students always moving at a boring pace. How can he tell if its not one
    of the students he's already seen that made it, being ignorant about what they were actually doing. "No," Chris thought, "there was a teacher
    there, he would have noticed something like that." Resting his hands on his legs, he keeps watching the same scene with different actors,
    some more frequent than others. 

        From all the clips, he started to like the parts where no one was there, less worry levitated among the atmosphere. As the night grew
    older, he grew more tired, eyes difficult to keep ajar. Fighting fatigue, the room became slightly distorted. Counters extended to others so
    the only way to walk through the corridors was to crawl. Approaching the television, he rubs his eyes, hoping to see the illusion disappear.
    It doesn't.

        A stranger passes through the phatom extension of the counter, pushing a cart next to a sink. Safety goggles, white robe, blue gloves,
    a black notebook and pen. It's rather quick how he manages to get everything on to the counter and starts grabbing glasses within a few 
    seconds. With an open notebook, he takes a quick glance at the writing and starts pouring. He always overflows but siphons it out with a
    pipette.  All glass flasks place around him, arm lengths away while he swiftly transitions from one procedure to another, taking advantage
    while the others need time to prepare. 

        Chris only sees the strangers back, arms lifting up and liquid disappearing in him. With both containers empty, he moves both of them
    away and places the filled container to the side of him. As he holds a jar, he starts to walk away from the sight of the camera. "He knows
    its illegal, knows the cameras are watching." On the lower left of the video, he sees the stranger walking into a dark room. It turns red
    and Chris gives up on trying to identify him, deciding that all he can do is watch his prey. With a mask covering his mouth, he opens the
    jar slowly and places a few scoops into a beaker. After weighting it, he puts a few grams back, closes the lid and puts leaves the beaker in
    the room.

       Back in the light, he packs only the active flask and glass and places them on the cart. He then returns to the red, moving in the same
    speed despite the loss of lucidity. Leaning closer, "Is he making lsd? Seems to risky to make in small doses." The strangers brings other
    fluids to dance together in a new, larger glass, giving them time to be acquainted before adding more to the party. This ballet lasts about
    40 minutes and then the stranger adds the final ingredient, the ergot. It percipitates, foaming on the top and congulating on the bottom.
    Chris doesn't fall out of his chair because he knees under the seat, hands pushing down and away from where he's leaning.

        Round and round does the solution go as he swirls it, holding it to shoulder height, paying close attention, making sure it mixes evenly.
    Done, he grabs a rack of test tubes and starts filling them up with a pipette. After a minute, he's done filling all five of them. The 
    stranger grabs the filled rack and goes next to a machine, similar to a hockey puck except bigger in width and length. He places all of them
    in there, sockets. From vertical to a slanted horizontal, the tubes spin around, faster and faster. In this procedure, Chris sees something
    start to form on the bottom, white.

        The stranger comes back a few minutes later, doing who knows what, with a vile. Going one at a time, he sucks the liquid with the pipette
    and pours all of into the vile. It takes all five for it to fill up more than half. When he saw him place the vile in his pocket, Chris
    expected him to just run out, waste no time to be caught. The stranger didn't, he took all the glass he was using and put it in the sink.
    As he started washing, a class came him and just considered him part of the park. He didn't alter his posture or even react, he kept on
    washing the supplies. Scrubing the pipes with a brush, washing the pipettes by sucking soap water and regular water into it and hanging them
    on a rack with wooden post for each type of glass.

        With that, he leaves while passing through a few students, them writing everything the teacher says, a few texting underneath the counter,
    glancing once in a while to see if the professor was looking at them. He moves to the door as a ghost to them and leaves.

        Still following with the camera, he sees the guy give back the jar to the worker. He types it in and returns to the stranger his i.d
    card. "He had to hack into the system remotely, the worker was telling the truth." But the stranger didn't leave the building yet, he 
    was on the premises, reading a book with a red cover on it. About twenty minutes later, he closes the lid and returns back to the worker,
    telling him that the class in the lab needs more carbon monoxide. He then shoots to the back and comes out with a jar on a cart, going to the
    labatory. As he passes the stranger by, the stranger walks into the office and sits in front of the computer. With a couple of keystrokes,
    Chris sees the criminal erase his presence. Leaving nothing to discriminate or persecute, his determination to catch the criminal set into
    a blaze.

        "Like hell he not." Chris says aloud, reassuring himself that he was still conscious. The first sighting of him gave nothing away from
    the criminal except that he's a male, about the same age as the other students. The taste of having found more than he was supposed to gave
    him a rush to keep going, watch more tapes until the sun rose. His only objective now was to capture this scum, do his duty and reach
    the expectation of the Sheriff. A growling stomach cries in vain, mouth desiring no food. There has to be more than one sighting of him,
    it has to be him that caused the previous jars of ergot to become empty, Chris thinks to himself. Nothing more he can do now is just wait
    and see.

\section{10, help}

        At seven, Roark guesses he has about 2 hours before Athena gets here, so why not use the time to try another trial since sleep has
    decided to be angry with him. He takes a tab, places it on his tongue and lets it dissolve. Breathing slower, he gently reclines on the couch,
    legs up on one side and his head on the other. Comfortable, he starts relaxing his body one part at a time, feet first. He imagines them on
    sand when the sun is out, bright. His feet sinking into the smooth, warm sand, purifying them. Next, his legs experience a warm simmer of
    water as they posture themselves at an angle, crossed, in a suana. 

        To his stomach, he recalls the warm steel cut oatmeal with bannana, blueberries and pomegrate. Hunger has no place in him and everything
    below his chest is as comfortable as a pillow. The beats go slower, chest expansion taking longer pauses in between. His neck becomes bamboo,
    flexible to go with the wind while strong enough to keep the head connected to the body. Before losing consciousness, he's on his 23 monitored
    breathe, voice soft but loud enough to hear himself. From ajar to close, his world becomes black and stays back when he regains consciousness.

        On the floor, Roark looks left and right of him to see anything else in there. "Of course, nothing here as usual. All the excess is gone.
    I wonder what I'm going to do now." Checking the area, he decides to just walk in any direction to prevent himself from sleeping. Holding his
    head up by putting his hand on his head, swerving left and right. Further along, he crashes down, one leg laying on the floor while one has
    its foot on the ground, knee above it. Thats when the absurd shows itself.

        He feels his ears tingle but watches the sound of music come to him in the form of waves, in color. Varying in size and color according
    to loudness and intensity. When they make contact with him, the complete inside of him and disappear. The yellow waves are the most vibrant
    and what attracts his eye the most. It takes a while before a complete circle of yellow only to take form in him. It doesn't disappear. 
    Instead, it appears as a yellow shirt on him. That's when the waves leave his sight and he hears them instead.

        Up, his body becomes easier to manage, feeling light. He then inspects the shirt he has, it has black markings on it. Taking it off and
    holding it in front of him, he checks the pattern. At the same time, the waves turn back into colored phantoms and move closer to him.
    He then gets a flash of all the yellow shirts on the other side of the river, the yellow raft he was floating on, the little boy. It's his
    shirt, the yellow shirt, he says to himself. He then saw why he had to help him, why he had to worry about him before Athena.

        Ding, ding, ding, "Open up, Roark, you're going to make me late." Up, he opens the door and finds Athena dressed in a red business suit
    with some tailored enhancements. "Are those shoulder pads?" She punches him on the chest, "Thanks for making me laugh." As she walked in to
    review her papers one more time, Roark stood by the door, holding on to it, trying to recover from his experiments. He couldn't let her 
    see him weak so he became more aware of his body, shoulders down, head up, an relaxed gait.

        He sets tea to boil until Athena says that he won't have enough time to make it. She was already packing and Roark decided to forgo the
    tea and keep up with this captain. She first out the door and him after, yearning for some tea.

        On the street, Roark legs feel tight keeping up this nervous suit. "You don't have to there when the conference starts so why are we
    practically running to it?" She turns at him, rolling her eyes, "I know that but my presentation starts in half an hour after that and 
    having everything set up takes a while. Don't want to keep anyone waiting for me when I wouldn't do the same." Her feet moving with more
    haste, Roark obliges and stays right next to her.

        "So, give a taste of the presentation." She must have been waiting for this question because right after being asked, she performed while
    her legs kept her on track. She first started with numbers of her company, how its doing in the real world and its potential. She accepted
    that Roark couldn't look at her all the time because he had stopped her a few times from going to on going traffic. It felt like the world
    was spinning for him, moving fast, noises everywhere and having to be considerate of her presentation.

        A few nods, sounds to let her know that he received the message. He already saw the building where she was going to perform and had
    ceased talking. All she could do is keep her eyes on the skyscrapper as she had finally earned it. Roark guided her through the sea of people
    as she kept herself fixed on her symbol. "Snap out of it princess, you're here."

        By the doors, both see swarms of people on the lowered floor, mingling and waiting for the sessions to start. When he turns around, she
    has left. Right after that, he gets a message on his phone saying where she's going to be at. He smiles, "she's just like batman." 

        Having left the house in a hurry, he goes to the food section and finds tea. A silent disappoint sigh exits his mouth as he sees the
    higher price brand tea in bags. "I don't care right now," he says, "its going to help more than the coffee or water." His first taste of
    the mass produced elixir gives him a boost, enough to go on for the hour. Body still cold despite taking the warm tea in, eyelids levitating
    too close to each end, fatigue is on him like a child jumping up to hug him.

        Passing all the people who are on their cellphones, tablets, bluetooth headsets and the electrifying young eager students, Roark enters
    the room where Athena is going to have her session soon. Almost all the chairs are filled in the room as he makes his way to the stage. Before
    going behind the drapes, he takes a view of the audience. Distinct clothing styles. There were some who wore suits with flair, people
    he felt he knew that they didn't need to wear glasses, others in loose clothing that could fit a twice the owner and a few who wore the 
    clothes that were fit well. Those were that either had a phone tucked away, holding on a notepad and pen or were had vim opened on a 
    laptop that didn't have a fruit on it.

        He finds Athena next to a table back stage, her bag thrown on it with everything out. Running her hands in her hair and then letting
    go as if her head expanded, "I can't believe I forgot, I'm so stupid. What am I going to do now?" Roark puts his hand on her shoulder only
    to have it slapped off, "Who do you think you --oh, I'm sorry Roark." He shakes it off, "I don't need pity right now, I want time to be on
    my side but its pressing to a corner." "You could always go ahead without it." Her lips tighten from side to side, as her eyes, "Or you
    could go get it now and be late and be awesome." 

        At that instant, she was gone again, sprinting towards the emergency exit. Roark looks at the clock and its five minutes before her
    session. "She going to be at least half an hour late." He then returns to the stage, checking from behind the drapes to see how the audience
    is doing. Coughs are heard clearly from around the room, people constant readjusting themselves on their seats. Cameras with the orange light
    on, music softly leaving the room and people near the door considering whether to leave or not. "I really don't want to go, don't want to."
    
        Memories of him watching Athena working on her laptop in the living room while he rested on the couch, both laughing. She was the one
    who introduced him to acid and was there to keep an eye on him during the whole trip. But she knew that she couldn't be holding his hand
    forever and yet couldn't just leave him by himself. So she spent the whole night with him, working on proposals on her laptop while Roark
    was in a space of colors that danced according to the music, she offering soft suggestions that appear in his trip. 

        When it started to get cold, images turned to monsters, black with some light flickering on him so he can still see the creatures of
    the night, she held his hand, physically. Her laptop closed, she besides him while they were under the blanket, trying to probe the 
    world they called reality.

        He found himself on stage, all the eyes on him, liquid and crystal. Standing there naked, more unprepared than Athena to those who can
    and will judge him. Taking a deep breath in with his diaphram, he says, "Just in case I have to state it, I'm not a girl." There were a few
    laughs from those with the notepads but the suits still kept their legs crossed and heads tilted away. "Thanks for waiting and if you wait
    a little longer, a better looking girl will come to replace me, so just get comfortable while I give you an idea about git writer." Some eyes
    peered over the lower glasses, "I have no slides right now and that's because I think they're inferior, never high-definition than what
    everyone in here has." All the audience members were looking around for a new device lurking in the session, some googling it. "Its electronic,
    and we're all given one since we were little. Our brains." Brows were raised.

        "For this to work, people have to be experts with this tool and all in this room are. You use a combo of imaginary to create, either art
    or applications or even startups. You don't accept the status quo, you know how to make it better and you take a shot at it. You guys are
    able to learn from failure and willing to do more than the standard." The suits were leaning closer, the glasses were tilted up and near to
    him. "I'm a creator so I'm not an expert photographer by default nor do I have the cash or time to spend on fancy pictures that will be
    filtered out when important info is given."

        "So to begin, start with one of your long nights where you been working on something. Either code, landing page, proposal or writing.
    We true geeks out there know about git and its an invaluable tool for source code, especially when a change can break the code. The idea
    for git writer is that some work should have an undo button and be able to compare previous editions of our work. For geeks, all they need
    is the cli and they know how to use it. For writers, its best to leave all the complicated stuff out of the head and put it on the computer.
    Writers are lazy too which also makes them great hackers. We rather make a G1-pilot using Monteblanc ink rather than buy the expensive pen
    itself. I doubt there's been any hack that turns a 3 dollars into five thousand dollars." People clap for the hack, a few laughing for the
    genius of it. "But I digress."

        Walking to one side of the room while keeping an eye to the audience, "In essence, is backing up every change done to a paper that is
    useful to the writer. For what has been common for writers is to edit their work after some time. A human is flawed and will skim, missing
    parts that can be improved on. This is where a computer comes in, giving all the data about their work into a graph or numbers so they can
    get a better picture on how to improve." The camera zooms in closer on to Roark before the curtains come to a close.

        People groan and Roark is left bamboozled. Looking to his right, he sees Athena by the switches of the stage, brows pointed down, hands
    planted on her waist, standing up tall. Going up to her, "I want to --sabotage my work, don't. DON'T SAY ANYTHING. I don't want to hear it.
    Leave, I had enough for today. Get out before you make things any worse." He saw Athena restraining her hands from choking him and thought
    it best to leave for now since it was apparent that fatigue was trying to help him find his bed. Roark goes out the door and the curtains
    open with Athena in the center with her slides.

        His legs are struggling with keeping him up. Collapsing by putting his back on the wall while next to the exit, Roark eyes close many
    times, he trying to stay awake. Just when they're about to seal, he pulls them furthest apart. He can't hold on forever, she's going
    to win and he'll be asleep. "I have to keep going. I have to ..."

        The door opens and Roark's fatigue is gone. Its Athena and with her index finger, tells him to follow him inside. Everyone else had left
    and the stage is quiet while he waits for her to speak. "Roark, you're a good friend but too much of a hassle." He wanted to say that this
    was the first time he did something like that to her but realized it would be better to keep his mouth shut, nod in agreement. "James
    wouldn't have thought about doing such a thing and neither would Mary. Both would have offered to go back instead and let me handle my
    own problems involving them," she points to the chairs off the stage.

        "What I am trying to say is I can't take it, its over, Roark. Don't call me, don't try to talk to me and don't even try saying 'hi' to
    me when you see me. We are now strangers to each other and its rude to assume that I'll be nice to you." She leaves through the fire exit
    while flipping the light switch before leaving. The lights stay on and Roark's replica statue stands like a child who has seen their friend
    for the first time in a coffin. He doesn't know how to react, to cry, run after her, laugh, break stuff? He looks inside himself for something
    besides his brain to tell him how to react, he continues to stand as a cold statue.

        Later on, Roark walks on the bridge at night. A fog covers this 2 mile bridge and cars come and go like ghosts. Stars covered by the
    gray bland silhouette give more fame to the light posts. Roark's head tries to figure what to do, he has to do something. Someone near
    and dear to him has left and it was according to his character that caused him to do the action that made it so. Only he would have gone
    up in the stage and help Athena by keeping them occupied. James wouldn't have done it, "too many people, she'll be back soon. They can wait."
    But then Roark could already imagine people leaving, giving up on her without letting her have a chance. That majority was there when she
    first started out and were there in the session, willing to use any excuse to leave since she didn't come on time.

        She has spent more time with them, its her speciality. "Me, I'm a kid wandering around a different reality, check each one and what I
    am capable of." He looks down to the water straight below the bridge and to some distance away, a ship. He keeps his right hand hovering over
    the railing as he continues to walk slowly, head down. "James fits in right yet he hangs around with us. She was my friend and I was hers."
    He now sees James with his crooked smile when he had to listen to anyone else except him or Athena. To them, he always tried it even though
    it look like a bad idea but when it came to others, he objected with a smile.

        A few stones fall from the top of the bridge, all the way to the bottom, the sound like a bubble popping. Closer and closer does the 
    ship get to the bridge, its horn with its low sombre cry walks into his hearing. Holding on to the railing with two hands, he tries to get
    a view of the city and fails; the gray omnipresent fog denies him this slight pleasure. Taking a deep breath in, he closes his eyes and
    becomes aware of everything aware him. The ship comes to mind first, its white hull that had gone against years of waves, ice and dents;
    those dents as sign of its age. The old metal vessel. It still goes on.

        Then the waves make their appearance by increasing in strength; clashing harder to the support columns of the bridge, ringing the buoy
    off somewhere in the fog, making a clanking noise when pushing the bridge. The waves want to push the ship away from the bridge, to go back
    to the sea. Poseidon is furious with this disobident mortal. Wave after wave, the ship is lifted higher, its end almost reaching a 90 degree
    tilt. Roark is expecting at any moment to see the ship turn at any moment, no one is that crazy to go against the bidding of the sea.

        The fight between water and ship approached the bridge to the point where when the wave have lifted it up, Roark could have literally
    walked on the ship if the railings weren't there. The battle was now underneath him and it started to rain. Winds blew hard enough to keep
    me pressed lightly against the railings. Thunderbolts strike the clouds, lighting the area. Its sound comes to him in less than a second.
    Looking up, he sees the wires swing to and fro.

        Running as fast as he can in a wind that is trying to keep him still, full sprint is a jog in this storm. "I have to get off," he says
    loudly to himself to motivate him to keep going. He runs as drops of rain hit him faster than a showerhead, his clothes drenched in water;
    add more to his challenge. He then hears a snap about 2 miles from behind. His brain neurons fire like firecrackers. Faster, faster. His
    legs feel empty and sore at the same time. "I can't give up." 

        Running, he hears a loud crash of metal and metal. The ground he's running on starts to rise and up ahead of him, it bursts open. His
    eyes open wide for the instance but then he returns to the here and now, swings his arms faster, hits the ground only with the balls of
    his feet. On the 3 meters before the edge, he watches his footing and adjusts it so his last step is on the edge before flying into the
    air. His legs run in the air, the sound of the wind takes longer to reach his ears, eyes dialate and he sees that its further than he 
    expected.

        He hangs on the broken edge of the street, limbs feeling faint and legs swinging to the winds desire. To lift himself is like lifting
    the ship along with him. He sees a light holding the contour of a person. His arm reaches over the edge.

        A bee the size of his palm starts buzzing in his pants. On his cellphone, all it says is, "We need to talk."

\section{11, pew pew}

        Sitting on the floor in a lotus position, in the living room, his ears each hear a different frequency. Consciously controlling his
    breathing so only ten breathes per minute, the outside of the apartment leaves his thinking. The door dissolves, the kitchen fades to white
    and he floats in the dark void. One hit and his whole imagination burst with colors, organic lines going according to a faint melody of
    heaven in silence. 

        From a small bean sprout to a several stem extending out of it, lines turning back around, swirling in chaos. Going according to
    the patterns of electrons in an ion with less speed, the mind imposes a figure on it.

        Beyond the metal railing, mountains clash among another in the sea. From small welters vary from spot to spot; instances of tsunami
    occuring on nearby islands, swallowing them whole. Roark stands in the rain, "Why is Poseidon angry with me?" Recalling his most recent
    quarrel with the sea and the bridge, he tries to find some connection. Light shines upon the tab he's taken before the conference; he also
    checks on the music player. Two different methods that modify the brain, giving hallucinations. "Not that similar for now, should let the
    ideas simmer for now."

        Straighten his unbutton shirt in the rain, sliding from top to bottom, he wicks some water off. The storm is harsh yet somehow Roark
    manages to keep his eyes open in the millions of water pellets in the air. Water in the sky and on the ground are both angry; always in
    the middle of the argument. His body gets rocked to the wall from a wave the pushes against the left hull. His hands jumps repeatedly on the
    wall, trying to find something to hold on to. "No bridge, no other way to escape. Surrounded by water."

        Shifting his focus from the sea to the right here, right now, he sees the yellow shirt standing in front of him, his two hands holding
    on to the edge of the railing. Head over it to get a better view of the blue chaos in the gray fog. Roark joins him by going to the side of
    him, close enough for the child to grab him. Looking at the abyss, he hears a bell ringing as if it were being swung by someone. A
    picture of a orange buoy moving up and down, swing from side to side and its bell hanging just below the top comes to mind. Keeping his eyes
    on the ever so distant buoy, the yellow shirt says "We have to save her."

        Millions of ideas spark in his head and most of it get filtered rapidly, tailored specifically to this situation. Being left with a few
    choices, he makes the assumption that it has to be Athena. It wasn't impossible to see her here but to what purpose would she be here for?
    Besides the kid, he was the only person here. Maybe ... "there isn't any time for that, I have to save her." Roark then looks to the child
    and asks who. "The ship."

        A tug boat with tires all around it, 1950's, and has been abuse for too long by the sea. "We have to save her, she's all we have left."
    Roark decide to think about how the ship relates to him later -- considering its a she -- since from a distance, he sees something almost
    surface. It doesn't break the water surface but the size of indent it made before return down below looked like it could swallow the ship
    whole. "The ship can't outrun it," the child says, still not looking at him.

        "You're going to lose, nothing you can do about it. You're nowhere near land and water is all around you." Grabbing on to his behind
    his head, he tugs it back a little. The kid is now facing him, "he's here." Roark then checks the ocean again and sees that a colossal wave
    is approaching them. The bold dark skin shows beneath the light blue hue of the water. "That wave will be the end of you. It will throw
    you to the sea, into the savage chaos of the waves and eat the ship, sending it to the depths of hell on earth. It will be crushed and 
    impossible for you to reach."

        He runs to the cockpit after grabbing the kid and locks the door. "Is this the best you can do? Hope? Ha." Rapidly turning his head in
    the room to find something, he sees that a table is bolted down. He puts the kid down there and start building a fort with odd length boxes.
    He puts one between the kid and the legs furthest away from him, the box being longer than the table. Three boxes provide a space where
    he'll be safe from anything flying in the room, including himself. Checking the window, he sees that the wave is about to slam down on the 
    ship. Grabbing on to the vertical bar and wrapping his arm around it, he puts his back against the wall and gets ready for the showdown.

        The ship becomes enveloped water which tries to ram itself inside; the door being a formable opponent. The window shows a fish swimming,
    light being distorted by the water and the shadow of the monster. Objects thrown everywhere, Roark asks if the kid is fine, "Wow, that
    was fun, lets do that again."

        "Stay down there, I don't think where done here yet." Right at that moment, the ship is hit by the monster, causing the ship to spin
    vertically. Roark sees the ceiling become the floor over and over again until the window becomes the floor. "We're not going to last in
    here long, I have to get the ship out, save her, save him." The idea pops into his head, he jumps close to the window and starts cursing at
    the monster. As Roark looks down, the monsters appears from the distance, small; however, that lasts seconds as it headbutts the ship.

        Like a lifesaver under water, the ship pops out of the ocean right side up. Roark is slammed by the ceiling and the falls to the floor.
    "Are you still okay?"  "I'm scared, I want to go home. Please. Take me home." "If you want that, help me save her." Watching the boy crawl
    out of his fort, Roark sees a picture on the floor. Picking it up, its his elementary school picture. The boy goes to the side of him to
    get a view, "I like this picture."

        A picture of Roark in 2nd grade, everyone smiling to the camera while he has his head directed to the left. "What were you looking at,
    Roark?" Trying to find his way back to the picture, he notices that has his mouth open and eyes open high. He's now picturing himself among
    the rest, most of them owning a toy cellphone. The memory of his sight is blurred to black. The only thing that pops to mind is that he
    could have either been looking at a butterfly or an explosion but can't tell which. Maybe it was both.

        Shaking his head, he turns to the boy and asks, "You must know something about the monster out there, you knew it was out there. You
    weren't worried about the ship being destroyed by the storm, you knew it was coming for us. Talk!" The child had back away to the controls,
    head down, sobering. The cries Roark heard made a ringing in his head, piercing his thoughts. He looks at the child again, "Who are ..."

        The door is thrown open by a wave and floods the room with water. Receeding, the yellow shirt holds on the side of the door. Another wave
    comes to retrieve the prize and Roark jumps along for him. Both are carried out of the room and the water returns back to the sea.

        On the side of the ship, Roark holds on to the child while holding on to the railing. Putting his arm over it, he swings the kid up first
    and then gets back on the ship. The kid is already waiting for him inside the door; Roark gets in, locks the door and puts a box to press 
    against the door and the opposite wall. Resting on the box, Roark catches his breath while the kid sits under the table, holding on to
    the leg closest to the wall. "He's after me," the kid says, not looking at Roark.

        "Just take the self-inflating liferaft in the closet, the storm is nothing compared to the monster after me." Roark checks the window 
    again, "the monster hasn't figured out that he had held on to the boy." The ocean more at rest now. "Leave, Roark, leave. He lied to you,
    the monster doesn't want you. Besides, he just one human, there's many of those every on earth." The picture of him in elementary had
    sailed underneath his legs and this time, the picture included the yellow shirt kid.

        A flash of being in school with him, his friend. Everyone making fun of Roark for his choice. He didn't know why they would laugh, the
    yellow shirt is just like them. Then again, he isn't and that's why he's friends with only with him and not anyone else. The memory then
    flashes to weeks later, him by himself, reading. Roark then looks to the yellow shirt, "Who are you, really?" The boy turns his back to
    him and hides his head in the shadows, refusing to talk anymore. Waves start to jump again. Roark then decides that he should give the
    kid more time, he almost disappeared.

        Water beings weltering again, "he knows," says the little boy. Taking the box that he's sitting on, he puts another defense in the
    boy's fort, goes to secure himself on the bar and with his back on the wall, plants his feet on the door. He sees a bigger wave than before
    lunge itself to the small carrier and Roark hopes he can keep him safe. A whirlpool in the room was the manifest of the giant monster outside
    of the ship, wanting to get a hold of the yellow shirt. Both of them were blinded by the thrust of water in the room and only seconds later
    is he capable of opening his eyes, finding the fort empty of boxes. With the room still fulled more than half way of water, he dives into
    the water again to find him.

        He checks the closet, underneath the controls but he's gone. The monster has taken him. "There's nothing you can do now." Standing up,
    he sees a yellow shirt bob out of the water. He grabs it, wraps it around his left hand and looks at it. Circles, circles that are by
    themselves, connected to others, all filled in black. He then punches the wall with his right, once with his head down; another with his
    brow down. Observing the ship is still on the surface, he tugs the door open and all the water inside overflows off the ship. He keeps his
    hand held tightly to the yellow.

        "He needed you're help. He knew if the ship was safe, he would be too. You wouldn't let anything happen to him. He put all his trust on
    you. He never expect to live though, that you would give him more time than he thought after you threw yourself after him. Save the yellow
    shirt, don't let the monster get it."

        Hands try to compress the sudden expansion of his head, eyes shut, knees on the floor. He's then pushed to the side by a wave the jumps
    on the ship, landing on his back on the rear of the ship. An anchor hanged and a harpoon gun mounted on the east of the ship. He needed to
    find an island, get off before the whole sea turns on him. Picking himself up, he runs into the cockpit and looks through the mess for a
    map. Placing it on the bolted table, he uses the compass to help him estimate his location. Everything about the land looks foreign to
    Roark, "must be a locally scaled model, small scope." He then dismisses the criticism and focuses on the task at hand.

        Marking the best spot where he could be wandering, he then finds the closest piece of land near him. 35 degrees south east. He then
    grabs the meter large anchor and hooks it on to the harpoon. He directs it to the land and shoots, the anchor flying in the water like a 
    torpedo. Waiting for the rope to stop and then tighten, another wave rams into the ship, he injuring his left arm. The yellow had helped by
    comforting the blow but now his arm feels limp. He keeps looking at the rope, hoping it will stop soon.

        The monster attacks again from behind the ship, causing the rear to dip into the water and propelling his body to the air. He would
    have been drowning in the water if he yellow didn't get snagged in the harpoon, giving enough time to grab on. The ships bobs up and down
    from front to back and his body hits the floor. Getting up becomes arduous, able to begin by lifting his knee first and then letting his
    momentum build from that. Standing by the harpoon, he sees that the rope had stopped.

        A pull of the lever starts yanking on the ship which in turn pulls the ship closer to land. Its pulling so fast that the rope would set
    on fire if water wasn't around it. Roark saw land from a distance, his breathing was becoming easier. Trying to keep his head up, hand still
    holding on to the yellow shirt, he thought he might get through this. On the side of the ship, water becomes a mountain extending higher
    than the ship. It slows down but hits the ship on its rear left. The ship spins ahead of the rope and Roark holds on.

        The ship does another spin while being brought closer to land. The monster follow in the back, always remaining a black bludge from
    the sea. It then dives back into the water and Roark keeps alert for its next visit. The ship is almost close to the land, he can see the
    coast. Just before the sea level started to decrease, the monster makes its final move by jumping over the ship, starting from the front,
    breaking the chain in the process. It happens so fast that Roark only sees a black smudge jump in a semi-circle over him. 

        Still going closer to the island while losing speed at the same time. He then saw the monster starts forming a giant tsunami behind
    the ship. "Its nothing in the water, the chain is underwater." He runs to the front of the ship, steps on the railing and dives into the 
    water a few seconds before the ship is consumed by the wave. From below, he sees the ship torn limb from limb. Drifting to the side of
    him as he watches the result of the masacre, a chain tickles his ear.

        He grabs on and pulls, one hand after another. "You know the rules." He pulls for a while until he reaches the point where he can just
    start walking, most of his body now out of the water. Shoving his legs forward to finally get on land, he takes another look back to the
    chaos. Only pieces of wood are floating at the boy's grave.

        Holding on to the yellow shirt, Roark turns to the island, mother nature's untouched paradise. Kid gone, storm gone and silence humming
    in his ear. The only noise comes from his head, "how long have I been waiting for the kid? Why am I waiting? Who is he?" Pacing by where
    the water extends furthest to the shore and then recedes, Roark stops and lifts his left arm. Without warning, the wind picks up and throws
    him to a palm tree.

        Soft cushion on his back, arms being held up by something. Opening his eyes, he finds himself back in his home. Recovering over the
    lucid hallucination, he runs his hands through his hair. That's when he feels a cloth slide against his face. Extending his arm, he sees
    yellow.

\section{12, Mathematical Induction}

        "No!" James says with his arms closed, face turned away from Roark. "You're not going to get hurt. All you have to do is only check 
    for something. As the developer of the experiment, I'm prone to some bias. That's where you come in, fresh eyes. You can spot inconsistencies
    better than most." James faces Roark. "I can reverse it effects if you experience the slightest discomfort."

        "So it is dangerous?" Roark shrugged his shoulders, "Only the user can make it so. If you can keep your head on straight to a new 
    experience, it by cloud 9. Assume the worse and you'll be plunged into the deepest hell in your mind." His mouth fell open, "Why would
    you tell me this?"  He locks his eyes on to James, "I trust you and I want to give you the tools to help you whenever I lose contact with
    you."

        "Have Athena do it, she has more experience with this. You don't need to sacrifice a virgin for science, act civil." James then watches
    Roark's head fall to the floor, and forgetting about the conversation. "What happened, Roark?" Roark gives him his cellphone and James reads
    the text message. "Roark, but why," It hit James that talking about it would make things worse, "I'll do it but you better get me out when
    I tug the rope."

        Roark sits on the opposite of James who is laying on the couch, headphones on and a vile in his hand. He gives Roark his final look 
    before taking the shot and then carefully lies down, lets the frequency be the focus of his mind and colors swim into existence. Red, green,
    blue, yellow and black play together in a invisible translucent liquid. At that moment, James forgets everything; about his the danger,
    about his deadlines, his needs except breathing. He knows he's sitting down even though his body hasn't come into existence yet, enjoying
    the display of colors in front of him.

        The stage becomes bigger, enveloping him. Colors longer, more vibrant; they fill a shape of a box. An unorthordox box and fill the
    contours of the objects in the space. Whiteboards, bookcases, kitchen, chairs; the sofa and him included. When the process is complete,
    it is an exact replica of his home except it all being drenched in a red hue. Amazed, he stands up and decides to take a tour. He lets his
    hand hover behind him as he goes from one wall to another, trying to find the crease in the prop wall. Everything is connected. The 
    whiteboard feels the same as he writes an equation with a marker.

        With his bookcase, he pulls a book down and checks the contents. All the words are there. He wonders if his favorite new book that he
    didn't get yet is on it and to his surprise, it is. He pulls that one and as he opens it, finds nothing. Now skeptical that he fell for a
    trick, he starts pulling more books out. Each one identical to the dimension he had came from, cover and contents. After going through 
    several, many being on the floor; he wonders why that one book is empty.

        "I'll accept it as real until proven otherwise," he says to himself, seeing that this world is almost an exact copy and that it would
    be better for the contradiction to manifest into something concrete. Turning back to the couch, he backs to the wall. There's a little
    boy on the couch. His heart is racing as he alludes to the last time he had a visitor in his dream. With a book at hand, aimed at him, "What
    are you doing here?"

        The boy sitting on the couch, feet hanging, "To help" he says as he plays with his feet. James keeps the book on him still. "I know
    you have a monster lurking here." The book hits the floor. Taking a seat opposite to him, "So, how are you going to help me, are you a
    weapon or something." Kicking his feet higher, "Nooo. I'm here to help you do it yourself. Think of me like a cheerleader without the
    proper attire." 

        He grabs the book again from the floor as the red gives him more flashes of the quarantine he was in. "That thing could learn, adapt.
    It can think." The kid is now laying on the couch, feet over him, "The source, you have to disconnect it from the source." Recalling
    the monster, he never saw anything connected to it. If it had something, he would tripped over it by then in that whole fiasco in the
    room. "Why should I trust you?"

        "The monster lives in your subconscious, if you can destroy him here soon, he'll destroy you by subconscious control." His perception
    changes to where he notices his body inside the room and wonders what would happen if some takes the control panel. His work, that would
    be to easily proned to destruction, his friends, Mary. He shakes it off, "fine, I don't want to risk losing my work. How do I fight this
    thing?" "Disconnect it from the source." James watches as the boy rocks back and forth while holding on to his feet.

        The idea of him losing against the monster comes to mind, how will it affect him in real life. Does it wake him up or will the monster
    wake up in his place. Either way, the monster won't leave unless he stops it so he might as well take his stance here and now. At that
    moment, a siren starts to scream quarantine. A revolving orange light emerges from the ceiling and the room begins to spin. He runs to
    the kitchen and arms himself; cast iron frying pan and a knife. Up against the corner, he sees that the couch is empty. "Was he the monster?"
    he thinks to himself. "No." He had a feeling it wasn't despite the controversial answer of the monsters destruction.

        He pulls out a kitchen draw and lets the metal fall on the floor around him. His book case falls down, breaking the coffee table in
    the living room. Some of the sofas are shoved, the whiteboard has nails running on it. James decides to put both hands on the pan handle
    puts it across his body as protection. Then it becomes silent underneath the noise, the monster has disappeared from his perception. With
    eyes shut, he tries to hear the monster's faint step.

        A loud piercing roar of pain fills the room and James goes directly to it, swinging the pan from behind him to the creature. He sends it
    flying to the wall and jumps on it, shoving the pan to its neck. It is only then that he notices a blue infinity sign yolk on its neck and 
    waist. A headache strikes him, taking his eyes from the monster, flashing him pieces of his work that he had a bad feeling about. He can
    see the pen writing on white paper and then he thrown to the living room. Getting up, the monster jumps on the kitchen counter and roars
    at him. James throws his frying pan at him, knocking the monster down to the metal again. All he can think of now that he has to find a way
    to kill him before he finds the extent of the monsters anger.

        Grabbing a pillow, he stands in front of the bookcase. He waits for the monster to recover and watches it slowly approach him. Both
    see the other, the monster's blue infinity becomes James' obsession. The monster scratches the floor in front of him and then jumps towards
    James. They both fall down near the bookcase, the monster biting into it and pull off its skin. The bookcase falls as the monster takes
    away the white stuffing from the pillow.

        On the floor, tilted above the horizontal, James finds the monsters head sticking out, unconscious. From above the book case, he reaches
    down to grab the chain. The mere touch passes a reel of memories in his head, of all the times he hesitated; that the things he never did.
    Then it showed red slashes on his current work that he felt unsure about. The monster opens its eyes and slams the bookcase to the wall.

        James shoots up and falls back down on the couch, out of breath. Roark comes up to him with a water bottle, asking what happened. "I'll
    explain later, just give me another shot." Roark remember that he James volunteered and if he wanted to return, he couldn't object right now.
    So Roark grabs a vile from his bag, gives it to James who drinks it and lets the couch hug his body. He puts the headphones back on and
    lets the sine wave carry him back to the red.

        On the floor just like the bookcase is to the side of him, he jumps back to his feet and runs to the kitchen. He grabs the knife and
    scans the room. From the whiteboard with all the scratches to the door out the home, he sees the closet closed. "He's waiting" resonates
    in his mind. Doubt then infatuates his whole body, the knife shaking irratically in his hand, the other hand having to support his body
    because of wilting legs. "Quarantine, quarantine, quarantine," breaks some of his sanity, making him feel scared of what might happen
    when he goes in there, when the monster wins.

        Shaking his head repeatedly, "I have to do it, just do it, James. Why are you scared, you have been to go heads up with more than once,
    which is five times more than you could have." The numbers gave him a better probability of his fight with the monster but then other
    variables came into play that made a bet on him a long shot. Taking a deep breath in, "Nothing is always in my favor, might as well create
    my own luck."

        Before heading to the closet, he goes by the metal and picks up the frying pan he threw at the monster, "this has proven to be useful."
    He stands at the door, hand on the knob, having second thoughts about staying outside, "the monster will come out." As the red light shone
    second after each spin, all he could see were those red slashes. He lifted his chest, turned the knob and entered the closet.

        Surrounded by darkness, James already conclude that this wasn't his closet for having walked more than five feet without running into
    clothes or a wall. Looking back, the door was gone. So he kept walking until he found a wall and kept his hand on it as he walked parallel
    to it, waiting to hit a corner. His feet make contact with the other wall and that's when he hears a screech from the ceiling. Something
    flies at him -- not the monster -- and he manages to defend himself with the pan. He is knocked hard against the wall and he the pan falls
    to the floor. As he picks himself up, he finds the frying pan with a deep indent that could have killed him.

        The monsters head extends to the origin of the room while still hanging upside down. Hand on the frying pan, he throws it instantly at
    head and watches the monster fall down, through the floor. The lights stop swirling and he finds himself alone in the room, tapping his foot
    where the monster had fell into. The siren ceases to exist, lighting returns to white and James finds himself in his room, again. The only
    difference now is that everything is in blue. A skeleton of what his room is. Anything not bolted to the floor or wall is gone. He kicks
    the floor again, hoping it would do something.

        Figuring out that he's going to have a long wait here, he decides to test this blue room a little further. "If the floor can be a portal,
    so can be the wall." Just about when he puts his hand on the wall, he backs away and holds the knife by him. "He would have came after me
    after the hit, it always does." Still, he hesitates as he comes closer to the wall. With each small advance, the fear in him of the monster
    jumping onto him causes him to shake. "It stole the data from your head." He touches the wall.

        Different than what he's used to, touching the wall is elastic. As he retracts his finger away, the wall substance hangs on to a certain
    extent. Releasing his finger, the wall fills with ripples. A step back shows the ripples spreading to one wall to another, ceiling and floor.
    "I barely touched it and its changing structure." It was only the surface and he figured how deep the wall actually was. He returns to the
    wall and starts by first inserting his finger halfway. A pause, expecting to receive a shock or to come in contact with a solid surface. He
    continues by putting his hold hand in. Nothing. Half is arm is in and now he is debating whether or not to take the plunge. "I'm here," he
    says to himself and takes the chance.

        After a flash of light, he finds himself back in the room again. The wall is now behind him. Raising his brow, he sticks his arm into
    the wall and looks at the opposite wall and finds fingers waving to him. He taps the floor again, foot landing on the hard wood. It didn't
    make sense, these walls are practically the same as the ceiling and floor; including the fact that the monster fell into the floor increased
    the complexity of the situation exponentially. He lowers his head a little, this whole place doesn't have to appeal to logic, its just
    something that he craves from the world. Not here, here, it comes from him.

        With the new perception, he tried a new experiment. He walks into the wall in front of the couch and reappears in the kitchen. A jump
    onto the floor shows that its still rugged. "One out of two." He then jumps again, reaching for the ceiling and his hands go through. Back
    on the floor, he returns to the kitchen to get a chair. Placing it under the ceiling portal, he starts climbing closer to it. Right before
    he emerses himself completely, it snaps into his head that if he's right, going to another subset of this dimension, what's not to say
    that the monster is there, waiting or unaware of his arrival?

        Feet planted on the floor, he looks up the ceiling, visualizing all the possibilities. It should have attacked the moment James had put
    his hand through, pull him into the subset and killed him while it had the chance. He just couldn't figure out the numbers, the number
    of subsets is unknown, the creature's mental state is unknown. "I should stay here, I'll wake up or it'll come for me soon." Sitting on the
    couch with his legs resting on the chair, hands behind his head, eyes ajar, he imagines the green infinity sign on the creature. Its is only
    now that he realizes that he's been bleeding for a while, apparently not feeling it from the adrenaline rush of the fights he had recently.

        Resting, the room starts to shake, for a second, abruptly. It shakes again, making the couch vibrate closer to the wall. On the speaker,
    he hears, "I'm out so whatever you need to finish, do it quick." Down to his last match, James thought it best to go to the trap. Grabbing
    the worn out frying pan, he leaves the knife behind and gets on the chair. One foot on the seat and another on the reclining back, he
    bends his knees and jumps into the ceiling.

        At first, he sees himself flying to the new subset's ceiling until he runs of momentum and gravity takes over, falling down while
    looking up. He hears something rustle in the kitchen and that's when he grabs the frying pan with his right. James gets up and stands in
    the center of the room, directing all his energy towards sight, hearing, the right hand and his feet. The monster peers from behind the 
    counter to find James there, brows down, frying pan cocked back. This batter has to hit a homerun to be able to remove the chain of the
    monster.

        Two strikes and only one life, he has to hit his first try. The swing, the monster flies at him faster than he expected. James steps to
    the side, the monster lands where he was standing a second ago, turns around to his prey only to be swung at full force at the head, a
    swing that ran from the floor to the ceiling. The monsters head flies back, body spins in the air and falls face first on the floor,
    unconscious. Hands on his knees, trying to recover from the rush, he moves closer to the monster. Looking over its neck, it grabs two
    ends of the chain and unhooks it. He removes it from the creature and lets it hang as he holds it in front of him.

        Symbols, pen scratches ans slashes become more apparent in his head, red showing up on where he had a bad feeling about. A jolt comes
    of the monster but ends up being immobile. James steps back a little, keeping his attention on the green infinity. Then as he holds it with
    two hands, the size gets smaller, shrinking right before him. It takes the minute when it becomes the size of his hand and becomes animated
    for a while, wrapping itself on his right wrist. Several infinity signs in this bracelet of his, green and foreign to him. Just then, the 
    monster jumps right at him.

        With his eyes closed, James is shaken back and forth while sitting upright. "Wake up, James, you been out for a while." As he peers to
    the distant reality he left behind, Roark repeats, "Wake up James." A yawn, an arm stretched over his body and the other hand scratching
    the back of his head, smiling at Roark, "What happened?"

        "Your heartbeat, I heard it from across the room. What the hell was going on in there?" Lifting his right hand to Roark, the green 
    bracelet makes sound. Roark looks at him with amazement, "You didn't have that when I was here with you, did you?" James shakes his head
    and Roark pulls the yellow shirt from his bag. "I got something when I went down there but I wasn't sure until now", Roark's eyes still
    on James' bracelet. 

        Both lay on the table, a yellow shirt and green bracelet. James then asks, "Do you know anything about a kid wearing a yellow shirt?"

\section{13, Let's talk}

        When she looks in the mirror, she sees nothing wrong but for the occasion, there has to be something she can could use in her looks. 
    Being in a red dress already made her feel like an expensive slice, so uncomfortable to her standing or walking. Inspecting her face with
    her right eye, make up in her hand and the brush in the other, "Where?"

        Eyes trying to look above her brows to check on her hair. Longer than shoulder width, a few split ends; a pair of scissor and a comb 
    on the sink. A clip there, a clip to her right, behind her head, left and a little more. Hair still a mess, she starts combing it in front
    of the mirror, watching it regain its natural volume. After many passes, the comb returns to the sink and she checks her head again.

        She splashes water on her face, already putting the make up away. Any blemishes she finds are washed away with some soap. She adds a
    a faint pink chapstick to her lips and puckers them to spread it. Another check on her face gives her mixed feelings, satisfied since she
    can't think what else to do to herself.

        Her hands runs all over her arms, spreading a lotion on each of them. She works her hands and then makes a pass to her face, spreading
    while giving herself a massage. Rubbing her temples, her breathing reaches a serenity that she was craving for before leaving her home.
    Arms swinging freely, she walks to her bed, sits and puts on her shoes. When she stands up, she has an artificial growth spurt. Arms
    behind her, shoulders hanging down, she walks out her home and heads to the restaurant.

        An alarm rings in the darkness, saying 7:00pm. "Ugh," Roark grunts, the clock having disturbed his dream. With a sigh, he turns on the
    light and sits upright. Rubbing his eyes to get all the sand out, he stands and heads to the drawers. He pulls a shirt, some pants and
    puts them on. Back on the bed, he puts on his shoes while looking at the window. Dark and windy come to his mind which is why after he 
    has his shoes on, he grabs a jacket. He should be leaving soon but before he does, he writes down an experiment to try after he comes back,
    assuming he does come home before 9 pm.

        She stands leaning on the pillar of the restaurant, black boots on, almost in the shadows, going over some data that she's written in her notebook.
    The clock says its 7:35 and Roark still hasn't shown up. She checks down the street, then up; nobody walking by. Her foot starts to
    tap involuntarily while she bites on her nails, wondering if he's going to show up. Just standing here makes her look like a whore and
    wants to go inside already, to talk.

        From the alley, Roark emerges in the light and finds Athena leaning on the corner, hand to her mouth. He reaches to her, pauses,
    retracts his arm and says, "Hi Athena." She jumps in shock, "sorry about scaring you, I felt like wandering around a little before getting
    here. I'm not that late, am I?" Athena shakes her head, "No, I only this strange feeling that you weren't going to show up. Since we're
    both here, lets go inside, I'm cold."

        They sit at a small square wooden table, facing each other without making eye contact. She makes one more checkmark on her notebook, puts
    it away and grabs Roark's hand. His body goes further into the chair without moving his hand. "I wanted to explain why I blew a casket at the
    conference." This was not what Roark was expecting; he leans closer. "I had too much on my head at that time, you became another variable
    that I couldn't control and that's how I lost it. That was before I realized what you've done. When I go on stage after you, people were
    already hooked, the slides just reinforced the fact. I thought that when I got back, everyone would have left," she puts another hand over
    his, covering it, "but you did something, something that isn't natural to you."

        "You're my friend, Athena; I'm always will to extend myself to help those that want more. I saw that you were carrying too much by 
    yourself so I decided to help without announcing it." He puts his on the glass of water, "Don't give me too much credit though, you had
    everything in place, I only gave it a kick to get it started."

        After taking a sip of wine, "You're something I haven't seen before. Irish and Mexican, do you mind telling how that happened?" "Well,
    it started with my dad," he said as he was spinning his fork on the food, "he wanted to try New York after being in California for a 
    couple of years. After a few train rides, he got there with no money. So he decided to get a drink at a bar." Athena is leaning a little
    over the table, waiting to hear an answer to an implicit question of hers. "He didn't drink, lost the urge once he got there. It was after
    he got comfortable in there that he realized that he was in an Irish pub."

        "My mom was there with a few with of her brothers, drinking their asses off. Rarely did anyone go to her because her brothers were
    always ready to fight. Once they jumped a man for whistling at her. Another time they almost killed a man for trying to touch her breast.
    When he set eyes on her, she was nothing he was used to. A woman that treated her gender as a strength and not a weakness, having to depend
    on others to be happy. So before he got up to ask her to dance, an old man had stopped him with a cane. The old man said, 'I don't know
    what you are but if you go there, you're going to be attack by all of those guys.'"

        "Zooming out, he did see the guardians that surrounded the woman now but disregarded them. He walks up to her, opens his mouth and ends
    up being punched in the face. My dad fights back, even when the others join the barrel, including other bystanders. He takes out two by ducking
    in front of guy behind him and uppercutting the person in front of him. He then gets tackled to the ground and everyone starts to pile on
    him. He gets out by pushing a man down, stepping on his shoulder and jumps out of the pile. While they're busy, he goes back to her an ask
    if she would want to dance. Before her response, two guys grab him and throw him out of the bar."

        Underneath the table, Athena is holding on to the table cloth, winding it up tightly, spinning the cloth in two different directions.
    "He looks through the outside window to see her but finds her gone, her brothers still drinking. That's when she shows up from behind with
    a beer, saying sorry about her brothers, she their only sister, being the oldest of all of them. She hands the beer and as he grabs it, he
    feels her touch on his hand."

        "Why aren't you as Romantic as your dad, considering you hold that loving story in your heart. The one thing I noticed about you is that
    you distant, even with us. To add to the absurdity, you're capable of laughing at anything. I ... should stop, I'm not here to judge you,
    I'm hear to make up for screaming at you earlier, I was wrong and saying sorry won't cut it for me." Roark returns back to the text and
    realizes that he had misintrepreted. "Why is your jaw dropped, Roark?" Returning to the right here and now, "My bad, I just thought when
    you sent me the text, you mean't that you wanted to separate."

        "Separate, from you? No! James is nice but he's no you. I like your take on the world, always fresh. So enough about me, lets get down
    to business, what do you want?" Roark turns his face away while keeping his eyes on her, "I mean, what can I get you to make up for me
    screaming at you?" Scratching his chin, "Tell me about your name, Athena." "That's easy, Athena is the name for a goddess -- I know that,
    I mean't why do you have such a name?"

        She accidently knocks down her purse with her elbow and quickly turns to put it on her legs. "Oh, sorry for the jump, I just never been
    asked that before. If you really want to know, it was because of my mom."

        Both parents were cowboys, her mom being the best cowpuncher and her dad being a deputy. They had hit it off in a salon and two weeks
    later, got married in a chapel. My mom's name is Amelia and my dad always tells me that she hated the name, despite loving the letter 'A'. 
    Fast forwarding, for the three years that they have been married, my mom kept her condition incognito. My dad notice and wanted to take
    her to the doctor but she always refuse, saying don't fix what ain't broken. He would always add 'ask for help isn't a form of weakness.'

        It was only during the last three months of her pregnancy that her condition got worse and my dad had forced her to go checked by a 
    doctor. There, they found out that she has cancer and should have been dead a year ago. Hearing the news, she grab his collar shirt and
    said, "I'll make sure I last long enough to bring our child into the world."

        On their bed, a person dies and another is born. The baby was a girl and my dad being a bookworm, thought of the best way to reincarnate
    his wife spirit in me, he called me Athena. Even though most guys want boys, he raised me to become more like the wife he loved. The first
    thing he taught me was to read and I went on reading bienge considering my dad had practically a library in his home. I read about Plato,
    Aristole, Ayn, Aldous Huxley, George Orwell and others. He would always tell me,, "make your own interpretation of the book, don't listen
    to it verbatim."

        She pulls out her knife from her boot, "he gave me this when I was 5 so whenever he wasn't around, he knew that I could defend myself.
    Never actually had to use it but showing the other guys when they decided to pick on me made them turn yellow."

        Playing with her fork, "then came a time when my dad got a computer and told me that I should play with it, see what I could be capable
    of making it do. I refused at first when he brought it, wanting to stay doing everything by hand, saying that a machine can't properly break
    or care for cattle. He agree but again, the computer's purpose wasn't to replace our jobs, it was to make it easier. The computer is the 
    manifest of pure logic, giving you errors when you don't abide by those rules. A place where you had to pick your words carefully since
    it's taken very literally."

        Out of nowhere, Roark starts laughing. "What's so funny?" "I'm picturing what it would have been if your mom was with you when you grew 
    up." Underneath the table, she kicks him hard on the shin with her boot. She grabs her fork and is about to stab his with it until she
    remembers the last time she was upset with him, she didn't see things in his way. "Only for him."

        Then she closed her eyes and imagined a life where she and her mom lived together with her dad. He would leave in the morning and after
    making breakfast, both girls would be in the kitchen. As she puts the dishes away, both say that they are going to check on the cattle. 
    Her mom wags her finger at her, "you're too young, you might get hurt. Stay here and clean like a good girl." She would snap back, "okay,
    grandma, talking about me getting hurt. Looks like you'll break your hip just going outside." "Why you little brat!!!" Her mom would grab
    a rag, she would run away, her mom ready to hit her with the rag. Round and round they go in the home until her mom comes in front of her,
    grabs her and throw herself with her on the bed. Both would laugh, "lets clean the kitchen together, we'll finish faster and then we can
    go outside and have some fun."

        A tear falls across her cheek, smiling. "Thank you, Roark. Thanks for letting me be with my mom for once. My dad has never been able
    to do so since he was unable to get over her death." She puts her warm hands on his, brings it to her lips and kiss it. "Athena, I can't
    let you act like the gentlemen between us two, I'm going to take you somewhere tonight." He pulls her while she leaves cash for the meal,
    running out of the restaurant and into the dark alley.

        On the roof, Athena legs swing from the edge of the building as she watches Roark stand on the lighted billboard, the ocean being below
    it. After taking a breather, he jumps off the billboard and sits next to Athena. "I'm like a ricochetting bullet, the good I do will be
    based on those who observe. My weakness and my strength is I'm not like them, apathy is my core. I can lose interest in the irrevelant, move
    on faster than most and learn quicker. Where I fail is to be happy like them, its not possible with me so I don't try. Instead of wasting
    my effort on happiness, I'm allocating it to something else."

        Athena saw the people walking below her, a few couples hold each other close as the moved along. She knew that she didn't want that,
    she didn't want comfort with someone she would love. The same thing with Roark, the best he could be is a loyal husband but he would never
    want to be a husband nor father, others trying to reach to apathy can freeze. She grabs his hand and looks at him, "What if I told you I
    was dating another man, Roark." "I would say that you're your own woman and that no one can decide to take that away from you." "What would
    you do to keep me with you?" "I have constantly prove to you that being with me is a good idea."

        She couldn't see Roark with flowers at her door but being on top of building during the cold clear night was something marvelous that
    he was capable of. Never seeing Roark in love, she didn't know if this something he would do with a friend or someone he loved. Asking him
    right now wasn't right, both had things to attend to, after tonight. Best to leave the stress down below and just focus on each other for
    now.

        "Can you tell me anything about yourself, Roark. I was think you'll like the phantom of the opera except your face isn't deformed." She
    touches his face as she says it, resting her head on his legs, facing the sky. One blink and everything had a yellow hue to it; another 
    blink and everything returns to normal. "I'm fighting with something inside me that has been dormant for years until I decide doing my
    experiments. All I can remember is a boy in a yellow shirt."

        "Is he you, younger?" "No, he doesn't look like me but very familiar, a dear friend of mine. I don't know anything before or what ended
    the friendship. With both parents dead, I'm not going to find the answer here."

        Hands on her knees, looking at her boot as she swings them up and down, the ground climbs to her, turns to dirt and the sun throws an
    yellow-orange light on the surrounding. Besides her, a boy she once knew, laughing. The boy shoots her again with a pellet gun, she screams
    in a high tone voice, "Ouch!! I'm a girl." He jumps to the ground, turns to her and looks up to her, "Are you going to use that excuse for
    everything?" He gives her hand, she jumps and he pulls his hand away before she can grab it, falling face first on to the dirt. Laughing
    so hard that he falls to the ground, grabbing his stomach, Athena picks herself up and kicks him in the ribs. "Not so funny when you're..."
    she hears him shoot pellets; runs away from him with her arms over her head.

        "You have a gun, use it." he cries as he continues to shoot at her. She pulls the gun out the holster only to have it shot out of her
    hand, landing behind her. He's not going to make this easy, she thinks to herself. She runs faster as she takes a turn to the right, still
    keeping her gun in her sight. He stays on the same track as her, reloading his gun. Once she had finish the backtrack, her gun is up ahead
    of her. Right before he finishes reloading the damn thing, she slides to her gun, shoots his hand and sends his gun flying. She shoots again,
    hitting him in the cheeks, left and right; her last shot to his ear. Putting up his hand, he waves it left and right, "fine, you win."

        Content, she lets her gun fall down and that's when the shooting starts again, with the running. Now she's mad, "that little bastard."
    So mad that she decides to run head on against him. Runs to him with her head down, arms bent up to keep her head safe; she rams into him,
    both fall on the ground. He laughs again, harder this time. She punches him in the stomach but his laughter is now immune to pain. "Stop 
    laughing" as she tries punching him harder and harder.

        After five minutes, the daimon leaves him and he looks at her with a rekindled curiousity of her. He hugs her; she holds her arms up,
    not knowing if she should do the same or not. When he squeezes, her arms fall on him.

        She falls backwards and stares at the sun, saying aloud, "Roark, what's your diagnosis of me? Am I the only girl you know that would
    ever wear boots with a dress?" As he faces the ocean, "First of all, you're the only one that continues to call herself a girl, which honest
    compared how most women are acting now." He then leaves a silent pause in the air for her to give her time to wonder about her own question,
    if he is necessarily the best person to answer that for her. "Anything else?"

        Walking near her, he notices that she has her arms and legs crossed, shaking a little. Roark takes off her jacket and hands it to her;
    she looks at it in bewilderment. Without waiting any longer, he lifts her up by placing his hand softly on her back, puts the jacket around
    her and sets her down while he looking at her face for any slight discomfort. Keeping her arms inside, she closes the opening of the jacket.
    She shivers a little but it was worse before. "Thanks."

        "Have you spent some time sitting in the park or mall and just watching how others act?" As she presses her shoulders together, she
    thinks whether or not she has, trying to remember when she sat outside without anything pulling her away. "No, I don't I have." He rocks
    his head to a melody that Athena can't seem to hear. "But you do walk often to places, right? Especially when there's crowds on the sidewalk?"
    She nods. "Do this for me then, imagine yourself walking to get some coffee in the morning, already dressed and nothing at hand. No one can
    see you as you walk but at the same time, they never run into the space you take. So just walk and tell me what you see."

       "I see most of the with their cellphones, either texting or calling. The majority are going to work." "Can you tell me what they're doing,
    more emphasis on the women." "A woman in a stroller passes me as the girl who is walking in front of me is carrying four cups of coffee,
    her hair distraught, speed walking. Then there's a bunch of girls together, holding bags and talking to one another. Passing by a coffee
    shop, I see that all the staff are women, young and pettite." Laying right next to her, "So what would you say that a woman, or in your
    case, a girl, supposed to act." "Delicate." 

        She slams her hand to the ground, "That I'm supposed to be only for show, nothing more. That acting different to the standard
    disqualifies me from being a girl. That I'm not a boy nor a girl." His eyes turning to her as he keeps his face looking to the sky, "their
    standard."

        "I'm sorry, can we go home now, I'm not feeling so well." She sits upright while still shivering in his jacket. He puts his arms around
    her and ask if that's what she wants right now. "Yes, I need to be by myself right now." Lifting her up, he releases her.

        "Thanks for tonight, Roark. I'll see you next time." Roark asks her if there's something wrong, "No, nothing's wrong." She closes the 
    door and through the hole in the door, watches him leave. He pulls out his phone and finds that its 2am. 

\section{14, lights, camera, bang!}

        Sitting in the white room, facing the television; his gun pointed to the empty space on the screen. Pop, glass shatters to the floor yet
    no one from the outside comes in to see what happens. "They wouldn't come, it's natural for them to leave the building. Just in case 
    something dangerous happened." The clip pops out, another bullet unfired pops out too when he pulls the gun back. He places the gun on the
    table beside him, kicks up his feet and continues to stalk the past of the criminal.

        Already seen him three times in the 5 months of videos he's been watching and nothing conclusive can be drawn out. The criminal always
    places his face at an angle that might as well been blurred. Chris gradually tightens his grip on the base of the chair as he spends more
    of his hours to trace this random pattern of the raccoon. 

        The second time that he had seen him, it took longer for the unknown chemist to finish cooking. Still smooth with a hint of doubt. He
    almost drop one of the flask and putting the wrong amount, started over again, checking his numbers on the notebook. During the whole time,
    Chris kept thinking that the camera would slip his mind and the criminal would bring himself to focus. But no, he had a system in place that
    Chris noticed, always going out of the camera's view whenever he had to look in the camera's direction. Once he found out this little trick
    of his, Chris slammed his fist on the table.

        On the third visit, he doesn't start right away on his recipe. He arrives when a class is doing a lab so he stays on one of the desks
    and writes on his notebook, leaving the supplies out of the camera's view. Face hidden in the notebook, he hears a student asking for the
    teacher's help. This student is a long queue of worried students. He turns around, closes his notebook and heads to the student. They talk,
    the student turning back to his experiment, makes eye contact with him and shows him his notes. He nods during his plead, points to his
    work and underlines an equation. The student pleads for more help but he walks away, back to his seat to write in his notebook.

        At first, the student tries to wait for the professor to give him additional help but the queue is so long that the class would end 
    before it would get to her. Putting down her hand, she turns to her paper with the underline and tunes everything out. She doesn't move
    for a while until she bounces up slightly. She writes down a few things in her paper and continues with the experiment.

        Her hypothesis is wrong and she's left in dispair, thinking she is never going to get it right. No help from the teacher nor any more
    from the student that told her to reconsider something. She goes back to the underline, her hypothesis and tries to figure out what went
    wrong. A few strokes of the hand, a pause; she taps the pencil to her lips and in an instant, raises it high. She scribbles the epiphany on
    to the paper and tries again with experiment.

        She almost got it, less mistakes than before. She could have just left it at there but the sudden rush of having gone this far without
    her professor motivated her to go further. She considers the two trials, the underline and puts a few ideas on the paper. She starts slashing
    the paper without pity, a mess that she can make pretty later, until she ends up with one bubble. Without hesitation, she goes on her third
    trial. (consider giving hint of last after class has left)

        All the students walk out of the class, most of them grunting and sighing. He only sees one the jumps with a step. Once they all leave,
    he heads to traditional lab area and spreads the supplies. With his notebook, he checks if he has all the supplies at hand. Next, he
    places the relevant glass flask to each chemical, according to amount needed. After he finishes washing his hands, the alchemist gets
    to work.

        Just then, Chris knocks down the door and points a gun at him. "Let go of the chemicals." The criminal would roll his eyes at him, "I 
    don't think that's a good idea." But in Chris' head, the chemist would freeze, terrified of what will happen next. Then without warning,
    the chemist throws a flask filled with red solution to him. Avoiding it, it smashes on the floor and releases a fume that reaches the
    sprinklers on the ceiling. A siren screams for the occupants to leave the building, flashing a red light just in case they can't hear. 
    Re-adjusting himself after throwing himself to the right, he finds that his person of interest is gone underneath the sheet of chaos. He
    runs out the room, only to see classes of students in the hallway, making their way down stairs.

        Shoving himself into the crowd, he takes quick scan of all the people near him. Face after face but none that he can persecute 
    justifically. People are thrown out of his path as he continues his hunt for the slime of society. A white sleeve with a colored bracelet
    attracts his attention, he can't figure out why. Then it hits him, when he was holding the criminal at gun point, the flask, the hand
    he held it with, it had a black-blue with pink beads. He couldn't think of the moment what gang the criminal could be related to but he
    knew that the wearer was his guy. Reaching for the hand, two metal walls close between them. As the elevator goes down, he slams his fist
    to the metal.

        Hand on the white railing, running down the stairs, he keeps a mental note of where he is compared to the elevator. He runs at full
    speed until he reaches the first floor. He stands in front of the elevator, holding his gun out, waiting for him. More students go around
    the cop with the gun, wondering which danger they should heed to. Once they leave, Chris starts tapping his foot. He then taps his foot
    harder and loud. Having enough, he presses the button and watches the '2' light up. He quickly shuts his eyes, puts his head down. All
    the students are gone of the building.

        The chemist becomes invisible to him, forever. Having failed his assignment, he stands in the sheriff's office, being screamed about
    how inferior he is compared to the chemist. That hiring the chemist would be better than him. That's where Chris takes his stance, speaking
    for once during the whole meeting. "No, I know the law, how to reinforce it." "It doesn't matter if you're criminals run loose." Writing
    on a piece of paper, he gives the slip to Chris. Its a invoice of his new lower rank, traffic control. Chris tightly squeezes his fists
    as he holds the paper.

        Sitting in the car, legs kicked up, he points the speed gun to every car that passes him. "Nope. Nope. Nope. Nope. Nope ..." Feeling
    less incline towards his new position, he keeps the gun on with a rubber band and leaves it on the dashboard. Reclining his seat, he makes
    himself comfortable; closing his jacket. Slowly, he starts drifting from the world he hates into a place where he can make it how he wants
    it to be, better than this.

        With the light brown being the last thing he sees before his eye closed, the speed gun brings him back with its ringing. 45 on a 35 mph
    limit street. Shifting back to position, he turns on the siren and goes after the car.

        Walking to the driver's side of the car, he finds a white collar driver. Chris takes a look at his watch, "I suppose you're going to
    say that you're late to work, right?" The driver smiles with uneasy. "Not a reason to be speeding, driver's license and registration." He
    holds it for a second, just to check if nothing is expired and then hands it back. Then he leans to the side of the car while the driver
    keeps his eyes over the steering wheel, accepting his fate. When the connect eyes to eyes again, the driver brow concaves down, lets a sigh
    be heard and says that he'll watch his speed from now on. Walking away from the driver, Chris is trying hard to tolerate his sentence, if 
    only he did things differently during his encounter.

        Back in the lab, Chris holds his gun out in front of him while the chemist has his hands up. Shots are fired before the flask is thrown,
    before the alarm goes off and before the chemist thinks of his idea. Walking to the soon to be deceased, he goes through the criminal 
    pockets to find an identification card. He finds it, calls 911 to pick up a body and starts putting the whole scene within a yellow tape.
    Once he finishes the barrier, he looks back to the chemist and finds him similar to all the inanimate objects around him, not breathing.

        Standing over the body is not the near and dear, on the contrary, its the two people that wanted him dead and won't be persecuted for it;
    they will think of this as a necessary homocide. The sheriff pats Chris on the back as he shakes his hand, smiling. Chris responds by smiling
    too, from the room where his only company is the television.

        Another month, another sight of the criminal. He skips the fourth one since there is nothing he can use. Its only when he gets to the
    last one that he becomes obsessed with. There's more pauses to his steps than the last four times he's seen him, turning around often. The
    chemist is seen a few times leave the camera's area and come back with a new chemical. After he places the chemicals on the counter in front
    of him, he starts checking them off in his notebook. Check, check, check ..., he leaves the camera again. Back, he brings some carbon
    monoxide.

        His face stretches side to side when he sees the criminal do next. Putting his chest to the counter and chemicals near his face, he puts
    two chemicals into the flask in front of him without measuring, without referencing his notes. Chris jumps back a little when he sees the
    mixture start to foam while the chemist stares with a little boy's wonder. When the motion continues, a white precipitate settles on the 
    bottom. Grabbing the flask with the solution, he swirls it around and around, watching if he can start the process again. All it does is
    spread the precipitate more evenly in the solution.

        Then Chris starts to wonder how the chemist will act towards the argot. He makes him wait a little, trying the other chemicals and their
    products. One solution foams so much that he has to place it on the sink to prevent a mess. When he gets to the argot, he reads all the
    labels on it with leisure. Done, he holds the jar with one hand and heads to the red room. Fast forwarding that part since his face won't
    be red lighting, he sees the chemist exit the room with a solution on the other hand. He adds each chemical to the solution after review his
    notes.

        Done, he stands in front of the chemicals, back towards Chris. He points a gun to the television again, maybe shooting the image will
    ease his mind. Just then, the chemist turns around, smiles and waves to the camera. Chris has a mini seizure that causes him to drop his
    gun and fall of his chair. On the floor, he can't get this eerie feeling out of him.

        Getting back up, he rewinds the film to where the face is and freezes it. He takes a picture using his phone and can't help that this
    slip of the chemist will be his demise. Deciding that he has enough to continue, he turns off the television and exits the room. 
    Straightening his clothes, moving his shoulders round and round, he tries to shake off the eerie feeling with no avail. Lifting his head up,
    he carries himself, irregardless of the state, to the car. 

        Walking down the corridor, a student passes him by. Chris goes out the double doors and the student into the lab. The car turns on and
    leaves the university as a red light turns on, a flask tilted to let a liquid pour out.

\section{14, Sure}

        He fastens his scarf tighter, closes his jacket as he wears the yellow jacket. The ship sails across icy waters, white almost everywhere.
    Standing on the front of the ship, he leans closer to the edge while holding on to the railing, surveying the horizon. The sun far from it,
    hanging above him, making his back warm. Exhaling, he rests his head on his hands. Yellow, the boy wore yellow, Roark goes through all the
    papers to find the highlighted kid in his younger years. Starting from elementary, he works backwards and relives the days artificially.

        Sitting in class while the kids continued to work, a paper in front of him, already filled out and a check mark from the teacher. He
    wanted someone to be finished so wouldn't be alone but it seemed permanent. Most gave up on the task and settled for something easier, to 
    talk about cartoons and such to to others. Their motions go in reverse, the sun sets, the classroom becomes empty, the moon rises; falls, 
    class begins and the video rewinds faster as he ignores all the other colors. 

        A cold breeze interrupts his internal search; eyes back to the horizon. Looking at the sail on the water, he notices the ship is going
    faster. Returning back to the horizon, he checks from left to right for anything that might indicate where to head next. While turning,
    he feels himself get warm at a certain point but quickly dismisses; thinking its just the heat of the sun finally penetrating his clothes.
    He turns his head again, feels warm and finds nothing that attracts his eye.

        Folding his arms, putting his hand under his arms, he tries to ward off the cold. Turning his body left and right in place, he settles on
    an angle. A small white fog comes out of his mouth as he tries to think where the kid might be. "He's not dead. I know he's not. He's
    here, somewhere." The closer the ship gets to the horizon, the more its surrounded by ice and snow. Even with the wind on his side, the ship
    starts declining in speed. "Just a little more, you can do it, keep going, almost there."

        He can hear the ship breaking through the thick floor of ice and as he watches the blocks be thrown to each side of the ship, it becomes 
    hard for him to see hear bear so much. An anchor is thrown overboard, sinks rapidly through the chilly waters and buries itself in the 
    floor. The ship finally reaches to the stop after the wind has left, leaving Roark on his own from this point on.

        By the railing, he throws his legs over and holds the anchor's chain with two hands as he places his feet on the hull. Carefully walking
    backwards, he looks to the right of him, back to the horizon, sensing something wrong with the line. His feet go from metal to snow and he
    lets go of the chain, shivering in the cold.

        Walking, he takes a look back to the ship that took him this far. Closing his eyes, all he can see is the kid in the yellow shirt
    being washed away from the wave that climbed on board, slamming the door and flooding the room. Opening them, he finds himself still walking
    to the horizon, losing the reason why somewhere on his path. Wandering in the snow, he does the same in his mind. "Why did it have to be
    yellow? Yellow isn't my favorite color, never was. And what makes me so sure that the boy is somehow related to me, he could easily been a
    girl instead." 

        He leaves imprints of his boots behind him, his mind blank as the snow surrounding him. The ship is no longer visible and the horizon
    is barely noticeable. All he does now is focus on his breath. Breath in, out, in, out, in, out ... out. His body feels warmer, he smiles
    in simple bliss. Lifting his leg through the thick snow, he returns to his last mental checkpoint. The body becomes smaller than his head
    and the setting changes from the classroom to the park. The rate the kids skip backwards goes slow to the point where they almost stop. 
    With only a second pause, they move forward.

        Kids running all around the playground in the park. Blue, yellow, red on the slide playground, black turf, green in the trees and
    kids in joy. On run pass the swings, going through it with four kids following them. Another group is on the spinning a two kids on the
    spinners. Wind blows leaves across the play, adding more color to the painting in front of his eyes.

        Another boy runs across him, wearing a yellow shirt; shining like gold. After getting over the unexpected visitor, the balls of the
    feet beat the ground repeatedly as he leans toward the direction of the yellow shirt. The two run on the grass, yellow shirt taking a turn
    around the tree and Roark tries to cut him off. No luck, he just keeps running in front the tree. Dodging tree after tree, the cries of
    joy from the other kids disappear.

        Running over a bridge with a grass trail underneath it, through more trees. As he's following him, the distance becomes greater; each 
    turn leaving the leader more time to disappear. Being more than 10 seconds behind him, he persist even when his legs want to crash down.
    "Stop, stop," his legs say. Yellow is the only thing on his mind, the only thing he wants to keep his eyes on. 

        Its when he goes into the bushes is that the boy disappears but Roark doesn't know this yet. Moving the vegetation out his way, checking
    for any footprints or broken twigs, "He's here." Running to each path he puts his hope on, ending up trying others and others. One path leads
    out back to where he came from, another to more bushes, again, bushes; that's when he decides to get out. He walks around the bushes and 
    finds that running around it would take less than half a minute.

       Tired, he goes to rest by the pond. Grabbing his knees as he sits up, he tries to comprehend the situation. He now found the memory of
    the yellow shirt before it was consumed by whatever is lurking in his head but the memory escapes him. The memory of here is more a child,
    he thinks, while the other one feels like he lost the kid in him. "I must have been part of the event that changed him, it happened here.
    The question is how long and in what form it happens," he whispers to himself.

        His eyes wander from the horizon to the pond, watching the swans sail, fish swim and the water breathe. Colors then start taking form
    around him and his eyes follow; watching the water settle on a picture. The first thing he notices is the yellow shirt; he turns around
    to find an empty space behind him. He looks again to the reflection, waiting to see the boy's face. He backs up a little when the reflection
    becomes lucid.

        Looking down, he sees that the shirt he's wearing is yellow; the same yellow shirt that the boy had, in both cases. What he couldn't
    understand is why was it on him. Yes, of course, he is related to him but why is the shirt on him. "I better be real," he keeps thinking
    to himself, punching himself on the shoulder. "Can't start question the foundation now, have to believe in my existence at least. What
    I have to do is figure this out first, then I'll go down the stairs further. This is the only pillar shaking." 

        Up, he accepts the fact he's the boy is gone for now and with the yellow shirt, should see what its capable of. He jumps up with his
    arms stretch up, hands closed in a fist. He jumps again and again; "Can't fly." Next he tries running in the park, breaking the sound
    barrier might be possible. Nope, all he does is background noise. As he wanders all around the park, trying all the ideas in his about what
    the yellow shirt would allow him to do, he finds himself back in the playground with the kids.

       Curious, he asks other kids if he could play, thinking it has to relate to them somehow. The kids face turns sour and the others around
    him back up. "What are YOU doing here?" Roark tilts his head to the side, "Who do you think I am." The stern child lowers his brow, "Don't
    think that we don't know who you are, Roark. You're crazy, we might catch that crazy. Go be crazy somewhere else." Right away he wanted
    to punch the kid for the slander on his name but as he swings his hand back, he sees that he's surround by kids, all of them staring as if
    were a kid with claws.

        "Get out of here," stern kid screams, "or will hurt you." He could see that only a few of them were willing to abide by his words while
    the others were just going to get hurt. If he walks away, he'll be in accordance to their belief. That's when the swing is taken and he falls
    on the floor, as the puncher looks down at him. Grabbing his collar and bringing him near to his face, "Someone crazy would make your future
    end here, I won't. But if you keep calling me that, what the crazy person would do will come true."

        Walking away from the playground, all Roark wants to do is find somewhere breathe in tranquility, prevent tears of the easily hurt child
    from flowing out. He wanders passed the trees, passed the bushes and finds himself underneath the bridge. This is where he finds an inviting
    sombre shadow with arms open. He lets himself go in her arms, the grass spread all over his back. He, spread out like a star, feels his
    stomach go up and down, many times. The only tumor that is in his head is the kids ignorant scrutiny. It was them that was hostile and it
    would have been best to taken them all down. They wouldn't mess around with someone who's crazy.

        "No." he says softly to himself while laying down, eyes closed. Its best to show them that your capable of such a thing and not do it.
    For those that think, they will see something inside you, something they will at least consider good. For those that want to call you crazy,
    they won't try hurting you outloud. "I forgot about how lonely I was when I was little, I had no friends." He also remembers that he read
    a lot of books when he was at this age. When gaining this data, the more mystery grew upon the kid who he saw wearing the yellow shirt before
    him. 

        After he gets through the mind conflict, he checks his shirt again and finds the yellow shirt gone. "What the hell," he says aloud to
    himself. He searches around him for it and he finds all colors except yellow. As he looks under the bridge, kids start running in every
    direction. One stops on the side of the bridge, spying Roark and says if he wants to play. The same kid that he had punched earlier was
    now asking him to play. Roark shrugs the inconsistency of his memory away and sees where this play takes him next.

        He runs besides two kids as they are chased by the kid who's it. The group separates, one going with Roark and the other away from both
    of them. It follows the single runner; Roark and the kid run until they reach a tree, hiding behind it. Roark still up while the other is
    bent over, trying to work up to normal breath rate. Grabbing his shoulder and bring him closer, Roark helps him stand up. "Thanks," the kid
    says, his face becoming more smooth.

        Running again, he and the other kid stick together; the kid making him run faster as Roark is about to get tagged, saying not to give up.
    Roark helping the kid get away by distracting the it kid with a stick thrown at the bushes. Those are the only two that are left in the game
    yet the game comes to a close. Kids appear from behind the trees, bushes and other kids; "you won, Roark, now you're it." Looking at his 
    friend beside him, "he won too."

        "Who?" the leader looks around him and everyone stays silent, wondering where this friend of his is. "He's right here, don't you see 
    him." He points to his friend with his hands but he receives only looks of worry on their faces. Roark turns to his friend and sees that
    he's wearing the yellow shirt. Remembering what happened when he had the yellow shirt, "I have to go, my mom's calling me." He runs with
    speed to make his legs bleed, far enough to where the falls out of existence for them.

        Under the bridge, he finds his yellow friend sitting on the opposite side of him. At that precise moment, Roark feels himself become
    an observer rather than his body's driver. The boy Roark is supposed to be is crying, pointing repeatedly at him. His mouth opens a lot
    but the words fail to make a sound. Roark tries as much as he can to get close until a large crack is heard. Looking up, he sees the bridge
    collapse and his world turn black.

        Opening his eyes, he finds himself laying with his stomach on the pillow soft snow. The warmth has always been with him ever since he
    switched consciiousness, daydreamed. Standing up and straightening himself up, he sees that the horizon is but seconds away. Wanting to get
    this over with, he runs. Eyes still on the horizon until he passes it falls and watches it go above his head, further and further away
    from him.

\section{15, Mutiny}

        "So any ideas on what we can do?" she asks her team as she is presenting them a board open for ideas. Two guys and a girl shy away from
    the request. Then the black rim glasses stands up and talks; "Well, can we first look at how were doing. Can't improve if we leave the ship
    sinking."

        He and her start writing on the board, words relating to money pop up on his side while hers is relevant to using less. Done, both look
    to the rest and ask for their opinion, "Which issue should we address first?" they say in unison. Again, the faces on the couch remain silent,
    baffled of what they being asked. All they know is their trade, anything outside like meetings is another foreign language to them. "They
    both look good," says the girl as she is cautious about word she says next.

        Athena then takes a look at his side and sees the word that makes her feel like tearing the board down and smashing it. "How can you
    think about selling this company to somewhere else." With his arms crossed, he puts his head over his shoulder, directed to her and says,
    "I'm offering what would be best for the team as a whole. I know it would be better to get cash now than hope for an uncertain future." 
    Turning back to the audience, "Don't you think so? Better to have a bird in the hand than two in the bushes?"

        "Stupid analogy," Athena kept thinking to herself. Her business is nothing like that but fear could always be conformed to the same 
    type. Turning him back to her, "Are we selling birds? No. We are selling a service. You all seen what it started from to what it is now,
    its going to get better as long as we keep going at it. Why stop? 50,000 won't last more than a year if we split it between all of us."
    After that, they look at each other and quickly discuss the cash they would get, they would have to go back to year if at least six months
    and there was always the possibility that her business can become huge were cellphone companies would promote it by saying its integrated
    in their phones.

        "If it can make it passed this month. Did she tell you, our cloud provider is going to shut us down for insufficent funds. We'll 
    probably be offline by the end of this week and I doubt we'll make any money like that." Furious, all she could do was look at him and
    turn every so often to the window, back and forth, repeatedly. The board she was restraining herself on was starting to tear off the wall
    that it was bolted to. She lets go and holds her wrist with the other hand, taking deep, slow breathes and she got ready to counter his
    argument.

        "I'm going to kill you," she thinks to herself, holding a knife to him in her head. "Running a business isn't easy, if it was, 
    everyone would be doing it. There's going to be some bumps that are going to test your tolerance, can you stand seeing your profits take
    a dip, are you willing to do something about it? I've already look at the number of hits we get a month, not much on a single minute so 
    for now we can afford to be off the cloud and host the site on our computers at home." Their heads move behind their bodies, "When sales
    pass a certain point, we can return to the reliable scalability of the cloud." 

       Watching their relief made the black rim glasses feel like he was being laughed at. "If sales pass a certain point, you say. Explain to
    me and them," waving his arm to them, "how you tend to do that when the amount of users subscribed are dropping." Holding his hand to his
    during a gasp, "Wait, she did tell you guys, right?" All those skeptical eyes look to her for an answer. Pulling her hands away from her
    face, slowly, from her hair to her chin, "I'm not going to give up on this." When she said this, she felt someone invisible standing beside
    her, "the fate of my company solely depends on me. I know that I need your help so I take the risk of hiring you guys instead of people
    online that are offering to do it for half than what I pay. I also thought that when I hired you guys, that I was going to get friends that
    would stand by me."

        The audience felt disconnected from both person, hesitating their alliance. From the window, the sun wanes, shadows cast on all their
    faces, hiding the stress on their face. The silence the roams in the room puts everyone except Athena on edge, she being mad at her team's
    betrayal in her dream.

        "Its not that we don't like you, Athena. Don't get us wrong, its been great working with you. The pay is great and we're given freedom
    to use our time properly instead of being shoved to the wall under the clock." He turns, "the problem is that we know your past, the last
    two businesses you tried to get started and fell through for one reason or another. History is bound to repeat itself and its best to
    use it to our advantage."

        "You're first startup, I forget the name but involved tattoo pictures. It became viral on a small scale, more than 10,000 people became
    involved with it but it was impossible to make a profit from it. They weren't the type of people that was willing to pay five dollars for
    more features, they only saw it as a forum than anything else. Not worth paying according to them."

        "It was my first time, I learned from -- please, let me talk. You'll have your chance after I'm done." They look at her as if she 
    violated some norm. She recedes back to the wall and tries to soothe her anger towards the black-rim glasses, his face seeming like it
    needs reality to hit it.

        "So after 2 months, you shoot another risk, Commune; a site for locale community events. I think you got the idea since it worked in
    your home town but once you brought it here, it fell apart. We were more organized that you think, Athena." He taps his temple with his 
    index finger. "Your prone to keep doing these failure because you're different. If you came from this city, I would have more trust in
    you; but you don't. You come from a farm -- A RANCH (Athena)-- whatever," he looks away from her, "which a place where the internet is
    taboo over there and they still send letters written by hand. They have no idea how to use their time properly, losing it as they stand
    outside all day."

        The wall behind her had an indent that no one else except Athena was aware of since she had made it while she kept her hand behind her 
    back. Stepping up to the podium, she turns to him, "Are you done?" He presents her the stage and moves closer to the window. "Mistakes are
    necessary, many will happen and we will learn from them. Yes, I am different," she stands erect now, "we didn't always someone there to
    help us when something broke, a person to take all our worries away. We had to fix things ourselves and often created things that would
    improve production or prevent accidents. It was by these traditions that I sold my first product, to my neighbor; I was 9."

        They started to lean closer to her, wanting to hear more of this early prodigy. "He's right that my scope forgot the whole; I know this
    and now that I learned, I can adjust my ideas to include the whole as well. Consider the bet you guys took with the skills you have now,
    like you, Rachael, web design was innate to you but you dedicated time and effort into. Not for the money, it was because you were interested
    in the skill. For the persistence that you kept, you're here, doing what you like instead of working in a warehouse, doing simple things
    that the company doesn't want splurge money to have a robot do."

        Everyone on the table was leaning more towards to her now instead of the window. He returns to his stage with his hands up, trying to
    contain their enthusiam for her speech. "Don't let her dazzle you with her words, this business is still a high risk to keep going with."
    She turned to him and stared him down, "I tried being tolerant to your opposition but it seems that you desperate want to get out. Sorry
    to tell you, but I'm captain of this ship and if you don't like where I'm steering her, there's the door."

        Another staring contest between the two sparks, the others stay quiet. He lowers his glasses and looks at her over them. He blinks and
    then rolls his eyes; "you know that you need us to keep this alive. If the majority decides to sell the company, then the company is going
    to be sold. Before we came, the site was horrible, design dispicable, site kept crashing on browsers; a total mess. After we got through
    with it, the site appeals to the human psyche of colors and feelings, a minimal sharp design."

        Returning to face his adversary, she still holds her finger to the door as she stares at him. She smiles, "Are you talking about the
    majority? Yes? Let see, based on stocks, Athena is the holds at least 51% of the stock. Is she present in the room?" She puts her hand
    over her forehead and scans the room. "Oh wait, isn't that me? It is. I guess I'm the majority and you said that we should listen to the
    majority and -- but, but-- let me finish. It so rude when a man interrupts a lady, so childish," she waves her her to the other side. 
    "I've decided that I want to keep going. If someone is willing to buy our business, it shows that we have potential. I certaintly don't want
    to bail for only a louse ten thousand dollars when I see this making at least seven figures."

        Turning again to him, "the fight stops here, make your decision, stay with here and make your stock be worth more than a year worth
    of work or ..." He closes eyes, holds his hands in a pray and pauses for a second. With discontent, he walks out the door, leaving all them
    behind to what he thinks will be their destruction.

        An hour after the door has closed, everyone was on the table showing their mock ups and offering their input about the data logged by
    the site.

\section{16, Hope for}

        Working on the counter, sipping some coffee as the sun decides to call it a day; a week passes since the meeting and she has to do
    more of the work than before. She steps back from her work and gives it a look, "Something doesn't look right, I can't figure out what."
    Numbers on the spreadsheet stay within the same scope yet she doesn't know if she should interpret this as good or not. It could be that
    the computer made a mistake or that there is an error in what it was told to do. She takes another sip of her coffee as she lets her hair
    loose, letting her hands go through the honey silk that comes out of her head and barely touches her shoulders. Turning side to side
    warms up her body, always nice to stand up after being obsessed in something while stationary.

        Her mind juxtaposes the city to her home from afar. Its like being in a computer, the city. Everything always on, doing something,
    even when idle. The city that never sleeps is a fact here. Streets never lacking cars within a five minute span, someone is out there
    walking on the sidewalk, lights on all the time. Remembering the wooden floor in her dad's house, only one light was turned at a time at
    night, the kitchen. She would sit there, reading a book as he did the same, sitting opposite of her. He would then get up and start
    doing something near the stove that slipped her perception. Ten minutes later, a warm meal is on her plate and her dad tells her to eat.
    
        Looking at the chinese takeout box, she can't remember when was the last time she had a home made meal. Opening the fridge, she finds
    mostly condiments, a few eggs, greens and ham. Closing the door, she tries to forget her hunger by revisiting the numbers and the threat
    they pose.

        Leaning on the wall, resting her head on it as she holds the paper for inspection, the other hand with coffee, she hears the door call
    to her in slow hollow knock. She looks to the door and hears it knock again. Putting the paper back on the table, she walks to the door,
    opens it and finds James there. He stands in front of her door, rubbing his shoulder, looking down the corridors, not realizing that Athena
    is now where the door was. When she taps his shoulder, he jumps back with his eyelids disappearing. Once he sees that its Athena, he lowers
    his shoulders and a benign smile surfaces. She then grabs him by the shoulder and walks him in.

        He sits at the table while she gets another cup of coffee by the cupboards. "Thanks for letting me in Athena, I thought you were going
    to be busy." She though to herself, "I better not tell him that I have something due tomorrow, something is troubling his mind, like he
    has a locust on his mind. Have to figure out a way to light a fire in there." Holding two cups of hot black coffee, she hands one to him
    and apologizes, "I have no milk." She looks up to her and says, "its fine, you're black coffee is better than most coffeeshop sweeten coffee."
    She rolls his eyes at him, "stop trying to impress me."

        As he sips his coffee with two hands, he makes eye to eye contact with her. "So how is everything going with her business?" She takes
    a sip of her coffee and looks out the window. Her face changes to wonder to skeptical in a second, as if she saw a brown fabric floating
    at the window. When she checked again, it hid itself. It wasn't important now, it must have been the long hours that she had been putting
    into her work. "Its been peachy," she tells him. "Work is never easy but I like it."

        James looks at the scatter of papers on the table and when he tries to see her reaction, she's has her head tilted to the wall behind
    her. "Is there anything I can help you with?" He pulls a paper from the mess and she takes it out of his hand. "I have to go through the
    papers first, James. Thanks but not right now." She then gives him her motherly look, "Tell me, what's wrong?"

        "Nothing's wrong. I just wanted to see you, chill out with you for a while. I know that you rarely take a break when you have a startup
    and that Roark would drag you out of the apartment for you to get fresh air but at the moment, he seems to obsessed as much as you are over
    something too so I decided that the responsibility fall on me now." She shoves her lips to the side, skeptical of this new James, "tell me
    James, I can help." "Its the truth, I'm just not used to being the person who gets the ball rolling in the group."

        She keeps her eyes on him, already seeing what's wrong but needs him to say it. "Okay, there's two things. First is what I said and the
    other is Mary, she wants me to propose to her this week or she'll leave me forever." Without hesitation, she jumps out of her seat, lifts
    James to the air and hugs him tightly. Turning her shoulders side to side until she decides to open her eyes, she finds an insecure child
    in her arms. She sets him gently back to his seat and returns to hers, moving her hand through her hair. "My bad, its a reflex of mine when
    I hear someone is getting married."

        This is something that he believed in, when someone at a coffeeshop was proposed there, she ran up to the bride and hugged her. It
    had taken away happiness away from the bride and replaced it with scared ignorance. Sadly to say, they broke up when they were outside of
    the coffeeshop.

        His head was down and she could see this, "Don't you like Mary, she is nice and attractive." He nods his head. "Then what could be the
    problem?" "Me, I can seem to let my toy go." She lifts her brow since she knew that he wasn't they type of person that has toys in his house.
    "She wants me to stop playing with math and go to work in the office with her dad." "Just take it, you can always use the rest of the time
    for math. The job will only take all the hassles of life out of your mind, math being the sole inhabitant of your mind." "That's the thing,
    my spare time will belong to Mary. We would have to do everything together."

        "You just have butterflies, that's all. You're nervous about getting married because its such a big decision in a persons life and don't
    get any practice before hand. You have to believe that she is the one you're looking for." James is now looking out the window, "And another
    dilemma, I can't believe that she is who I am searching for. Being with her is like a kid being inside a princess story, where I'm the
    pauper and now my whole life will change. Everything that I was will be disregarded."

        While he was giving his side of the story, it seem that he was doing working on some math problems behind the pages of Athena's reports,
    his hand acting involuntary. She puts her hand on it, "Talk to her, she has to consider that she changes you completely, you won't be the
    person that she loves." His face falls closer to the table. "I have; she doesn't budge. She gave me an ultimatum, her or math."

       This couldn't be the Mary that she had met before on a few occasions with him and Roark. She knew that she didn't like Roark, the reason
    being anonymous but besides that, she seemed nice. How could this girl that she met say something like that to James? It was impossible but
    then again, he wouldn't be here if the matter wasn't real or serious.

        James watches a coin thrown to the center to the table, flipping a few seconds before settling down. He then looks at her with a question
    mark hanging over his head. "Heads or tails?" "Tails." She flips the coin while he hopes that he gets tails. "Its tails, you win. Another?"
    "Sure, why not?" "Okay, now we're going to raise the stakes a little. Heads, you marry her. Tails, you leave her." His lower lip falls down
    like a brick to the floor. "Just a little? This quarter is going to decide my future? Athena, are you okay?" She keeps those piercing eyes
    on him, "Are you in or not?" "Fine, flip the coin."

        He doesn't know how she did it but it seemed to him that the coin flipping in the air hanged in the same spot for a least 10 seconds. 
    His heart was slamming his chest hard, his eyes fixed on the thing that will determine his fate, his destiny. He would have to go with 
    whatever it said since he wasn't sure which to pick. As the coin made its descend back to the table, she slaps it before it touches the 
    ground and it flies out the window. He sees the decision escape him and bewilderment fill his mind as he turns to Athena. "Why would you
    do something like that?"

        "Now tell me James, what were you hoping for?" This question was bizzare for him, it didn't matter what he was hoping for, only what
    the conclusion is. "Love is not logical, James. Take a look at you and her, to others. We don't get match perfectly by looks and the such,
    we find beauty inside the person and that's what keeps us with them."

        James puts his head down, becoming mute. To give him time for the choice to simmer, she goes to the kitchen and pours herself another
    cup of coffee. Leaning on the counter's edge, "love, it can bring the best or worse feeling in everyone. Something that no one can master
    and that is completely selfish." As she sips her cup, she sees him face her, "Its always been a selfish act of a person to love, despite
    what others tell you. You love a person based on how much you love yourself. If you don't care, you'll let yourself attach to anything. If
    love yourself the right amount, you'll try to find someone who will be your best friend, a complimentary form to yourself."

        James felt that he should be writing this down but then it would interfere from him absorbing the emotion behind the speech, forgetting
    that love isn't completely logical. It doesn't rest on the mind but on the heart. So he continues to listen to the Muse about love as
    Socrates would have enjoyed to hear. "Love is selfish in two-fold, your desire for the other. Your unwilligness to share her, to keep her
    to yourself. That is the first form of selfishness that it appears as. The second, you must convince the one you love to love you as much
    as you do yourself. If by tricks, you must keep up the act until you die. If by honesty, you must prove to her, provide her comfort, trust."


        With his eyes, James signals to Athena as if he held up his hand. She pauses and waits for him to speak. "Does someone always have to
    get hurt with love?" "Yes." This brought his head back down. "Tears always accompany love, either in joy or sadness. It is not destined for
    a person to love another, its a choice, always a choice. Those that think that it meant to be that both of them are suppposed to be together
    believe in their love too much. Excess can be fatal. Do not strangle the butterfly called love but hold her gently. She won't come to you
    if you chase her with worry. She is known to rest on your chest when you're happy with yourself, relaxed."

        He knew the choice he had to made but he kept trying to think of all the alternatives that he could do so both would be happy and not
    get hurt. "Isn't there any other way?" "You could prevent yourself from getting in love, a much simpler life but then again, who wants that?"
    She sits back on the table and lowers her face down to his, offering a warm smile. She blinks, "let me see if I can put this mathematically,
    when you do something to one side, the complete opposite happens on the other side of the equation. An extreme rugged allegory to love is
    an equation. There must be similarity between the two sides for the relationship to work. Things can be done for the equation to look better,
    something added or removed. A problem arises when the inequality increases, a person becomes detached of the other, demanding too many 
    changes, etc. and so forth."

        On a piece of paper, he wrote James on the left, Mary on the right and an equal sign between the two. He put one check on his side, 
    pauses and thinks if she had changed anything for him. One check mark for the raincheck proposal. More check marks started appearing on his
    side but her side remained the side. When he took an look at the equation again, the equal sign started to look like a 'less than' sign.

        "She's not going to be happy about this." James says, fumbling his fingers. "You have to some times let go of everything to get everything
    you want." Her eyes make their way to the bills on the table, "of everything." 

        As they stand by the table, he hugs Athena but she feels one of his arms fall limb. She hugs him tight to where breathing becomes 
    difficult yet he bears the pain. "Thanks for the help, I guess I'm my own from here, huh?" She puts him in front her, her arms extended, 
    nodding to him. He hugs her again, says his good-bye and walks out the door. 

        The only light on in her home is the kitchen, lighting all bills on the table. She leans near the where the light ceases to go any
    further, casting a shadow on part of her face. Coffee no longer offers her comfort so stands by herself, wondering where to put her trust
    in. Not her team, not after the fiasco with the glasses, all her trust in them has been stirred. Her company, the foundation is shaking and
    all the weight is resting on her. She can't look to her company as inspiration as its declining. "There has to be something to believe in,"
    she says softly to herself, looking to the sky through her window.

        Ring, ring; she pulls out her cellphone and sees the text sent. A smile flashes on her face, a fire rekindled again. 

\section{17. Lookout}

        The elevator rises up stops on the floor, opens and Chris is standing there, hands in the pocket. The corridor clear, he walks as his
    eyes wonder from one wall to another. Green walls as he walks to number 107. He puts his ear close to the door and hears writing inside.
    He then starts pacing back and forth to wonder how to get a better view of what is happening inside without alerting the owner. Back and
    forth, eyes wandering again until they find a fire extinguisher hanging on the wall. An exclamation mark pops over his head.

        Standing over the edge of the building, he starts having second thoughts about this. Behind him, a hologram of the sheriff is pushing
    him on. He lets one foot hang over the edge, closes his eyes and lets himself go. Shoes land on a metal floor that cascades all the way
    to the street. As he descends down to the window, he tries to estimate the time it will take before he meets this criminal face to face. If
    his source is right, he should be coming to see her soon.

        When he gets to the window, he sees someone else had just entered the home, sitting at the table opposite of her. Once he scanned the
    room, he quickly recedes away from the window, sitting on the stairs besides it. He pulls out a notepad and pen, waiting to hear anything
    useful. Laying on the stairs, he lets them talk as he relaxes a little.

        His eyes directed to the other building, a couple is kissing behind the curtains. He closes his eyes and reminisces about the affair he
    is having. How it started: he was shopping for groceries and had bumped into her by accident. The look she gave him hypnotized but he snapped
    out of it when he dropped his phone. While picking it up, he sees that from behind the other aisles, the front and back, there were eyes of
    men following her. "Sorry for running into you," she says as she turns her head away yet keeping her seductive eyes under those low hanging
    eyelids. Her smile brings him back to bliss.

        "The fault is mine, Miss ..." "Lady is more appropriate, mister." "Pardon me again, Lady. Like I said, the fault was mine, I wasn't 
    looking where I was going. Are you hurt or anything?" His eyes gently tread from her neck, shoulders, waist, legs and ankles. "I'm fine.
    Thanks for asking." She lets her hand graze his shoulder. "If you want, you can make it up to me by taking me out to dinner." "Such a large
    fine for something small, don't you think?" "Don't you think I'm worth it?" She smiles at him with her hands making a 'v' underneath her
    chin.

       It must have been her beauty, he thinks to himself, that made him oblige to the request. At her drive way, she stands by the door, waiting
    outside, looking him at the window. Then he hits him; he gets out of the car and opens the door, waving his hand like a chaffeur. When they 
    leave, she turns off the music that he was listening to and puts it to a classical music station. He hated the music, music of the dead
    and the old, the opposite of what was sitting in the passenger seat. She asked him where they were going to eat, "Hamburgers." Shaking her
    handing at him, "No, were going to eat a stake dinner instead." Right there and then, his destination had changed and he felt a bigger charge
    fall on his wallet.

        At the table with the white robe that barely touches the floor, sterling silver on top of it, spoons and forks varying in sizes, glass
    for drinking wine and all the waiters dressed in suits. Sitting down, he sees that she's staring down at him with her arms crossed, annoyed
    that he forgets his manners. He pushes her chair out with a kick of the foot, a gust of air flows out her nose as she rolls her eyes. He
    orders the steak, she orders the salad. 

        Waiting for their meal, she talks more about herself, require little confirmation from him. She says that she is from a royal blood,
    a high aristocracy class that is no longer recognized in the states and that its a shame, she would be able to bring so much class to
    those celebraties that most look up too. That she wouldn't be caught dead on one of those television shows that record her every step, she
    has much better things to do than that. Cameras belong in one place only, at parties. Anywhere else and they create scandals. He nods as the
    stake finally arrives.

        Finished with their meal, she asks if he has any drinks at his home. "Of course," he replies. As he pays the check and gets up, "Thank
    you for remembering your manners now." She gets up from her seat and heads to the car without him.

        She is laying on the couch, drink the scotch that he meant for a special occasion but unfortunately her eye caught glimse of it. It 
    was the only drink that she said was equivalent to her status, the others being bought a supermarkets. She swirls the cup with a dark gold
    liquid with ice cubes, puts it her lips and tosses it to the back of her mouth. She turns to him and smiles; "Can I use your bathroom?" He
    nudges his head to the bathroom, which is in his bedroom. It is while before he hears the toilet flush and hears her call to him, "I need 
    some help with something. Can you please come?"

        He finishes his drink with one gulp and heads to her direction. Turning on the light from his bedroom, he sees her sliding her back by
    the bathroom door. Surprise at first when he sees her appear like that dissapates when he realizes what is happening. She signals him with
    her finger for him to approach her. He walks close to her until she puts a hand on his chest, putting some pressure. He puts her head closer
    to hers, his lips almost touching her before she pushes him back a little. She then starts steering the dance, closer and closer to the bed
    without tripping over it. She then pulls him back to him as she makes her way to the wall, flips off the switch and tosses him to the bed.

        When the lights turn back on again, she is sitting up right against the headboard, smoking a cigarette while he is unable to comprehend
    how he got her in bed with him. "It must have been luck," he says to himself. Then she stands up, puts her clothes back on and says something
    before leaving him, "I'll call you when I want to have a good time." She doesn't turn around but holds his business card that she found 
    besides the bed. "Good night."

        At that moment, something hits him on the head, a metal coin. "What the hell are they doing in there?" he wonders. Letting the pass
    slip his mind, he catches her name, Mary. The Mary that had told him to go here, the person who knew something about the criminal. Maybe
    she had the sinister person under the same spell. As he continues to listen, he never hears the name of the criminal surface.

        Seven months after their affair, he gets a call from her saying that she wants to talk. At first, he was shocked, was she going to
    have a baby? "No, I've been with her this during these seven months, I would have noticed something." Eliminating the worst worry, it
    seemed strange that she would call him for anything else than to go under the sheets. He obliges as always to her request and carefully
    chooses the proper attire to meet her for brunch around 10 am.

        Outside of the patio, someone bumps into him that takes a look back to the tables. When he looks at the strangers direction, he finds
    Mary sitting by herself. Curious who the person was looking at her, he turns to him and finds a empty space. The stranger disappears in the
    morning crowd. Giving up on his wonder, he heads to the table she is sitting at. She stares at him over her brow and tells him to wait a
    minute, she has to finish sending a message to one of her friends. He crosses his legs as he turns the chair to the side, away from her
    and flips through his notes for his investigation. All he knows about the criminal is his face and his potential. Finding a record in the
    school would be impossible, assuming that most likely he isn't registered, probably using a fake id to get in and erasing the entry so
    the chemicals couldn't lead back to him.

        Closing her phone and putting it back in the purse, she puts her purse on her lap and faces him. She exhales, closes her eyes and tells
    him: "its over." He drops his notepad and looks to her, "What?!" "I have to give this up, can't have this type of clandestine activity 
    happening while I'm a wife."  Staring to her finger, "but you have no ring on." "I'm going to be a wife soon and I have to settle down. It
    was fun all the time we had together but its going to end today. Besides, it seems that lately that you been preoccupied with something else,
    unable to focus." "I thought I told you," he picks up his notebook, "I been searching for a criminal that has been using chemicals at a
    university to make drugs." She gasps.

        "The only reason why I haven't caught him is because he doesn't leave anything leading back to him. All I have is a picture of his face
    but no idea where to search." She puts her hand to him, palm up and he hands her the picture. She brings it close to her face, squints her
    eyes and a malicious smile creaks on her face. "You know who he is Mary?" "His name is Roark and I think he's doing the drugs on behalf
    on some disertation he's going to present." Chris slams his fist on the table, the plates shakes, Mary jumps up. "Now I got that sinister
    bastard, tell me where is right now so I can arrest him." Her face becomes drained of happiness, "Unfortunately, I don't have that type of
    information. Basically all I told you was it. He's friends with my soon to be husband and friend of his, a girl. I assume they have something
    going on but they never show it, at least in front of me anyways."

        Chris puts his head back on the table, hitting the table again softer than before. "This bastard just enjoys laughing at me." She then
    grabs his chin, lifts him up and tells him that she knows a way to get him but he has to go the opposite direction in order to catch him.
    He thought she was just teasing him but then she gave him an address of a girl on a slip of paper. "Its for Athena home, I suggest you linger
    there for a while, either he will show up for her or that she go to him. Keep a close watch on her, she has the talent of disappearing when
    you aren't paying attention."

        As he prepares to leave to the address, he asks, "Why are you helping me find your soon to be husband's friend? Shouldn't you be denying
    that you even know him." Holding her breath away from the vile that is also known as Roark, "he seems like a threat to my future. It those
    type of statements that he makes that leaves me disturbed. Can't have any of that absurdity seep into the James, I have to protect my 
    investment. Consider you putting him behind jails as a thank you directed to me for giving you the privilege to be with me." She brings him
    closer, tilts her face, grabs his head and puts those soft lucious lips on his, a sweet wine splashing on his lips. Once they part, he opens
    her eyes and finds that she is gone and that she left him with the bill again.

        Returning back to the eveasdropping where no key words were heard, he decides to call this stakeout a failure. Before climbing back up,
    he hears a door shut. Peeking over the side of the window, he finds that Athena is still in the room, drinking coffee and looking at her
    papers on the table. He takes a look at his watch, passed 2 am, "She's going to sleep anyways."

\section{18, Dust equivalent}

        Rorschach blots are pilled on the kitchen table that he is sitting at, fountain pen bleeding on to the pages as he tries to recreate the
    image the lurks in the shadows of his minds. His hairs pulled apart from his head, standing in the air; hours have gone by that he spent
    doing the sketches, no sleep nor food. Each drawing is a failure and step closer to the monster. What he can't comprehend is that each
    picture posesses a certain quality of the creature while the rest becomes distorted, the memory becoming unreliable.

        The moon lets him work without the tired orange light being on. He then becomes aware of the cellphone in his pocket and decides to
    send a text to her. He sends her a text saying, "I'm always there behind you." After that, he turns off his cellphone and lets his
    obsession with the shade take over. Shadows linger by the doors, over the ceilings and on the floors. Fear finds no home in him, only
    curiosity; a child that wants to know already what has been following him around for this long. Finds it impossible that he hasn't got a
    good look at it yet.

        With his mind out of images to copy on to the paper, he stacks the paper neatly into a pile and decides to go over each one in a test,
    seeing what his reaction is. Before doing the experiment, he closes his eyes and covers his ears. For 5 minutes he keeps this pose; after
    the time there, his mind decides to impose a reality on the surroundings. When he opens his eyes, he lifts the stack up and is shown a 
    creature with a large claw scrapping the floor, in front of its body. The only part of the face that he can make out is its eyes, angry
    and hungry eyes. Besides Roark, the yellow shirt yawns.

        Two more pictures go by, the kid going to sleep. When Roark pulls the third one, the child's jaw drops a little. The image is of the 
    monster underneath a bridge, waiting for something to pass by. Another one is pulled and this time the monster is appearing from a shadow
    of a child. The yellow shirt looks away.

        He grabs him, trying to comfort him but at the same time, the papers slip out of his hands and land on the floor. An image of the monster
    having the boy inside is what terrifies him the most, running to Roark's arm for comfort. He's found the picture.

        In the living room, he places all the viles in front of him necessary for the expedition: dmt, acid, thc and poyote. He goes to his
    music player and puts a binuaral beat that fills the room, causes the floor to shake. As the rhythm flows in and out of his ears, he 
    lifts each vile up and tosses the substance inside. Leaving four containers empty, he holds the image besides him, trying to keep his eyes
    on it as he leaves this world. The child next to him tells him, "I hope your ready," before Roark falls into the black vortex.

        A light segment flashes from one side to the other, touching everything once. It then shrinks near his bookcase and then disappears. 
    Breathing in, he sees that this his living room, only red. Up, he takes a look around to see where the inconsistency lies. Going to the
    kitchen, he passes the table and finds the roschachs papers lying on the floor. Then recalling what the boy said to him before his departure,
    he assumes that he's not going to be in here. By himself, truely? He had the image of the monster as he traveled here. 

        He walks back to the couch and finds the paper he was holding onto is on the coffee table, the image of the monster having been burned
    out. The pieces of papers then fly into the air, scattering to the living room, the kitchen and some falling on top of the table. Then he
    started getting a bad feeling about the papers. One burns up along with the three besides it, a gust of winds flows in the room. Another
    from the table burst into fire, lighting a flash that fills the room for a second. The remaining burn up right after the other, in sequence.
    All the papers are gone and the shadow holds more than what he expected before.

        They would get him either way if he stayed so he starts moving towards his bedroom to see if he can find anything useful to fight against
    the demons in the dark. Passing the corridor, he finds a kid wearing a yellow shirt standing at the end, waving to him. By instinct, Roark
    looks behind and a shadow rushes to him. Roark grabs the monster as he falls with him and once he touches the floor, kicks him off while
    keeping the momentum going. Settling on the floor, he hears a grunt come from the doll and the dark cloud. Up, he finds that his shoulder
    has be scratched, bleeding only a little. 

        Staying en route, he figures that whatever attacked him was the lowest of them all, rash despite the trap those two set up. If that
    was the minimum, Roark had to hurry up and find whatever is going to stop them from attacking. If the monster that made the yellow shirt run
    to him comes out, would that mean that his body will lose it consciousness forever?

        At the kitchen, he runs to the drawers and pulls out a knife knowning that this won't save him. "At least I'll be able to take out the
    first two" he says to himself. Holding the knife in front of his chest, he makes his way to his bedroom; the closed door being the only
    obstacle.

        Turning the knob has no effect on the door, he still remaining outside, vulnerable. When he checks over his shoulder, a shadow flies by
    the living room, over the couch and the bookcase. Cocking his knife, he eases his sight while putting more of his attention onto his hearing.
    A creaking comes from the door that leads outside of the home, the closet in the corridor. As he peeks into the corridor, he sees the
    closet open. Either way, he thinks, he's going to have to take down all of then eventually, might as well take out this rash monster while
    he is still alone.

        Taking a deep breath that inflates his chest, Roark walks to the closet while listening for anything that can be on the floor, ceiling or
    wall. Each step increase the testosterone in his blood, his heart works harder to keep up, being him up to his top potential for just in
    case he does not pass today. With his hand on the door knob, he turns it and opens the door. The same closet he knows, a few clothing, his
    bag and other stuff that he throws in here. Still facing the corridor as he steps inside, he closes the door on himself.

        In the trap, he waits for the monster to make its move while he holds his knife by his pocket, wrist angled as ready to strike. His
    clothes jump into the air, waving around the room. Then the room starts to shake. The first time moves him from his spot. The second one
    throws him to the wall. Its only the third one that holds him pressed against the wall, as if the closet is now a barrel rolling down
    some incline. He can feel that he that he is above the opposite wall as the clothing falls to it, he still being held up by momentum. It is
    a that moment that he sees the monster on the floor, looking up at him.

        A pounce to him misses as Roark grabs the clothes railing and pulls himself away. As the monster tries to readjust itself, Roark lunges 
    himself to monster, making the knife disappear into the shadow. A cry, a shove of the shoulder and he is thrown against another wall as
    the closet rolls, the monster crying in agony. The monster lifts its head, opens his mouth and lets the deep moan escape the shards of metal
    in his mouth. Watching that fatal teeth glisten convinces that he should finish the monster off before he experiences the harm a bite could
    do to him.

        The monster is tackled with Roark wrapping his arms around him, his shoulders driving to the floor. He stabs repeatedly, finding new
    flesh to let the blood flow out. He stabs the side a lot, switches to hammer strike to its chest, shoulders and legs. After the assault, he
    slips on the floor while the body falls on him. The force in the monster has left, the luggage being the only thing remaining. Tossing it
    to the side, he picks himself up and shakes his head.

        Exiting the closet, he makes a note that he's has taken one down, assuming that there is three monsters still roaming around him. The
    worst part that he's scared of the fact that their strength is greater than what he took down. He has to find the tool now. Running back to
    the bedroom door, he starts ramming his shoulder to the door as he turns the knob. The first hit refuses to budge, a few more times and 
    feels the barrier getting weaker until the side of the door breaks and he finds himself inside the room.

        Everything the same as his room outside of this world, even the color. There has to be something in here, he thinks to himself. He closes
    the door so at least he can use it as an indicator to hear whatever tries to enter the room, no longer being useful to keeping things out.
    As he tightens his fist, he realizes that he had left the knife in the closet, buried in the monsters exterior. All he can think is "damn,
    I hope Hera is on my side for now."

        Walking around his bed, first checking the walls for anything useful hanging on them, he checks behind the two protraits and finds
    only the same wall behind them, rugged and flat. His next target is the bureau with 6 drawers. Starting from the top left, he opens it and
    finds the same clothes that should be in there. Shirts, shorts, underwear and socks. Reaching for the second, he hears something break on
    the kitchen floor. His pressure jumps up but he brings his hands down, eyes closed and exhaling. Opening his eyes, he continues to the second
    drawer.

        Several glass cups fall on the floor, as if it has them all held up against its chest and dropping each one at a time to build its
    stage to attack him. His back curves forward, the body becoming tense. On the fifth drawer, he lets his hands replace his eyes and goes
    through all the content until he feels a flat square. Pulling it out, he finds a picture of him, when he was younger, a child. He had his
    arm held up as if put it on the shoulder of a friend but the space next to him was empty. He was the only person in the picture, smiling.
    Holding it closer to his eyes, he sees a translucent contour of another child, the size and features being very familiar to him. 

        His focus then shifts back to the kitchen, where the monster breaks a plate. "He's going to be in here soon, that's a fact." Trying
    to ignore the shattering on the floor, he reinspects the picture, to see if he can find something useful for his current predictament. He
    puts his hand on it, hoping that it would be able to enter the picture, only to have it make a dent on in it.

        Hoping to see something that he isn't seeing at the moment, he flips up the switch of the room. The light turns on but the picture 
    stays the same, the picture holding on to an invisible friend. Before he sees a change happen to it, he hears the fridge fall over. 
    He approaches the door slowly, his foot landing softly. Turning the door little by little into the room, he leans over the edge to get a
    view of the kitchen. No one there except for all the broken glass, dishes and refrigator. 

        Getting closer to the ground where the monster grazed, he tries to look for anything that might indicate something about the monster:
    size, strength and the such. On the counter, he sees a dirt mark left on the counter, three fingers and a claw on each. Since the light
    in the bedroom work, he turns on the kitchen light to get a better view. Just then, the monster rushes to the living room, keeping his eyes
    on Roark, ready to strike. Roark sees those yellow-green lights looking at him, an oval sharp ends tilted up from the outer side.

        Putting his back to the wall and scanning the area for the possibilities where the monster could strike from, he drops the picture
    near the destruction. His eyes remained fixed on it, wondering when its going to strike next.  When a while passes, he loses patience for
    the monster, taking away the tense in his muscles. As the eyes follow him as he walks in the kitchen, he wonders why it is not attacking.
    The last monster did not hesitate attacking him in the open, so what was stopping this monster from getting him now.

        Accepting the fact that the monster won't attack him as long as he is in the kitchen, as long as it remains the same condition as it
    is now, he is free to rummage. Going back to the broken dishes, he picks up the picture and looks again at the picture. Holding it against
    the light, he sees something start to glow. A shirt, it glows yellow.

        The kid he chased in the park, on the ship; "he was my imaginary friend." Then a flash hit him where he was wearing the yellow shirt,
    the kids hostile towards him. He sits on the floor, I was isolated because of my imaginary friends, they thought I was weird, crazy. No
    one wanted to be my friend because of that. The image next went to when he was playing with the kids. "Yet somehow I was able to get back
    with them."

        Roark was under the bridge, looking at the yellow shirt; angry. He remembers the screaming he did towards him, the excessive pointing
    to the friend, saying that he was the cause for all his misery. His perception returning back to this reality, he sees the yellow eyes
    looking back at him. Then the frequency in his head spikes, realizing where the yellow shirt is, what he is and what he became. What he 
    doesn't know is what he just killed in the closet.

        Walking around, he hears the music his body is listening to from the other dimension, it has hit the last 10 minutes mark. He can
    feel his body near the edge of the couch, arm hanging down, touching the floor. He had be conscious of how acted in the dream, knowing 
    that these things were now roaming freely in his head could be devasting if allowed to inhabit his subconscious. Once there, Roark
    wouldn't be able to pull them out. Standing on the balls of his feet, favoring moving back to the kitchen, he started to have a hypothesis
    about what would lure the monster back to him.

        Eyes kept on the monster and its eyes on him, he pulls the drawer open; metal clinks. Putting his hands closer to the light switch, the
    monsters eyes get bigger and more lucid. The floor is clawed, wood being scared very slowly. He can feel his chest rise and fall with
    more weight to it; part of himself is telling him that he should stop now, that he was barely strong enough to take on the first monster.
    This one has seen his ability, capacity and knows how to respond. Images of he being on the floor, bleeding as the monster was waiting for
    the others to arrive, a moonlight on his face, eyes closed. Roark turns off the lights.

        Legs of the monster crush some of the wood as it propels itself to Roark. Over the counter, it gets stuck in the passage that it knew
    it would be able to pass easily. Turning back on the light, he sees the monster struggling with the chair pressed against its chest, keeping
    him stuck between the ceiling and the two columns. It screams a piercing siren that brings Roark to his knees, it struggling to get out of
    a trap which basically is being stuck in a hole that is smaller than its head. Grabbing the frying pan, Roark rises and smacks the monster
    across the face, knocking it out.

        Laying by the bottom shelf, he sees the reason why the light is a good repelant to the monsters; it seems to be evaporating. Trying
    to reach homostatis with his breath, he keeps his eyes on the monster, grip still tight on the frying pan. "Just a few more seconds," he
    says to himself, "almost there."

        When the head starts disintegrating, that when the life returns to it. Claws thrown ahead of its body and Roark trying to ward off the
    fatal slashes with the frying pan. It hits his left shoulder, drops the pan and lunges himself the fridge; turning it the side to absorb
    the blows. He hears the metals being ripped like a chainsaw tearing up a piece of paper. Being so close to the claws with the refrigerator
    in between convinced him the end was invetiable. With the last slash cutting the fridge in half, the claws fell to the floor. 

        It strikes one more time at Roark, or what it thought he was, sticking the frying pan before is wandering eyes. It slices the pan into
    bacon pieces, moans until the noise is cut off. Pan slides away from it, whatever it became now, as Roark is breathing hard, keeping himself
    upright as he is on the ground, struggling to put his head up. The core of him is stirred, pictures of everyone against him, all those kids;
    he, by himself, standing against them all. He and his shadow, he did the best that he could do. The expectation was passed, to fall now
    would just bring him peaceful serenity. "I need a break," he says as his head falls on to his knees.

       A sun appears over the crowd, bestowing him with ichor that he (deserves/qualifies|merit); a fire flows into all the muscles, removing lethargy's
    hold on him. Then feels a hand on his shoulder, a shoulder press to him, helping him rise. Standing up, he sees that his comrade is the
    kid in the yellow shirt. Waving to him with a smile, he gives him a friendly punch and tells him to get his head back into the game.

        From the daze, he finds himself on the floor, lost in knowing how he ended like that on the kitchen floor. Planting his foot the floor,
    he picks his head up, faces forward, grabs the frying pan and sees a gust of shade reach for him. The hand reaching for him is smacked as
    it pushes Roark to the wall above the counter. Pressure getting worse, he pushes himself to the side.  On the floor again, he hears the
    shadow make indent on the wall. Back on his feet again, he runs to the bedroom and puts his back on the door.

        Sparks fly in his head, fire that follows a trail and ends to the air. Nothing is connecting, he's trying to find something that will
    connect to a fuse; all he starts to see is fire, red. The door shakes and Roark anchors his feet in front of him, letting himself run
    his curiousity without bounds. The door creaks open, the shade starts to slip through but Roark straigthens his legs. His eyes go in circles
    in the room, always in motion as it scans. Ceiling, wall, bed, painting; ceiling, floor, carpet, closet; ceiling, shoulder, hands, light
    switch.

        His body pushes the door with a sudden shock, eyes now locked on the closet. Putting his hand to the door, he pushes off the ground and
    to the closet as the door slams against the wall, the light in the room absorbed by the shade. The closet door is slid open, he feels a tug
    on his hand and throws himself to the closet.

        A sharp pain on his head after he hits the door. Remembering the situation, he gets out of the closet in the corridor and runs to the 
    bedroom and closes the door. He can feel the push of the shadow but the door still remains closed. Standing back from the door, his head
    goes from a boil to a simmer, muscles more loose. The question now is how to get the yellow shirt back, he can't leave him behind.

        Back in the kitchen, he drinks some tea, a strong vibration happening every 10 seconds, all the glass in the kitchen moving and the 
    refridgerator. Scratching his head, he reviews the image of when the wave came inside the room. So much lucid now, the censored scene during
    the event, being in the room as it was filled with water. Floating above the ground, a shadow enters from the open door, swims to him,
    wraps its head around him, scans his head from top to bottom and then releases him. It does the same with the yellow shirt except before it
    leaves, it envelopes the child's body.

        "So he has to be in here," Roark says with his eyes closed, taking another sip of his tea. A symbiotic relationship didn't happen in
    the boat, it must be holding him prisoner. Maybe its intention was to set the perfect trap for me. Directing his eyes to the door, "I hope
    this isn't the best it can do." Open his eyes again, he sees that the world had changed into white, the contours being the only sign that
    it was still his home. As he leaned on the counter's line, curious, he put his hand through where the ceramic would be at; his hand passes
    through. Turning back to the door, he sees the shade in the corridor, pointed at him.

        Skipping the idea that the situation is innocuous, he knew he couldn't let the shade press him against a line. Before he could jump
    out of the way, the shadow bolted at him; hitting his legs. Spinning in the air seems to take an eternity while he sees the shade moving
    faster, unheeded by the rules that govern his leviation. It cocks itself to him again and shoots. Bringing his knees to his chest, the 
    monster misses while Roark uses it to propel himself to the ceiling contour. The shadow makes a deep indent in the ceiling, a hole large
    enough to put Roark in.

        Pushing himself back down on the floor, he runs behind the bar. Roark can hear the room breathe, the chaos takes a break. Closing his
    eyes becomes one of his problems, wondering if the next time he opens them again, will the situation get worse. Just then, the shade crashes
    right in front of him, a few feet away from his tucked in knees. Grabbing on to the shadow, he throws himself over it and heads back into
    the bedroom, back on the door. Back here again, the same cycle, fuck. I need to stop this before the next one.
