\title{Running}
\author{Huxley Sparks}
\begin{Document}
    Outline:  Running down an incline besides someone, choose which is the cause, away or to. 
                Mark: Audacity
                Frank: Fear
        Steps land hard on the concrete, heels touching the surface first before the toes and body slanted forward. Step after step, the same cycle
    is repeated with a pain transferred to the body. Breathe becomes valuable and rest not an option for the moment for these two. Where they run
    in comparison to each other doesn't matter, only that they are running in the same direction. Mark, the younger of the two, is behind the faster
    person, Frank. As for the reason which is similar since there is something behind them quickly trying to approach them and they would prefer 
    not to be acquainted.

        With Frank in the lead, Mark takes a look back to see the black fog getting nearer. The most that his legs retailerate with is to stall in
    the same distance from Frank as if tied by a rope and Frank was strong enough to keep him going. Frank didn't want to look back, to be reminded
    of what he was running for;  scared of what he fears might be inevitable if he tries to calculate the time it will take for the fog to capture them
    versus the time to arrive at the safe house. Swinging his arms with force that he could throw death behind him, Mark was amazed that he was able
    to keep up with Frank.

       What they both had to realize that one of them will have to be captured for escape to be possible. Judging by the speed behind them, the fog
    would be right next to them before arriving at the plaza. "We have to lose it there to get to safety without betraying the safe hold." Frank
    says aloud to Mark.

        As Mark runs, his legs start to feel void of energy, chest heavy and his heart beating close to the range of Frank. In the storm of craziness,
    he closes his eyes and imagines himself at the safe house, laying down with his back on the wall, dozing off while a girl talks to him. He can
    smell her perfume, thinking how the hell she manage to find that but only showing a smile as acknowledgment of the smell. She grabs his hand, encloses
    it in hers and puts in on top of her crossed legs. She rests her head on his shoulders and he feels the warmth radiating from the sunshine sitting
    so close to him. As she turns to him, she slaps him. Opening his eyes, he finds himself running through a pile of leaves in a park.

        Frank is now 5 meters ahead of him and the fog much closer than before. Running, he feels the sun bring him a blanket of heat on his skin as the
    orange light shines through the few remaining orange and yellow leaves on the branches of trees extending to the sky. Taking a deep breathe, he
    exhales with a burst of speed that closes the gap between him and Frank. Only 2 meters left in the space and again he is as at full ability. At this
    point though, Frank has already forgotten about Mark, his ears being filled by the stomping hiding in the fog behind them. No hesistation he thinks to
    himself, if Mark is capture, can't waste time to confirm it. No time to pity him now. The plaza is so close now.

       What sends a chill up their backs is that falls of trees for having seen them with such fortitude as they passed them only to hear them a minute later
    hit the ground with a shock and a brush of leaves. Frank was now hitting the ground with the balls of his feet while Mark was becoming more aware of his
    posture.

        Just to wake up with her besides him is all that he wanted, to see her open her eyes to greet the sun and the day, finding him and thinking the world
    does know she exists. She would wrap him in her arms and bring him up to him, squeezing him with bliss on her mind. His arms sprouting out of the hug to
    show how much he loves being with her, giving her a kiss on the cheek. They rest their head over the other's shoulder, her cheek glued to his as they
    smile.

        Back on the concrete, Mark can almost grab one of Frank's feet that quickly revolve under his body. Turning to see how close the fog is to them, he
    realizes that they have to finish now. The pressing deadline throws away anything in their head that is unnecessary weight; the day, time, who is chasing
    them and fatigue. Based on the speed, Frank has already thrown almost everything away while Mark was holding on to something. The fear Mark had for being
    captured couldn't throw away the thought that had cohesive between it and his head. Even with what power the fog has demonstrated, it wouldn't budge. Then
    another idea surface that he gave one glance before throwing away, how did Frank manage to throw everything away so easily?

        At the plaza, they ran under the concrete slab extending over the streets, from the buildings, that was supported by columns. After each pillar they pass,
    they hear it be torn down, either thrown to the street, to the building or some times even reaching them. This is where they have to lose the fog, a split in
    parallel running of the two. Whoever it choses to follow will in turn save the other from certain destruction while the former can only hope for a quick death.
    Frank was already hoping that he wouldn't be the choice the fog would go after when the split occurred. Mark wasn't thinking of that, he was already thinking
    of the room where she was staying. "I have to keep going," he thinks to himself.

        Their destination is ahead of them if they continue to go in a straight line, through the clustered alley that the sidewalk leads into. Those golden
    strands of honey flowing down his shoulders as they stop swirling from the motion of him and her spinning. Both guys sense the breathing of the fog and
    both change accordingly. Frank flanks to the right to circumvent the building in hopes of losing the fog while Mark increase his speed. No longer is he
    bound to the stamina his body is used, with the bar empty, he keeps running. Faster as he hurdles over trash, long sticks of wood leaning on the wall;
    using his whole body to maintain his speed by pushing off the wall to move in a certain direction while his legs obsess with the only task of running
    with fire.

        Pushing off with his right, his feet run on the air incline that touches the wall opposite of his hand and then the perpendicular wall. Behind him,
    the fog collides with the wall, shoots ups about the height of the building and then as it falls back down, resumes it pursuit with the runner. In his mind,
    his desire for her burns higher than what the fog went, keeping him running while unable to say anything without it being distorted. His chest starts to 
    with the jackhammer where his heart is supposed to be. The view ahead of him starts to faded, losing scope of everything around except for the door about
    half a mile a way.

        On the track, he runs with her, for fun. She runs in the inner track while he runs in the penultimate, starting on the same intersecting line. "Go,"
    she shouts and both shoot off the starting line. The star he's running against gets the lead and he disregards the accommodation he should set on her
    for having the short distance. He just keeps running faster and faster until he catches up to the shooting star, turns to give her a smile and faces
    the track again as his face tolerates the pain of maintaining the speed. At the end, he wins by a few meters. Laying on the grass while she is bent down,
    hands on her knees, "you shouldn't be able to beat me, Mark." she says in between gasping of breath, eyes opened wide. "Yea, I hear that a lot."

        Almost there, he thinks to himself. To persist even the adrenaline and the high disipate becomes arduous for him. Adversity piles up as tired feet,
    exhausted lungs, arms empty like a scarecrow and the closed door at the end. He screams ahead with whatever breath he has left to open the door, staring
    into the eyes of the person behind the small window of the door with horizontal and vertical bars. "Open the door, damn it." He trips over a piece of wood
    and he falls near the fog's range. Only a few meters left as the ship is falling apart, he has to enter the harbor soon.

        A few seconds remain before he reaches the door and its still closed. All his resources have been allocated to finishing ahead of the door. His pace still
    the burst ever since he entered the alley as he stares at the door. Those two eyes on the other side look at the runner as their top line concaves down. The
    door indents momentarily to the inside, pushing the eyes away and then another push from the outside hits the door; the race is over. As Frank closes his
    eyes, he lets go of the door's handle that he was holding closed.
\end{Document}
