\title{Russian}
\author{Huxley Sparks}
\begin{document}
	
		Male, age 26, works as a consultant for the government. Always having an eye to see waste and capable of creative problem solving since the work is 
	mostly done by humans with machines only as accessories. Today he talks to me in the breakroom while the others eat in their offices. I was eating a sandwich
	as he steps inside with his meticulous suit, polished shoes, stubble beard, groomed eyebrows and his medium length hair thrown back. He asks if could sit
	at the table where I was at, I nod.

		He tells me his name is Marlow, I look at him to show that I heard. Continuing with my sandwich, I hear him talk to himself about how it would be
	better if he could leave his family. I interject that its yellow to leave a wife and his kids. He laughs, "Who would marry a guy like me? No, I mean't
	my parents and my sister." I miss some of his ramblings when I bite into my sandwich and taste a pickle. Its slimy taste covering my mouth in puss made me
	hold my tonuge out to quarantine it from spreading to the rest. Marlow blurred from my sight as I extract the contagen from my meal. Having pulled it out, I 
	toss it to the trash.

		Death is too easy, he says, pulling out a smoke and lighting it up. He offers me one as well and when I reach over for it, I see that its a cuban 
	cigar. I politely decline, "its too strong for me." Putting back the cigar back to his jacket's inner pocket, he asks if I have any family. One wife, one boy,
	that's all I need, I tell him. He congragulates me for my success and I can't help but smile since for a person above me, I beat him in tradition.

		I have to be honest with myself, the real reason we were alone is because people didn't like spending time in a building that was a work in progress.
	Construction workers in their section and the employees in theirs. I bring this up for the fact that the building is growing, it changes. Whatever might have
	been there an hour ago can be gone today. Well, apparently this dame thought nothing of it as she went down the corridor today. For me and Marlow, we hear
	her heels click on the floor as she walks to her office. Then the noise comes to a stop, a puase and after, a scream. Marlow launches off his chair looking for
	her as I try to catch up. With lunch being almost over, most of the people come back.

		After I take a turn, I see Marlow dive towards the edge as her hands slip off. I look away, not wanting to see the shatter of a nice man. Then I hear
	screams of joy and confusion from her. My eyes set themselves on the edge and find Marlow's feet on it. "Hey, would you mind pulling us up?" Me and a few
	employees hesistate for a second, thinking we might make things worse. Shortly, we find ourselves grabbing him from the legs and pull up. With both of them 
	safe, sitting on the floor, Marlow pulls out another cigar while she is left in freight.

		"Do not worry so much, you have survived, now it is time to celebrate." She looks at him with enlarged eyes, "What kind of sane man would say that?"
	Then she lets her head fall down as she cries. I suppose that is the first and the last time I will get to see him again. After that suicidal rescue, they
	no longer singed contracts with him but had him attend a psychiatrist so he wouldn't harm others.

		Six months later, I go from recording data to sorthing files; checking if they have all the correct paper work. No one worth remembering or talking,
about	except his. When I find it as the first folder waiting for me, I hide it away so I can look at it during lunch. Continuing with my work, the more I hope time
	moves faster. Around ten is where it begins to lag, where most of the files look identical except for gender and some seasoning. I keep my free hand in a fist
	to at remove some my adrenaline. Then at last, my lunch break arrives.

		In the breakroom, I open my briefcase on the table and pull out his file. I open the file and see a black and white picture of him, looking to his
	right, snickering. I turn the page and the first report is about his psychiatrist analysis of him. My eyes then notice every detail about the paper, the
	wrinkles, water stains, penmanship, diction; how each sentence is arranged. My eyes dilate, more emphasis goes to my hunger. So I reach inside and find nothing.
	I probably left my sandwich in my office, I can always eat later. I pick up the papers, bring my feet up the table and start to read the report.

		Upon his arrival, Marlow does not hesistate to be relaxed, lighting up a cigar and laying down on the recliner. I was a bit annoyed with the
	smoke but since my goal was to soothe him, I had to be tolerant. I asked him if he had any problems that were getting out of hand, he says no. "Are you sure?"
	The patient shakes his head without ever making eye contact with me. I write down his body's response. Then I ask the patient to tell me a story about himself,
	something that would let other people understand him better. He then looks at me and asks, "how so? To show that I'm one of them or anything about growing up?"
	I explain further, the one memory that leads directly to his character today. When he started talking about himself as an adult, I didn't think he knew what
	I meant.

		"Around my twenties, I had barely left my family to go live on my own. My home was a small apartment, by myself. This was different to what I was used
	to. The constant chatter in the house, complaints from my father, my mom always screaming at us to come and eat while my sister talked to her friends. I
	also had friends but we met sporadically, from seeing each other and spending the whole day together or going at least two weeks without talking to each other.
	It was week one and I was in my room, which also belonged to my sister, reading a book."

		"In my apartment, it was empty and silent, my cardboard box. The first week there I read twice as many books as I usually read in my parent's house. I
	also slept a lot since now I wasn't pulled away from my bed. The work I had to do kept a roof over my head wasn't hard, just watch packages in the warehouse.
	Everyone in there called it boring and I agreed but I wouldn't let something like that bring me down. I'll cut this part of the story doc, I eventually find
	ways to make the warehouse more effecient, they pay me a percentage and I quit to start consulting for businesses, which leads me to my past goverment 
	contract."

		As I write down the details and the tone, I hear him ask about me, if everything is fine. "I can't complain." He then asks, "so there is something
	you don't like about your life?" I reply by saying that I'm not making as much money like my collegues are. "Should it matter?" 
	"Yes, it matters," as I lean closer to him. "Why?" "If I'm not making more money than them, then I'm an inferior psychiatrist compared to them."
	At this point, 2 hours become a blur for me and when I regain consciousness, I have my head down on my clipboard.

		Knowing my state, I divert attention from me by asking him to go on about his solitary lifestyle as I recover from the sad truth I hid away.
	He puts his hands behind his head as he goes further into his life, eyes closed. "My family tried to stay in touch with me but for my first year on my own, I 
	wanted to try living without them in my life. I missed 4th of July, Labor day, Halloween, Thanksgiving, Christmas, New Years Eve and a few birthdays; I did
	send them gifts though. My neighbor tried to keep me company, always syaing that being alone leads to depression and that they were trying to help. All they
	were to me was nice."

		"Like I said before, I read much more than I used to in my parents house so I spent a whole month reading books, I think it was twenty. For a while, I
	actually forgot what year it was or where I was. The first Sunday of the following month, I sat on the porch in the morning and reflected about what I've done.
	I was extremely entertained that whole month but when I looked back to it, I've haven't made anything. I guess my need to create lead me to cooking the 
	following months."

		"I started with the basics: borche, vareniki, okroshka, shchi, pelmeni and then others, like bread, pies, steaks and cakes. The first two weeks I had
	food poisoning a few times from my meals and had lost weight because all I ate were the things I made. After that hell, my dishes were becoming edible. I
	spent many hours a day to make food to the point where I had mastered the fabrication. Placing myself to an ordinary chief, I went chasing down perfection."

		"Apparently hell came to visit me once again the following months but instead of frustrating my stomach, it pinched my brain. I kept recording all
	the measurements that went in my meals, crossing a lot of failures and I think I could never cook anything better than plain meals. Eventually, after so many disasters, my meals
	were a slice of heaven. To spread the bliss, I left some pies for my neighbors and left my familly a complete thanksgiving feast at their door. I remember
	my mom sending me a letter saying thanks and despite taking credit for it, she told me that I had made the best meal she could ever wish to do."

		"Reaching the zenith, I go and sit on the porch again to review my months. I have certaintly made something and by extraordinary skill.
	The borch, bread, cakes, turkey; all delicious. But then I started to think about what I had to show for it, nothing but requests. Of course I like what I made 
	in the end execept for its temporary existence. Then I thought about what is immortal that a human can do. Magic was out. Pondering about what to do, I see
	a fellow neighbor finish his jog and stop at his doorstep. There, he pulls out his watch and checks his time. The idea comes to me, to set a record in 
	running."

		"Committed, I go run at that moment around the pond near my home, with all my clothes on. Unfortunately, my first run didn't even make it to the pond
	yet I continue on the track, which is to the pond, around and back home."

		I then begin to see some of my coworkers return from lunch and unwilling to stop reading, I go to the only place everyone stays away from. I go over
	the yellow tape and sit on the edge so I can read. "Even if I get caught, this will be my first offense."

		The psychiatrist makes notes of the patients need to create a purpose for himself, unwilling to settle with life. That this obsession can lead to the
	danger of others, like he had put the dame from his last government contract. The patient asks for my analysis and I tell him he's fine. He chuckles and says
	he doesn't believe me. Curious, I ask him to tell me what I think of him. "I suppose I'm different to what you've seen and you don't know how to label me
	except as a threat. To try to convince you otherwise would just make things worse. I don't care, goodbye."

		The therapist's report ends and the following paper is a police warrant for Marlow. I bring it closer to my eyes to get a look at everything on it.
	"Officer Henry: The day after his meeting with the therapist, a warrant is placed on Marlow Kabov to be placed in an asylum. We go early in the morning to
	catch him before he wakes up but when we get there, we find the door open. From what we can see, everything has been left behind. We ask the neighbors if they
	have any idea where Marlow could have gone and they have no idea who he is. I ask again and replace his name with his apartment number but again, they don't
	nothing about the stranger. Fugitive is still at large and assumed dangerous, all I can say is for all officers to keep an eye out, he'll pop out eventually."

		Done with reading, I pulls out a cigarette and take a smoke. I let the warmth fill his lungs and lets the dark smoke leave my body. With the
	closed folder in my other hand, I put the tip of the cigarette on the folder and set it on fire. I watch it burn for a moment, smile and let it fall
	to the cement close to the base of the building. Getting up, I toss my smoke and go back to work.
	
