\title{Sad Princess}
\author{Huxley Sparks}
\begin{Document}
    Outline: A brother and sister in a mexican family, traditional is valued. Despite being the girl and trying to be good, brother
        is seen as better for only having a gf. Still their little girl that likes Simba but goes to her friend for trust and help.
        Characters:
                Brother: Vanity, Dj wanabie, only plays to friends | Tyler
                Sister : Tragedy, looking for home that only she can offer herself. Popular, social | Alma
                Mother : Old, sews, cooks, straight edge | Maria
                Father : Tired | couch, slow on house fixing | Juan
        Event:
                Saturday night, all heading out, car choosing
        End:
                Sister loses, ends up drinking as usual with friends, forgetting her family

        "But its my car." She says pointing to the door, her car being beyond the house. On his side, Tyler stood looking at her with a
    fabricated indignation towards her. "You're not even allowed to drive." "I don't care. Its my car, I paid for it and if I decide not
    to let you use it, you DON'T USE IT!" She never screams, people could always hear when her words were bolded. "If you don't let me
    use the car, I'm going to tell them that you been driving recently without a license."

        Tyler and Alma, brother and sister from a Mexican family. The only reason why they're so honest in front of their parents is because
    neither parent understands English or even if they did, not with that speed nor altitude. 

        Their dad had finished about half of an eighteen pack of beer to make the workdays seem like a dream and was ready to leave until he
    noticed that he couldn't go alone. His wife, Maria, was still in the bathroom fixing her hair and the more time he spent in the home, the
    more irritated he became. From the couch, as he was watching the television and holding a beer in his hand, he let a yell that would 
    scared the sirens away from the ship to their mom. The beer in his hand bent to the point where it will remained wrinkled as changed the
    channels quicker to find something for him to do.

        Running down the stairs, Alma comes down with her blonde hair done, necklaces pouring down her shoulders besides the sparkles on her black
    dress and her small purse. She runs up to her dad, lifts him up, goes on her toes and kisses him on the cheek. She tells him in spanish that
    she is going to her friends house and that her friends are going to pick her up. He asks if she has any money, "Its okay, dad. I don't need
    money where I am going." After giving him a hug, she runs to the door until her dad calls her. Turning around, she finds a twenty dollar bill
    floating in the air with the help of his hand. "Really, dad. I'm fine. If I'm trouble, I'll call you. Its just a small get together in the city,
    I'll be okay."

        While they talked, black rimmed glasses descended the stairs as he kept his eyes away from touching the dirty ground. Clean from taking
    two showers that day, all he was going to do now was grab the keys and leave. As he approached the table, he saw that the keys were missing.
    "Mom!" he screams. "Mom! Where are the keys." Alma and her dad turn around as they are hugging around to the baby of the family, him being
    seventeen while she was twenty-one. "What is it?" Alma asks. Pointing his eyes away from her and facing his dad, "Where are the keys to the
    300?" He tells him it should be on the table. "No, its not. Where is it?" Their dad yells again to his wife, asking if she got the keys. She
    responds that she didn't get them today and if they checked the table for them.

        "You have it, don't you." He finally looks at her but only after he pointed to her first. Lowering her eyes to ajar, she looks at him with
    right eye brow raised. "You know that you've decided to hold grudge against me and yet you still want to borrow my stuff?" She rolls her eyes
    away from him. Just as she was walking out the door, she hears him repeat everything she said with the sound of her words going through a 
    blender. She knew that that was the only thing he could say since there was nothing else he could say to counter her arguments.

        But he didn't have to win her with words, his home field would always guarantee him a win. Opening the gate, she hears her dad yell again,
    this time it was for her. Clenching the top of the gate with her hands, she felt like reproaching daddy's little girl who was everything he
    wanted him to be. Tyler had a girlfriend. That was all their dad wanted from him and having accomplished that, the judge is apt to lean excessively
    on Tyler's side.

        Shrugging her shoulders, she turns around, climbs the steps and walks back inside with Tyler standing besides their father. "Give me the keys,"
    Tyler asks with his hand extended, palm up. She locks eyes with him as she her fortitude strong. Tyler then breaks the contact, turns to his dad
    and asks for him to make her do it. His dad tells her to hand it over. Keeping her eyes on the little boy, "No. Dad, if he treated me a little
    nicer, I would. He always acts condescending to me even though he doesn't what that word means."

        "I know what it means," he retorts. "Are you sure? Give me the definition." "So what, you can learn the definition from me." "Fine, then if
    you already know the definition, you shouldn't have a problem using it in a sentence." "I don't have to prove to you anything. Give me the keys."

        She held her arms close to her chest, imagining that she was holding to her simba, a plush lion cub. This was the second one that she had since
    the first one was left behind a friends house that lived far away from her. Every time that she seen her friend at parties and the such, she would
    remind of her to bring her simba. Simba was buoyant in her thoughts despite all the things that went at home, how much alcohol she consumed or
    trance that she was under from the music. Standing close to the door, she felt like just running out the door with her simba and forgetting about
    the hour, the morning hold a better fate for her.

        However, her feet felt like they were soldered to the floor and her knees started to shake. Maybe her friends would come to the door and ask for
    her; this was what she hoped for. Her dad was a person who didn't like to be rude to guest but they were afraid of him from the stories she told them
    about him. She wouldn't be surprised if they stayed in the car, staying away from the curve, honking for her to come out. She hated the grin of her
    brother's face, hated the fact that she had to tolerate it or face the scrutiny of her father, saying that he isn't as bad as she was when she was
    that age.

        "I had a curfew, you guys told to always be back at a certain time and got on my ass when I passed the line. You would never let me hear the end
    of it and say that I would never go out again. Always making me clean and screaming for the house not being perfect. Oh, no, not with him. He can drive
    the car when he doesn't have a license, drive without glasses, talk back to you and always keep doing the same thing that pisses you off. When he
    tried to do the same thing with me, I don't respond with insults. I just took something from his room until he paid me back."

        Tyler remembered when she took away his external hard drive from him. He had yelled to his parents, saying that she was stupid for taking the
    hard drive away from him, that he did nothing wrong. When she tried to contest, they wouldn't hear it until she had returned the object. They said
    that they would handle him but after he got what he wanted, he ran up the stairs, calling her a 'pathetic loser.'

        It wouldn't have been a challenge to take him down, he's all talk, no sports. She had been in wrestling and actually, so did he but he couldn't
    last. For her, she was one of top wrestlers in the district. With the strength, she should have gone to his room and kicked his ass yet she didn't;
    "he's family, I can't hurt family."

        Simba would always be on her bed when she could stand her parents, her brother; smiling at her as a puppy sees sunlight. Jumping on the bed, she
    hugs the lion like they were meant to be one. After opening her eyes from the hug, she stares at the pictures of her quinceneira on the wall. Dressed
    in all white, hair up, some red blush on the cheeks and a smile of weightless serenity. Surrounded by all guys in black suits, a few smiling and her
    brother being amongst those that don't. But now the day has passed and rarely does she wear a white dress nor red makeup.

        The red shirt on her brother becomes vibrant as he smiles once again at the self conceived inevitable result that he is dreaming of. Knowing the
    result without knowing why, his parents always tend to favor him. The indignation the sister feels towards him with the absence of violence as he
    looks to the parents who hold the baby closed to them, rubbing his shoulders and eyes on him as they issue the verdict. This is where she lost the
    meaning of what family stood for.

        Keys hang from his extended hand; he runs back to his room while wearing a smile that can be sensed even with the back of his head staring to the
    other people living in his home. She doesn't look at her parents as she holds her fury on the doornob. If the door was any weaker, she knew that she
    would have torn it off and launched it in their direction. She knew they would jump out of the way but apparently they have no idea about how they
    made her feel. Before they would give her the talk about how he just being a kid, she had already jumped in the car and pulled out her flask as the
    car was moving.

       Orange orbs hang from the night sky, tainted white lights that look somewhat yellow on house and such, scattered around as if someone were throwing
    paint at a canvas, angry with the world. Letting the eccentric honey burn her throat offers her much sought for solitude that she could never achieve
    at home. With the radio blasting, people laughing and jestering, the car is the best place for her meditation. Having no care where the car is going,
    she bumps shoulders to her friend sitting in the back seat with her and asks what happened to her at the last party she saw her, having seen her
    friend legs being out of her control while a boy offered his shoulder as an anchor to keep her elevation.

        Music whispers into her eyes from the outside before she even turns to find the house radiating from their apparent destination. Taking another
    swig, she opens the door, slips out, closes it walks on the grass towards the door. By the back door, she spots people playing beer pong and gives
    a shout saying that she next. 
\end{Document}
