\title{Wash up Ashore}
\author{Huxley Sparks}
\begin{Outline}
    Lighthouse, siren | Oliver Smith: Pacific | Actions that lead to reflections | Year starts at sunrise
            On beach, cold, lighthouse as company. Removing excess to achieve want. Buying cups of coffee,
        eating out, clothes, walk more, cancel cellphone. To go to ibiza with your image
\end{Outline}
\begin{Document}
        Fireworks shooting up to the sky as a sign from others that midnight has struck. Their attempt at making another sunrise fails at his recognition for
    the new day that will be coming. His only beacon of light at night that outshines the rest is the lighthouse that stands on top of a cliff where waves
    tackle into about every few seconds, as they always have been since he got there. Putting his hood over his head, hands into his pockets and squeezing his
    body together using his elbows. Clenching them into a fist is difficult for trying to make them bend is bending a small rod of metal. He knows that sitting
    near the shore is making matters worst for him, the cold being excruciating right after being thrown off by the waves.

        Covered in mostly in light on this night by the neglected moon hanging so close to the world and the few seconds of intense light from the revolving
    light. Still able to see himself in a blue-gray hue, he considers if this is what he really wants. He doesn't have to be in the cold; he could be inside
    a room with friends, alcohol, music, dancing, lcd screens and sparkles. To deviate of course from his friends house happened in a click, having a flashback
    of how the previous new year parties were like for him. To go again would just be practice that everyone decides to use to talk rather than anything else.
    The new year would be the only change in the room, the people only acting different momentarily until the alcohol wears off.

        He already has an idea of what he wants, to go to Ibiza, stay at a white marble apartment, rise in the morning with the sun shining down on him as he
    goes to get breakfast with others that are there, sipping coffee, reading newspapers while the streets are sparse of people. Hear a car pass by the 
    restaurant more than after the point that they forget cars exist. Non-elevator music, a station that the owner is fond of while he rests his head by the radio,
    taking people's orders with a piece of paper and pen, a placid yell that he exhorts to the cooks in the back. With only 5 guests in the restaurant, 12 round
    tables empty, the owner's tranquility persist.

        Tea, beans and eggs drenched lightly in red tomato sauce that glistens on the plate, besides his notebook and fountain pen. Writing some of his thoughts
    from the morning, he closes the notebook and starts eating. None of the meal comes with nutritional labels or endorsements, theirs origins close to the 
    restaurant. The music has a moment that the instruments play so low that they create the silence for the room. Sun rays casade to the floor, warming his
    feet which are wearing sandals. 

        A splash from a wave transfers him from his cloud to the sand; his left brain now becomes more active. Based on his salary, the hallucination is
    impossible. The airline ticket to Ibiza is at beyond what remains at the end of the month. What he did have enough for is to do the usual, like the party he
    should have been at instead of the beach, in the cold. As a child that refuses to believe that their pet is dead, he kept trying wake up his desire. To
    keep it a dream would mean that the year that is approaching will be exactly the same as the previous ones.

       "Is Ibiza what you really want?" he asked himself in his head. "Yes, nothing else matters." The light shines on him again as he says that and synapses start
    to spark, finding what to throw overboard to let the sinking ship reach the harbor. Starting from Day 1 in his life, Monday, he goes to wakes up, goes to work,
    goes home, goes out to eat, television, and sleep. Same cycle until Friday, with variety falling once in a while for those work days. "But what is my body
    numb to?"

        Recalling those days, most of his days were void of highlights. What he did routinely is go out to get coffee in the morning, buy clothes every other
    week and the such. Coffee now just went down him like cash, absent of flavor. His clothes he assumes now that they aren't made of paper. Taking out his
    notebook, he writes to make his own coffee at home and to stay with the clothes he has while the lighthouse lights him. Crossing those two unconscious
    acts in his life, his ship sinks about a mile away from the coast.

        "Something else." Inspect his life, his cellphone starts ringing. Pulling it out, he sees that the alarm is shaking the phone. Turning it off, he 
    thinks about how essential the phone is. Rarely does it make him lose opportunities with friends or life. The standard form of communication is email or
    internet. Ditching his cell phone for an online number, listening to voicemail or screening them out with the transcibed text makes his ship finish 3/4's
    of the mile. Giving a quick check of his cellphone for anything important, he stands up and throws it to the ocean as far as he can.
    
        "Fuck, I had her number on it." Then he had a thought that crossed his mind, go after the phone but having a sense of his attachment to the phone, he
    made the pass immune to interruptions. Standing back at the shore, he knew his previous self was right and had to climb back to that state. The guy that
    stood on the beach was away from the ship that finally arrived to the harbor, setting its anchor.

        What started to pile up against him is the backlash that it would hold when he told others about not having a cellphone anymore. Staying connected to
    him will be adverse and he behind all. It will be natural that his friends will drift further away from him since their bond was with wireless signals
    instead of a rope. The awkwardness it will be for others when he has to write down their number on his notebook, wondering if he's poor. Being labelled as
    less fortunate than them, the more distance they will place between him and them. He will be the buoy that rocks back and forth in the abyss, existing
    to only those ships that go further than the coast.

        Looking at the white marble of the lighthouse, he thinks about how far it had to come to manifest as a sailor's beacon to land. Marble being an import,
    it had to cross the sea just like the ship did, without guidance. Someone had to go with their idea that the land was worth visiting more than once and
    commit oneself to building it. A foreign land that had now become an old friend that guides the blind ships to the coast safely. He calls to the friend with
    a soft elongated call, wondering if he will be heard. What comes back to the sea is a light and solace.

       Resting his head on top of hands, knees bent; he looks beyond the line where the ocean and black sky meet. Time will slow down once again, he will
    be alone more often; will he survive the solitude? His walls more apparent, the mess in house visible and the urge to fill his space will develop. 
    The sin of gluttony in whatever his mind choose to latch to is possible in his most vulnerable state, using his want as his only sword to ward off the
    shades. For him to succeed, its best to take certain precautions, tilt his environment into his favor. As time passes, his body and mind will adapt to
    the circumstance and gliding pass the danger easy as walking.

        Orange appears on the ground in front of him. Tilting his head up, he sees the first sun rays that start to slay away the night. The day almost here, a
    day where Aphrodite is born, a day of new route. Deja vu, not possible in the path he decided to lock himself in. This unwilling child guided by logos and
    narrow walls to a destination that he committed himself to. Going to his wallet, empty of cash bills, he cuts his credit cards into pieces using his teeth
    and launches them into the ocean. Narrow walls leading to his moment, no where else to go.

        Stretching his fingers, cracking them by compressing the finger with the other hands and pushing them to the other side, frost's bite always hurts, rarely
    tears the hand off. Wringling his hands to keep them in motion cause a heat from within his chest to kindle. On the beach with a hoodie to ward off the fierce,
    artic winds; his body becomes more aware of coast. Hunger takes back seat in his struggle for what he assumes is more than six hours and having thrown his
    credit card into the ocean, pictures making some eggs and beans. He puts that idea to the side as he does with his jacket as he awaits the last seconds before
    the sun surfaces.

       Taking off his sweater makes him vibrate involuntarily as he tries to tame it. A few burst here and there, an average of at least (interception) every
    20 seconds. Despite his body indignation towards the act, his mind becomes succinct. More aware of the each inhale and exhale with the use of his diaphragm.
    Walking closer to the coast, his feet wet from the sea's fluid blue carpet, the sun finally arrives with all its glory. Chest reaching higher than normal,
    shoulders pulled back and hands numbness neglected. The rays send red waves to his body, giving him more warmth than what his hoodie could or the night
    at his friends house. It also gives him something else that remains in pandora's box, smiling in bliss for being olbios.

        Then his back straightens and head reaches for the sky, winter reminding him what day it is. Automatically, he sends his hands to his triceps, pushes them
    closer to the center and rubs them quickly. Icarus has fallen and now it was time to get out of the ocean; to take off his shoes and socks to prevent himself
    from catching a cold. 

        On the concrete, hoodie in one hand and his shoes on the others; he turns over his shoulders to stare again at the waves that are raising in height. The
    breeze now feels refreshing, rejuvinating his tired body for the day. As he is about to leave towards his car, he sees an orange blur from the distance. He
    throws his shoes next to his car, shapes his hand into a teloscope and looks through it. The orange that rocks back and forth is a buoy, ringing its bell.
\end{Document}
